### 2021-04-06 frontiers.tex
Initial Overleaf Import

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is just an example/guide for you to refer to when submitting manuscripts to Frontiers, it is not mandatory to use Frontiers .cls files nor frontiers.tex  %
% This will only generate the Manuscript, the final article will be typeset by Frontiers after acceptance.   
%                                              %
%                                                                                                                                                         %
% When submitting your files, remember to upload this *tex file, the pdf generated with it, the *bib file (if bibliography is not within the *tex) and all the figures.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% Version 3.4 Generated 2018/06/15 %%%
%%% You will need to have the following packages installed: datetime, fmtcount, etoolbox, fcprefix, which are normally inlcuded in WinEdt. %%%
%%% In http://www.ctan.org/ you can find the packages and how to install them, if necessary. %%%
%%%  NB logo1.jpg is required in the path in order to correctly compile front page header %%%

\documentclass[utf8]{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
%\documentclass[utf8]{frontiersHLTH} % for Health articles
%\documentclass[utf8]{frontiersFPHY} % for Physics and Applied Mathematics and Statistics articles

%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
% \usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage{url,hyperref,lineno,microtype}
\usepackage[onehalfspacing]{setspace}

% \linenumbers # commented out when sending the abstract

% Leave a blank line between paragraphs instead of using \\

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Nalborczyk {et~al.}} %use et al only if is more than 1 author
\def\Authors{Ladislas Nalborczyk\,$^{1,2,*}$, Ursula Debarnot\,$^{3,4}$, Marieke Longcamp\,$^{2}$, Aymeric Guillot\,$^{3,4}$, and F.-Xavier Alario\,$^{1}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Aix-Marseille Université, LPC, CNRS UMR 7290, Marseille, France \\
$^{2}$Aix-Marseille Université, LNC, CNRS UMR 7291, Marseille, France \\
$^{3}$Inter-University Laboratory of Human Movement Biology-EA 7424, University of Lyon, University Claude Bernard Lyon 1, Villeurbanne, France \\
$^{4}$Institut Universitaire de France, Paris, France}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Corresponding Author}

\def\corrEmail{ladislas.nalborczyk@univ-grenoble-alpes.fr}

\begin{document}
\onecolumn
\firstpage{1}

\title[Covert verbal actions]{What covert verbal actions tell us about the interplay between language, action, and perception}

\author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
\address{} %This field will be automatically populated
\correspondance{} %This field will be automatically populated

\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}

\maketitle

\begin{abstract}

\noindent Humans have a remarkable ability to imagine actions without executing them. Such motor imagery is accompanied by a subjective multi-sensory experience with auditory, visual, and kinaesthetic components. An influential hypothesis states that these sensory percepts result from a simulation of the corresponding motor action that relies on the same internal models recruited for the control of overt actions. A significant consequence of this hypothesis is that the sensory experience of covert actions would be continuously shaped by sensorimotor interactions with the environment. However, the precise computations required by these internal models and their neural implementation remain unclear. Moreover, this simulationnist view raises the question of how it is possible to imagine actions without executing them. In this perspective, we focus on covert verbal actions such as covert speech, writing, or typing, as an exciting case study to help understanding the interplay between language, motor control, and perceptual processes.

% Since the first explorations of the phenomenological and psychophysiological properties of imagined actions, there has been considerable efforts and progresses towards describing the mechanisms leading to these sensory percepts.

% In other words, despite the involvement of the motor system in providing the sensory experience of the covert action, how can we imagine raising our arm without actually raising our arm?

\tiny
 \keyFont{\section{Keywords:} motor imagery, covert speech, motor simulation, motor control, response inhibition} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

% \tableofcontents

\newpage

\section{Introduction}

% For Original Research Articles \citep{conference}, Clinical Trial Articles \citep{article}, and Technology Reports \citep{patent}, the introduction should be succinct, with no subheadings \citep{book}. For Case Reports the Introduction should include symptoms at presentation \citep{chapter}, physical exams and lab results \citep{dataset}...

Motor imagery can be defined as the mental process by which one rehearses an action, without engaging in the physical movements involved in this particular action \citep{}...

Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}. Therefore, a parallel can be drawn between covert speech and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery...

% Defining mental and motor imagery. Briefly presenting the simulation and emulation theories of motor imagery. What about covert speech? Recent models and relation to the simulation/emulation theories of motor imagery.

\section{The interplay between motor control and cognition}

...

\subsection{Sensory content: Simulation vs. association}

Simulation or association? Direct or indirect routes? Depends on situational (e.g., surrounding noise) and intrinsic (e.g., expertise), in brief on computational cost/resource, concept of memoisation \citep{dasgupta_memory_2021}...

In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms. Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more...

\subsection{Development and novel actions}

How learning does affect sensory experience? Can we use internal models to imagine totally novel (i.e., never executed actions)?

\section{Covert verbal actions as inhibited verbal actions}

% For the sake of clarity, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" (MacLeod, 2007). In the current project, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response (Aron, 2007; O’Shea \& Moran, 2018).

% To be even more precise, Ridderinkhof et al. (2014) described the concept of response inhibition on three continuous dimensions (intentionality, premeditation, specificity). Inhibition can be employed with more or less intentionality (intentional versus reactive inhibition), planned ahead or employed in the moment (early versus late inhibition), and more or less specifically (global inhibition versus effector-specific or action-specific inhibition). More detailed categorisation of inhibitory mechanisms can occur in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...

\subsection{Motor imagery as inhibited execution}

Inhibitory mechanisms underlying the ability to imagine actions...

\subsection{Not producing speech}

Vygotsky idea of speech internalisation and development of inhibition... Induced inhibition deficits (TMS). Inhibition "deficits" in Tourette syndrom...

\section{Discussion}

Summary of the main proposition, theoretical and experimental perspectives.

\section*{Conflict of Interest Statement}

% All financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed. If no such relationship exists, authors will be asked to confirm the following statement:

The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.

\section*{Author Contributions}

The Author Contributions section is mandatory for all articles, including articles by sole authors. If an appropriate statement is not provided on submission, a standard one will be inserted during the production process. The Author Contributions statement must describe the contributions of individual authors referred to by their initials and, in doing so, all authors agree to be accountable for the content of the work. Please see  \href{http://home.frontiersin.org/about/author-guidelines#AuthorandContributors}{here} for full authorship criteria.

\section*{Funding}

Details of all funding sources should be provided, including grant numbers if applicable. Please ensure to add all necessary funding information, as after publication this is no longer possible.

\section*{Acknowledgements}

...

% \section*{Supplemental Data}

% \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure. LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder.

\section*{Data Availability Statement}

No novel data were used in this paper. However, the source (\LaTeX) code is available at XXXX.

% Please see the availability of data guidelines for more information, at https://www.frontiersin.org/about/author-guidelines#AvailabilityofData

\bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
%\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
% \bibliography{test}
\bibliography{bibliography/covert_verbal_actions}

%%% Make sure to upload the bib file along with the tex file and PDF
%%% Please see the test.bib file for some examples of references

\section*{Figure captions}

%%% Please be aware that for original research articles we only permit a combined number of 15 figures and tables, one figure with multiple subfigures will count as only one figure.
%%% Use this if adding the figures directly in the mansucript, if so, please remember to also upload the files when submitting your article
%%% There is no need for adding the file termination, as long as you indicate where the file is saved. In the examples below the files (logo1.eps and logos.eps) are in the Frontiers LaTeX folder
%%% If using *.tif files convert them to .jpg or .png
%%%  NB logo1.eps is required in the path in order to correctly compile front page header %%%

\begin{figure}[h!]
\begin{center}
\includegraphics[width=10cm]{figures/logo1}% This is a *.eps file
\end{center}
\caption{Enter the caption for your figure here.  Repeat as  necessary for each of your figures}\label{fig:1}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=15cm]{figures/logos}
\end{center}
\caption{This is a figure with sub figures, \textbf{(A)} is one logo, \textbf{(B)} is a different logo.}\label{fig:2}
\end{figure}

%%% If you are submitting a figure with subfigures please combine these into one image file with part labels integrated.
%%% If you don't add the figures in the LaTeX files, please upload them when submitting the article.
%%% Frontiers will add the figures at the end of the provisional pdf automatically
%%% The use of LaTeX coding to draw Diagrams/Figures/Structures should be avoided. They should be external callouts including graphics.

\end{document}

### 2021-04-06 manuscript.tex
Rearranging the repo

--- 2021-04-06 frontiers.tex
@@
 
-\documentclass[utf8]{frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
+\documentclass[utf8]{template/frontiersSCNS} % for Science, Engineering and Humanities and Social Sciences articles
 %\documentclass[utf8]{frontiersHLTH} % for Health articles
@@
 % If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
-\def\Address{$^{1}$Aix-Marseille Université, LPC, CNRS UMR 7290, Marseille, France \\
-$^{2}$Aix-Marseille Université, LNC, CNRS UMR 7291, Marseille, France \\
+\def\Address{$^{1}$Aix-Marseille University, LPC, CNRS UMR 7290, Marseille, France \\
+$^{2}$Aix-Marseille University, LNC, CNRS UMR 7291, Marseille, France \\
 $^{3}$Inter-University Laboratory of Human Movement Biology-EA 7424, University of Lyon, University Claude Bernard Lyon 1, Villeurbanne, France \\
@@
 \def\corrAuthor{Corresponding Author}
-
-\def\corrEmail{ladislas.nalborczyk@univ-grenoble-alpes.fr}
+\def\corrEmail{ladislas.nalborczyk@univ-amu.fr}
 
@@
 
-% In other words, despite the involvement of the motor system in providing the sensory experience of the covert action, how can we imagine raising our arm without actually raising our arm?
-
 \tiny
@@
 \end{abstract}
-
-% \tableofcontents
 
@@
 
-% For Original Research Articles \citep{conference}, Clinical Trial Articles \citep{article}, and Technology Reports \citep{patent}, the introduction should be succinct, with no subheadings \citep{book}.
-For Case Reports the Introduction should include symptoms at presentation \citep{chapter}, physical exams and lab results \citep{dataset}...
+% Succinct introduction in four paragraphs.
+% 1) Introduction of motor imagery
+% 2) Covert verbals actions
+% 3) Relating 1) and 2) to the thematic of the research topic
+% 4) Aims of the present perspective
 
-Motor imagery can be defined as the mental process by which one rehearses an action, without engaging in the physical movements involved in this particular action \citep{}...
+Motor imagery can be defined as the mental process by which one rehearses an action, without engaging in the physical movements involved in this particular action...
 
@@
 \subsection{Motor imagery as inhibited execution}
+
+% In other words, despite the involvement of the motor system in providing the sensory experience of the covert action, how can we imagine raising our arm without actually raising our arm?
 
@@
 
-No novel data were used in this paper. However, the source (\LaTeX) code is available at XXXX.
+No novel data were used in this paper. However, the source (\LaTeX) code is available at \url{https://osf.io/dsfgb/}.
 
@@
 
-\bibliographystyle{frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
+\bibliographystyle{template/frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
 %\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
@@
 
-\begin{figure}[h!]
-\begin{center}
-\includegraphics[width=15cm]{figures/logos}
-\end{center}
-\caption{This is a figure with sub figures, \textbf{(A)} is one logo, \textbf{(B)} is a different logo.}\label{fig:2}
-\end{figure}
-
 %%% If you are submitting a figure with subfigures please combine these into one image file with part labels integrated.

### 2021-04-09 manuscript.tex
some draft updates

@@
 % If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
-\def\Address{$^{1}$Aix-Marseille University, LPC, CNRS UMR 7290, Marseille, France \\
-$^{2}$Aix-Marseille University, LNC, CNRS UMR 7291, Marseille, France \\
+\def\Address{$^{1}$Aix Marseille Univ, CNRS, LPC, Marseille, France \\
+$^{2}$Aix Marseille Univ, CNRS, LNC, Marseille, France \\
 $^{3}$Inter-University Laboratory of Human Movement Biology-EA 7424, University of Lyon, University Claude Bernard Lyon 1, Villeurbanne, France \\
@@
 
-Motor imagery can be defined as the mental process by which one rehearses an action, without engaging in the physical movements involved in this particular action...
+The ability to examine our private thoughts is central to our subjective experience...
+Motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action...
 
 Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
-Therefore, a parallel can be drawn between covert speech and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery...
+Therefore, a parallel can be drawn between covert speech and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}...
 
-% Defining mental and motor imagery.
-Briefly presenting the simulation and emulation theories of motor imagery.
-What about covert speech?
-Recent models and relation to the simulation/emulation theories of motor imagery.
+Briefly presenting the simulation and emulation theories of motor imagery. What about covert speech? Recent models and relation to the simulation/emulation theories of motor imagery...
+
+In this perspective, we explore some of the theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions...
+We explore two main themes.
+First, how is produced...
 
@@
 
-...
+How does motor learning/experience influence the multisensory content/experience of motor imagery and covert verbal actions?
+In other words, how to the motor and perceptual system interact during covert verbal actions?
+In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement and delimitations.
+In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of imagined actions, namely studying the imagery ot totally novel (i.e., never executed) actions...
 
@@
 
-Simulation or association?
-Direct or indirect routes?
-Depends on situational (e.g., surrounding noise) and intrinsic (e.g., expertise), in brief on computational cost/resource, concept of memoisation \citep{dasgupta_memory_2021}...
+Where does this sensory (e.g., auditory) content dome from?
+Prediction-by-simulation or prediction-by-association \citep{pickering_integrated_2013}?
+Direct simulation (attention-guided memory retrieval process) or indirect simulation (motor simulation process) \citep{tian_mental_2012, tian_effect_2013, li_corollary_2020, ma_distinct_2019}?
 
+The balance between these two mechanisms may depend by the precise instructions given to the participants (cf.
+Fig \ref{fig:1}).
+More precisely, depending on whether they are instructed to "imagine speaking" or "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})...
+distinct MEG correlates and effects on a subsequent categorisation task \citep{ma_distinct_2019}...
+
+In the absence of non-ambiguous instructions, the balance between these two mechanisms may depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise), in brief on computational cost/resource, concept of memoisation \citep{dasgupta_memory_2021}...
 In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms.
-Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more...
+Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms...
+See also the discussion in  \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}...
 
@@
 
-How learning does affect sensory experience? Can we use internal models to imagine totally novel (i.e., never executed actions)?
+How can we imagined totally novel (i.e., never executed) actions?
+The simulationnist framework suggests that multisensory percepts experienced during motor imagery would result from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions.
+In other words, internal models developed for the control of actions would then be used to simulate the sensory consequences of covert actions.
+Notice that these internal models are generative models, which means that they can a priori be used to compute (predict) the sensory consequences of any action that can be parsed as a (possibly supramodal) goal to an inverse internal model.
+In other words, although never formally tested, this framework entails that novel actions could be simulated internally.\footnote{Briefly mention the study by \cite{mulder_role_2004}...}
+
+A prediction of this putative mechanism is that the imagination of novel actions (rather, the predicted sensory consequences of novel actions) may be "biased" (or "constrained") by the repertoire of already-known actions, given that internal models were developed based on precisely the repertoire of already-known actions.
+This prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an intermediate (interpolated) novel action in the articulatory space.
+The same logic could be applied to the covert production of speech with someone else’s voice.
+How can we imagine speaking with the voice of our partner?
+If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else’s voice should have sensory properties that are somehow “biased” or “constrained” by the properties of our own sensory and motor systems.
+Taking as an illustration the auditory sensations of speech, the subjective auditory sensation of covert speech with someone else’s voice should be situated in a somehow intermediate location in the auditory (e.g., formantic) space between the acoustic properties of our own voice and the acoustic properties of someone else voice.
+
+This prediction could be assessed experimentally by...
 
@@
 
-% For the sake of clarity, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" (MacLeod, 2007).
-In the current project, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response (Aron, 2007; O’Shea \& Moran, 2018).
-
-% To be even more precise, Ridderinkhof et al.
-(2014) described the concept of response inhibition on three continuous dimensions (intentionality, premeditation, specificity).
-Inhibition can be employed with more or less intentionality (intentional versus reactive inhibition), planned ahead or employed in the moment (early versus late inhibition), and more or less specifically (global inhibition versus effector-specific or action-specific inhibition).
-More detailed categorisation of inhibitory mechanisms can occur in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...
+One obvious difference subsist between overt and covert verbal actions, namely that covert actions are not accompanied by overt movements...
+This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be summarised as follows: given the putative role of the motor system in providing the multisensory perceptual content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
 
@@
 
-Inhibitory mechanisms underlying the ability to imagine actions...
+Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}...
+For the sake of clarity, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}.
+In the current project, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
 
-\subsection{Not producing speech}
+To be even more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions (intentionality, premeditation, specificity).
+Inhibition can be employed with more or less intentionality (intentional versus reactive inhibition), planned ahead or employed in the moment (early versus late inhibition), and more or less specifically (global inhibition versus effector-specific or action-specific inhibition).
+More detailed categorisation of inhibitory mechanisms can occur in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...
 
-Vygotsky idea of speech internalisation and development of inhibition... Induced inhibition deficits (TMS). Inhibition "deficits" in Tourette syndrom...
+Neural correlates...
+the inhibitory triangle (cf.
+Fig \ref{fig:2}), composed of the preSMA, the rIFC, and the STN...
+A functional dissociation between the preSMA and the rIFC \citep{diesburg_pause-then-cancel_2021}...
+Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...
+
+\subsection{Learning not to produce speech}
+
+\cite{watson_psychology_1919} first suggested that thought (inner speech, in the terminology) was rooted in (overt) speech, that is, that it matured from overt speech...
+Vygotsky idea of speech internalisation and development of inhibition...
+Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development...
+\cite{fernyhough_alien_2004} extended this model...
+What if speech internalisation was related to the development of inhibitory abilities?
+
+These ideas could be assessed experimentally in several ways.
+First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years).
+We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage.
+Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery.
+For instance, using TMS...
+\citep{angelini_motor_2015, angelini_proactive_2016}...
+Third and finally, inhibition "deficits" in Tourette syndrom...
 
@@
 
-Summary of the main proposition, theoretical and experimental perspectives.
+Summary of the main proposition (i.e., considering covert verbal actions as inhibited verbal actions) and its consequences on the relation between perception and action, theoretical and experimental perspectives.
 
@@
 
-Details of all funding sources should be provided, including grant numbers if applicable. Please ensure to add all necessary funding information, as after publication this is no longer possible.
+% Details of all funding sources should be provided, including grant numbers if applicable. Please ensure to add all necessary funding information, as after publication this is no longer possible.
+
+This work, carried out within the Institut Convergence ILCB (ANR-16-CONV-0002), has benefited from support from the French government, managed by the French National Agency for Research (ANR) and the Excellence Initiative of Aix-Marseille University (A*MIDEX).
 
@@
 
-\begin{figure}[h!]
+\begin{figure}[ht] % float was h! initially
 \begin{center}
-\includegraphics[width=10cm]{figures/logo1}% This is a *.eps file
+\includegraphics[width=10cm]{figures/logo1} % This is a *.eps file
 \end{center}
-\caption{Enter the caption for your figure here.  Repeat as  necessary for each of your figures}\label{fig:1}
+\caption{Prediction-by-simulation and prediction-by-association mechanisms... FIGURE IN PROGRESS.}\label{fig:1}
+\end{figure}
+
+\begin{figure}[ht] % float was h! initially
+\begin{center}
+\includegraphics[width=10cm]{figures/inhibitory_triangle.png} % This is a *.eps file
+\end{center}
+\caption{Inhibitory triangle... FIGURE IN PROGRESS.}\label{fig:2}
 \end{figure}

### 2021-04-09 manuscript.tex
minor updates to readme file

@@
 In other words, how to the motor and perceptual system interact during covert verbal actions?
-In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement and delimitations.
+In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement and delimitation.
 In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of imagined actions, namely studying the imagery ot totally novel (i.e., never executed) actions...
@@
 
-The balance between these two mechanisms may depend by the precise instructions given to the participants (cf.
-Fig \ref{fig:1}).
+The balance between these two mechanisms may depend by the precise instructions given to the participants (see Figure \ref{fig:1} for a summary).
 More precisely, depending on whether they are instructed to "imagine speaking" or "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})...
@@
 
-In the absence of non-ambiguous instructions, the balance between these two mechanisms may depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise), in brief on computational cost/resource, concept of memoisation \citep{dasgupta_memory_2021}...
+In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics.
+In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource, concept of memoisation \citep{dasgupta_memory_2021}...
 In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms.
@@
 This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be summarised as follows: given the putative role of the motor system in providing the multisensory perceptual content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
+We outline some working hypotheses regarding these mechanisms and their plausible roles in certain inhibitory disorders...
 
@@
 the inhibitory triangle (cf.
-Fig \ref{fig:2}), composed of the preSMA, the rIFC, and the STN...
+Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN...
 A functional dissociation between the preSMA and the rIFC \citep{diesburg_pause-then-cancel_2021}...
@@
 
-\cite{watson_psychology_1919} first suggested that thought (inner speech, in the terminology) was rooted in (overt) speech, that is, that it matured from overt speech...
+\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that it matured from overt speech...
 Vygotsky idea of speech internalisation and development of inhibition...
@@
 Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery.
-For instance, using TMS...
+For instance, using TMS, can we brake these inhibitory mechanisms and "force" execution during motor imagery...
 \citep{angelini_motor_2015, angelini_proactive_2016}...

### 2021-04-13 manuscript.tex
minor figures updates

@@
 First, how is produced...
+Second...
+by joining together results from motor imagery, motor inhibition, and covert speech research, we highlight some...
 
@@
 
-\subsection{Sensory content: Simulation vs. association}
+\subsection{Sensory content: prediction-by-simulation vs. prediction-by-association}
 
@@
 To be even more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions (intentionality, premeditation, specificity).
-Inhibition can be employed with more or less intentionality (intentional versus reactive inhibition), planned ahead or employed in the moment (early versus late inhibition), and more or less specifically (global inhibition versus effector-specific or action-specific inhibition).
+Inhibition can be employed with more or less intentionality (intentional vs.
+reactive inhibition), planned ahead or employed in the moment (early vs.
+late inhibition), and more or less specifically (global inhibition versus effector-specific or action-specific inhibition).
 More detailed categorisation of inhibitory mechanisms can occur in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...
@@
 \cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that it matured from overt speech...
-Vygotsky idea of speech internalisation and development of inhibition...
+\cite{vygotsky_thought_1934} idea of speech internalisation and development of inhibition...
 Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development...
@@
 First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years).
-We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage.
+We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage...
+\cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old, but not later...
 Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery.
@@
 
-Summary of the main proposition (i.e., considering covert verbal actions as inhibited verbal actions) and its consequences on the relation between perception and action, theoretical and experimental perspectives.
+% Summary of the main proposition (i.e., considering covert verbal actions as inhibited verbal actions) and its consequences on the relation between perception and action, theoretical and experimental perspectives...
+
+To sum up, we explored the analogy between covert verbal actions such as covert speech and other forms of motor imagery.
+This led us to a discussion of two main themes, that is, the question of how the sensory content of motor imagery is produced, and the question of how is it possible for motor imagery not to lead to motor execution.
+To sketch an answer to these questions, we connected results from the distinct motor imagery, the inner speech, the motor inhibition literature...
+
+We suggested that (section 1 propositions)... and (section 2 propositions)... Taken together, these propositions pave the way for many lines of research that should...
 
@@
 \begin{center}
-\includegraphics[width=10cm]{figures/logo1} % This is a *.eps file
+\includegraphics[width=0.75\textwidth]{figures/association_simulation.png} % This is a *.eps file
 \end{center}
-\caption{Prediction-by-simulation and prediction-by-association mechanisms... FIGURE IN PROGRESS.}\label{fig:1}
+\caption{The balance (weighing) of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms during covert verbal actions depends on both internal (individual) and external (situational) characteristics that jointly determine the computation cost of each option...
+FIGURE IN PROGRESS.}\label{fig:1}
 \end{figure}
@@
 \begin{center}
-\includegraphics[width=10cm]{figures/inhibitory_triangle.png} % This is a *.eps file
+\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
 \end{center}
-\caption{Inhibitory triangle... FIGURE IN PROGRESS.}\label{fig:2}
+\caption{Neural implementation of the inhibitory mechanisms responsible for proactive inhibition.
+The cerebral complex formed by the preSMA, the rIFC and the STN is known as the inhibitory triangle may be responsible for braking motor commands...
+FIGURE IN PROGRESS.}\label{fig:2}
 \end{figure}

### 2021-04-14 manuscript.tex
minor updates to fig1

@@
 
-The ability to examine our private thoughts is central to our subjective experience...
+The ability to mentally examine our thoughts is central to our subjective experience.
+Silently rehearsing...
+allows us to become better at performing them \cite{}, to explore novel situations \cite{}, or to...
 Motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action...
 
+% One of the most influential theoretical model of this broad phenomenon, the motor simulation theory (Jeannerod, 2006, 1994, 2001), contains the three following postulates: i) there exists a continuum between the covert (the mental representation) and the overt execution of an action, ii) action representations can operate off-line, via a simulation mechanism, and iii) covert actions rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited (O’Shea \& Moran, 2017).
+A second class of explanatory models of motor imagery are concerned with the phenomenon of emulation and with internal models (see Gentsch et al., 2016, for a review of the similarities and dissimilarities between simulation and emulation models).
+Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus (Jordan \& Rumelhart, 1992; Kawato et al., 1987).
+The function of internal models is to estimate and anticipate the outcome of a motor command.
+Among the internal model theories, motor control models based on robotic principles (e.g., Kawato, 1999; Wolpert et al., 1995) assume two kinds of internal models (that are supposed to be coupled and regulated): a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states (Gentsch et al., 2016; L\oe venbruck et al., 2018).
+Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models...
+
 Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
-Therefore, a parallel can be drawn between covert speech and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}...
+Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}...
+By building upon models of motor control (e.g., Houde \& Nagarajan, 2011; Wolpert et al., 1995), a recent model describes wilful (voluntary) expanded covert speech as “multi-modal acts with multi-sensory percepts stemming from coarse multi-sensory goals” (L\oe venbruck et al., 2018).
+In other words, this model considers the auditory and kinaesthetic sensations perceived during covert speech to be the predicted sensory consequences of inhibited speech motor acts, emulated by internal forward models that use the efference copies issued from an inverse model (this proposal shares some similarities with the emulation model of motor imagery, Grush, 2004).
+This model is supported by several empirical results providing both behavioural and neurophysiological evidence for the efference copies issued during inner speech production (e.g., Scott, 2013; Whitford et al., 2017).
 
-Briefly presenting the simulation and emulation theories of motor imagery. What about covert speech? Recent models and relation to the simulation/emulation theories of motor imagery...
-
-In this perspective, we explore some of the theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions...
+In this perspective, we explore some theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions.
 We explore two main themes.
-First, how is produced...
+First, we discuss the plausible origins of the sensory (e.g., auditory, tactile) content of covert verbal actions.
 Second...
-by joining together results from motor imagery, motor inhibition, and covert speech research, we highlight some...
+by joining together results from motor imagery, motor inhibition, and covert speech research, we highlight some novel and possibly fruitful lines of research.
 
@@
 \begin{center}
-\includegraphics[width=0.75\textwidth]{figures/association_simulation.png} % This is a *.eps file
+\includegraphics[width=0.75\textwidth]{figures/simulation_association.png} % This is a *.eps file
 \end{center}
-\caption{The balance (weighing) of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms during covert verbal actions depends on both internal (individual) and external (situational) characteristics that jointly determine the computation cost of each option...
+\caption{General depiction of the balance (weighing) between the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms during covert verbal actions depends on both internal (individual) and external (situational) characteristics that jointly determine the computation cost of each option...
 FIGURE IN PROGRESS.}\label{fig:1}
@@
 \end{center}
-\caption{Neural implementation of the inhibitory mechanisms responsible for proactive inhibition.
-The cerebral complex formed by the preSMA, the rIFC and the STN is known as the inhibitory triangle may be responsible for braking motor commands...
+\caption{Neural implementation of the inhibitory mechanisms responsible for proactive inhibition during motor imagery.
+The cerebral complex formed by the preSMA, the rIFC, and the STN is known as the \textit{inhibitory triangle} may be responsible for braking motor commands during covert speech production...
 FIGURE IN PROGRESS.}\label{fig:2}

### 2021-04-16 manuscript.tex
minor updates to figures

--- 2021-04-13 manuscript.tex
@@
 
-The ability to examine our private thoughts is central to our subjective experience...
-Motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action...
+The ability to mentally examine our thoughts is central to our subjective experience.
+Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them (citation), to explore novel situations (citation), or to (citation)...
+Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action.
+Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
+Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}.
 
-Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
-Therefore, a parallel can be drawn between covert speech and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}...
+One of the most influential theoretical model of this broad phenomenon, the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, contains the three following postulates: i) there exists a continuum between the covert (the mental representation) and the overt execution of an action, ii) action representations can operate off-line, via a simulation mechanism, and iii) covert actions rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited (O’Shea \& Moran, 2017).
+A second class of explanatory models of motor imagery are concerned with the phenomenon of emulation and with internal models (see Gentsch et al., 2016, for a review of the similarities and dissimilarities between simulation and emulation models).
+Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus (Jordan \& Rumelhart, 1992; Kawato et al., 1987).
+The function of internal models is to estimate and anticipate the outcome of a motor command.
+Among the internal model theories, motor control models based on robotic principles (e.g., Kawato, 1999; Wolpert et al., 1995) assume two kinds of internal models (that are supposed to be coupled and regulated): a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states \cite{gentsch_towards_2016, loevenbruck_cognitive_2018}.
+Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models...
 
-Briefly presenting the simulation and emulation theories of motor imagery. What about covert speech? Recent models and relation to the simulation/emulation theories of motor imagery...
+% Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
+Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}...
 
-In this perspective, we explore some of the theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions...
+By building upon models of motor control (e.g., Houde \& Nagarajan, 2011; Wolpert et al., 1995), a recent model describes wilful (voluntary) expanded covert speech as "multi-modal acts with multi-sensory percepts stemming from coarse multi-sensory goals" (L\oe venbruck et al., 2018).
+In other words, this model considers the auditory and kinaesthetic sensations perceived during covert speech to be the predicted sensory consequences of inhibited speech motor acts, emulated by internal forward models that use the efference copies issued from an inverse model (this proposal shares some similarities with the emulation model of motor imagery, Grush, 2004).
+This model is supported by several empirical results providing both behavioural and neurophysiological evidence for the efference copies issued during inner speech production (e.g., Scott, 2013; Whitford et al., 2017)...
+
+In this perspective, we explore some theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions.
 We explore two main themes.
-First, how is produced...
-Second...
-by joining together results from motor imagery, motor inhibition, and covert speech research, we highlight some...
+First, we discuss the plausible origins of the sensory (e.g., auditory, tactile) content of covert verbal actions.
+Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions.
+By bridging together recent results from motor imagery, motor inhibition, and inner speech research, we highlight some novel and possibly fruitful lines of research.
 
@@
 In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement and delimitation.
-In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of imagined actions, namely studying the imagery ot totally novel (i.e., never executed) actions...
+In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of imagined actions, namely studying the imagery of totally novel (i.e., never executed) actions...
 
@@
 
-One obvious difference subsist between overt and covert verbal actions, namely that covert actions are not accompanied by overt movements...
-This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be summarised as follows: given the putative role of the motor system in providing the multisensory perceptual content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
-We outline some working hypotheses regarding these mechanisms and their plausible roles in certain inhibitory disorders...
+The proposal that overt and covert actions share common/similar neural circuits is faced with a serious problem.
+If the neural circuits used for the control of overt actions are reused for covert actions, how can covert actions not lead to execution?
+This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory perceptual content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
+In the following, we briefly summarise the evidence in favour of the view of covert verbal actions as inhibited verbal actions.
+Then, we discuss the relations between this view and the supposed progressive internalisation of speech in childhood.
+Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms and their plausible roles in psychological disorders.
 
@@
 
-Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}...
-For the sake of clarity, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}.
-In the current project, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
+First and foremost, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}.
+Here we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
+To be even more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, specificity.
+Inhibition can be employed with more or less intentionality (intentional vs.
+reactive inhibition), it can planned ahead or employed in the moment (early vs.
+late inhibition), and it can be more or less specifically (global inhibition versus effector-specific or action-specific inhibition).
 
-To be even more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions (intentionality, premeditation, specificity).
-Inhibition can be employed with more or less intentionality (intentional vs.
-reactive inhibition), planned ahead or employed in the moment (early vs.
-late inhibition), and more or less specifically (global inhibition versus effector-specific or action-specific inhibition).
-More detailed categorisation of inhibitory mechanisms can occur in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...
+More detailed categorisation of inhibitory mechanisms can occur at any location in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...
+or maybe both global and effector-specifi, cf.
+the results of \cite{rieger_inhibition_2017}...
 
+Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}.
 Neural correlates...
@@
 \begin{center}
-\includegraphics[width=0.75\textwidth]{figures/association_simulation.png} % This is a *.eps file
+\includegraphics[width=0.75\textwidth]{figures/simulation_association.png} % This is a *.eps file
 \end{center}
-\caption{The balance (weighing) of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms during covert verbal actions depends on both internal (individual) and external (situational) characteristics that jointly determine the computation cost of each option...
-FIGURE IN PROGRESS.}\label{fig:1}
+\caption{High-level depiction of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms.
+The balance (weighting) between these two mechanisms during covert verbal actions depends on both task demands and "computational cost" (cf.
+text for more details), which are jointly determined by internal (individual) and external (situational) characteristics (e.g., expertise or (equivalently) task difficulty, noise, feedback perturbation).}\label{fig:1}
 \end{figure}
@@
 \end{center}
-\caption{Neural implementation of the inhibitory mechanisms responsible for proactive inhibition.
-The cerebral complex formed by the preSMA, the rIFC and the STN is known as the inhibitory triangle may be responsible for braking motor commands...
+\caption{Plausible neural implementation of the (cortical and subcortical) inhibitory mechanisms responsible for proactive inhibition during motor imagery.
+The preSMA, the right pIFC, and the STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production...
+Created with BioRender.com...
 FIGURE IN PROGRESS.}\label{fig:2}

### 2021-05-17 manuscript.tex
minor updates to intro

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 % Succinct introduction in four paragraphs.
+% ------------------------------------------
 % 1) Introduction of motor imagery
@@
 % 4) Aims of the present perspective
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 The ability to mentally examine our thoughts is central to our subjective experience.
-Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them (citation), to explore novel situations (citation), or to (citation)...
+Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them \citep[e.g.,][]{toth2020}, to explore novel situations \citep{babar}, or to ...
+\citep{babar}.
 Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action.
-Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
+Because speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
 Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}.
 
-One of the most influential theoretical model of this broad phenomenon, the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, contains the three following postulates: i) there exists a continuum between the covert (the mental representation) and the overt execution of an action, ii) action representations can operate off-line, via a simulation mechanism, and iii) covert actions rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited (O’Shea \& Moran, 2017).
-A second class of explanatory models of motor imagery are concerned with the phenomenon of emulation and with internal models (see Gentsch et al., 2016, for a review of the similarities and dissimilarities between simulation and emulation models).
-Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus (Jordan \& Rumelhart, 1992; Kawato et al., 1987).
+One of the most influential theoretical model of motor imagery the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, postulates the existence of a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism.
+In short, covert actions would rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited \citep{oshea_does_2017}.
+A second class of models are concerned with the phenomenon of emulation \citep{grush_emulation_2004} and with internal models \cite[for a review of the similarities and dissimilarities between simulation and emulation models, see][]{gentsch_towards_2016}.
+Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus \citep[e.g.,][]{jordan_forward_1992, kawato_hierarchical_1987}.
 The function of internal models is to estimate and anticipate the outcome of a motor command.
-Among the internal model theories, motor control models based on robotic principles (e.g., Kawato, 1999; Wolpert et al., 1995) assume two kinds of internal models (that are supposed to be coupled and regulated): a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states \cite{gentsch_towards_2016, loevenbruck_cognitive_2018}.
-Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models...
+Among the internal model theories, motor control models based on robotic principles \citep[e.g.,][]{kawato_internal_1999, wolpert_internal_1995} assume two kinds of internal models: a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states \citep{gentsch_towards_2016, loevenbruck_cognitive_2018}.
+Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models.
 
-% Because speech production results from sequences of motor commands which are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
-Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}...
-
-By building upon models of motor control (e.g., Houde \& Nagarajan, 2011; Wolpert et al., 1995), a recent model describes wilful (voluntary) expanded covert speech as "multi-modal acts with multi-sensory percepts stemming from coarse multi-sensory goals" (L\oe venbruck et al., 2018).
-In other words, this model considers the auditory and kinaesthetic sensations perceived during covert speech to be the predicted sensory consequences of inhibited speech motor acts, emulated by internal forward models that use the efference copies issued from an inverse model (this proposal shares some similarities with the emulation model of motor imagery, Grush, 2004).
+% By building upon models of speech motor control (e.g., Houde \& Nagarajan, 2011; Wolpert et al., 1995), a recent model describes wilful (voluntary) expanded covert speech as "multi-modal acts with multi-sensory percepts stemming from coarse multi-sensory goals" \cite{loevenbruck_cognitive_2018}.
+In other words, this model considers the auditory and kinaesthetic sensations perceived during covert speech to be the predicted sensory consequences of inhibited speech motor acts, emulated by internal forward models that use the efference copies issued from an inverse model (this proposal shares some similarities with the emulation model of motor imagery, Grush, 2004) \cite{grush_emulation_2004}.
 This model is supported by several empirical results providing both behavioural and neurophysiological evidence for the efference copies issued during inner speech production (e.g., Scott, 2013; Whitford et al., 2017)...
@@
 We explore two main themes.
-First, we discuss the plausible origins of the sensory (e.g., auditory, tactile) content of covert verbal actions.
-Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions.
+First, we discuss the plausible origins of the multisensory (e.g., auditory, kinaesthetic) content of covert verbal actions.
+Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions more specifically.
 By bridging together recent results from motor imagery, motor inhibition, and inner speech research, we highlight some novel and possibly fruitful lines of research.
@@
 
-\subsection{Sensory content: prediction-by-simulation vs. prediction-by-association}
+\subsection{Where does this sensory content come from?}
+
+The production of covert speech is often accompanied by the feeling of hearing speech.
+In this section, we discuss a theoretical account of the mechanisms leading to the generation of these percepts during covert speech, while noticing that these mechanisms could be extended to other forms of covert verbal actions as well.
 
@@
 Direct simulation (attention-guided memory retrieval process) or indirect simulation (motor simulation process) \citep{tian_mental_2012, tian_effect_2013, li_corollary_2020, ma_distinct_2019}?
+The dual stream prediction model \citep{tian_mental_2016}...
 
-The balance between these two mechanisms may depend by the precise instructions given to the participants (see Figure \ref{fig:1} for a summary).
+The balance between these two mechanisms may depend by the precise instructions given to the participants...
 More precisely, depending on whether they are instructed to "imagine speaking" or "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})...
@@
 
+Memoisation: avoid redundant computation by storing computational results and reusing them later...
+functions call are intercepted with by a memoiser the inspects the previous calls of a function and its outputs.
+If a function has already been called with the same input, then the previously computed output is retrieved and reused...
+memoisation can be made more flexible (generalisable) by using \textit{interpolation} between cached outputs...
+for instance, in the context of motor control, reaching a goal (e.g., a cup of tea) can be decomposed in motor primitives, where input-output mapping can be retrieved from a memo table and/or interpolated from sufficiently similar stored mappings...
+or as put by \cite{dasgupta_memory_2021}, the "shift from algorithm to memory"...
+this shift is consistent with studies showing a lesser involvement of the motor system for well known imagined actions...
+Depending on whether the task needs to form "precise" sensory representations and whether we have the time resources to do it...
+training studies also suggest that we rely more and more on domain-general memory-processed with expertise \cite{tarr_mental_1989, jolicoeur_time_1985}...
+
 In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics.
-In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource, concept of memoisation \citep{dasgupta_memory_2021}...
+In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource of either alternative.
+To clarify, we ...
+the concept of memoisation as applied to cognition and mental imagery \citep{dasgupta_memory_2021}.
+In this context, memory can be considered as a mechanisms to facilitate computational reuse.
+In the same way...
+efficient cognition may relies on stored past computation results rather than reinventing the wheel every time.
+In the context of motor and speech imagery...
 In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms.
 Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms...
-See also the discussion in  \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}...
+See also the discussion in \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
 
-\subsection{Development and novel actions}
+\subsection{The motor imagery of novel actions}
 
-How can we imagined totally novel (i.e., never executed) actions?
-The simulationnist framework suggests that multisensory percepts experienced during motor imagery would result from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions.
+How can we imagine totally novel (i.e., never executed) actions?
+Broadly speaking, the simulationnist framework suggests that the multisensory experience of motor imagery would result from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions.
 In other words, internal models developed for the control of actions would then be used to simulate the sensory consequences of covert actions.
 Notice that these internal models are generative models, which means that they can a priori be used to compute (predict) the sensory consequences of any action that can be parsed as a (possibly supramodal) goal to an inverse internal model.
-In other words, although never formally tested, this framework entails that novel actions could be simulated internally.\footnote{Briefly mention the study by \cite{mulder_role_2004}...}
+In other words, this framework makes it possible for novel actions to be simulated internally.\footnote{\cite{mulder_role_2004} assessed whether the mental practice of a totally novel movement (abduction of the big toe of the dominant right foot) resulted in better overt execution over the course of several weeks of practice.
+They observed that although mental practise did improve execution in the group of participants that already had some experience with the task at baseline, mental practise did not lead to statistically significant improvements in execution in the group of participants that had zero experience with the task at baseline.
+However, a Bayesian reanalysis of their results suggests that the evidence in favour of the null hypothesis was rather inconclusive ($\text{BF}_{01} = 1.92$, using a weakly informative Cauchy prior on the standardised effect size for the alternative hypothesis, with $r = 1$).}
 
-A prediction of this putative mechanism is that the imagination of novel actions (rather, the predicted sensory consequences of novel actions) may be "biased" (or "constrained") by the repertoire of already-known actions, given that internal models were developed based on precisely the repertoire of already-known actions.
+A prediction of this putative mechanism is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions, given that internal models were developed based on precisely the repertoire of already-known actions.
 This prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an intermediate (interpolated) novel action in the articulatory space.
 The same logic could be applied to the covert production of speech with someone else’s voice.
-How can we imagine speaking with the voice of our partner?
-If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else’s voice should have sensory properties that are somehow “biased” or “constrained” by the properties of our own sensory and motor systems.
+How can we imagine speaking with the voice of our relatives?
+If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else’s voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems.
 Taking as an illustration the auditory sensations of speech, the subjective auditory sensation of covert speech with someone else’s voice should be situated in a somehow intermediate location in the auditory (e.g., formantic) space between the acoustic properties of our own voice and the acoustic properties of someone else voice.
@@
 This prediction could be assessed experimentally by...
+the prediction-by-simulation and the prediction-by-association accounts could be distinguished by constraining the motor system and assessing whether this influences the internal sensory representation of the produced speech.
+If it does...
 
@@
 
-The proposal that overt and covert actions share common/similar neural circuits is faced with a serious problem.
+The proposal that overt and covert actions share common neural circuits is faced with a serious problem.
 If the neural circuits used for the control of overt actions are reused for covert actions, how can covert actions not lead to execution?
-This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory perceptual content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
+This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
 In the following, we briefly summarise the evidence in favour of the view of covert verbal actions as inhibited verbal actions.
-Then, we discuss the relations between this view and the supposed progressive internalisation of speech in childhood.
-Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms and their plausible roles in psychological disorders.
+Then, we discuss the relations between this view and the presumed progressive internalisation of speech during childhood.
+Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms \textit{(and their plausible roles in psychological disorders)}.
 
-\subsection{Motor imagery as inhibited execution}
-
-% In other words, despite the involvement of the motor system in providing the sensory experience of the covert action, how can we imagine raising our arm without actually raising our arm?
+\subsection{Cognitive mechanisms and neural implementation}
 
@@
 More detailed categorisation of inhibitory mechanisms can occur at any location in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...
-or maybe both global and effector-specifi, cf.
+or maybe both global and effector-specific, cf.
 the results of \cite{rieger_inhibition_2017}...
 
-Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}.
+Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}...
+mentioning the success of BCI with neural activity recorded in premotor/motor areas durmong motor imagery and silent speech...
 Neural correlates...
@@
 
-\subsection{Learning not to produce speech}
+Inhibition or subliminal activity/bypassing?
+\citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} vs.
+\cite{loevenbruck_cognitive_2018}...
+However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that to be inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned".
+In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level.
+What cognitive and neural mechanisms operate in order to maintain this activity under the threshold?
+In this section, we provided empirical arguments in favour of the first "active inhibition hypothesis", but proponents of the "subliminal hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.
 
-\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that it matured from overt speech...
-\cite{vygotsky_thought_1934} idea of speech internalisation and development of inhibition...
+\subsection{Inner speech development: Learning not to produce speech}
+
+\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, covert speech matured from overt speech.
+\cite{vygotsky_thought_1934} then prominently formulated the that inner speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood.
+The idea of speech internalisation and development of inhibition...
 Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development...
@@
 We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage...
-\cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old, but not later...
+\cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old).
 Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery.
@@
 
-We suggested that (section 1 propositions)... and (section 2 propositions)... Taken together, these propositions pave the way for many lines of research that should...
+We suggested that (section 1 propositions)... and (section 2 propositions)... Taken together, these propositions pave the way for several lines of research that should...
 
@@
 
+\color{blue}
+
 The Author Contributions section is mandatory for all articles, including articles by sole authors.
@@
 Please see  \href{http://home.frontiersin.org/about/author-guidelines#AuthorandContributors}{here} for full authorship criteria.
+
+\color{black}
+
+...
 
@@
 
-...
+None.
 
@@
 
-\begin{figure}[ht] % float was h! initially
-\begin{center}
-\includegraphics[width=0.75\textwidth]{figures/simulation_association.png} % This is a *.eps file
-\end{center}
-\caption{High-level depiction of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms.
+% \begin{figure}[ht] % float was h! initially
+% \begin{center}
+% \includegraphics[width=0.75\textwidth]{figures/simulation_association.png} % This is a *.eps file
+% \end{center}
+% \caption{High-level depiction of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms.
 The balance (weighting) between these two mechanisms during covert verbal actions depends on both task demands and "computational cost" (cf.
 text for more details), which are jointly determined by internal (individual) and external (situational) characteristics (e.g., expertise or (equivalently) task difficulty, noise, feedback perturbation).}\label{fig:1}
-\end{figure}
+% \end{figure}
 

### 2021-06-07 manuscript.tex
minor updates to introduction

@@
 \noindent Humans have a remarkable ability to imagine actions without executing them.
-Such motor imagery is accompanied by a subjective multi-sensory experience with auditory, visual, and kinaesthetic components.
+Such motor imagery is accompanied by a subjective multisensory experience with auditory, visual, and kinaesthetic components.
 An influential hypothesis states that these sensory percepts result from a simulation of the corresponding motor action that relies on the same internal models recruited for the control of overt actions.
@@
 \tiny
- \keyFont{\section{Keywords:} motor imagery, covert speech, motor simulation, motor control, response inhibition} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+ \keyFont{\section{Keywords:} motor imagery, motor simulation, motor control, response inhibition, covert speech} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
 \end{abstract}
@@
 The ability to mentally examine our thoughts is central to our subjective experience.
-Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them \citep[e.g.,][]{toth2020}, to explore novel situations \citep{babar}, or to ...
-\citep{babar}.
+Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them \citep[e.g.,][]{toth2020}, to explore/practise novel situations \citep{babar}, or to rehearse past situations \citep{babar}.
 Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action.
 Because speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
-Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) and other forms of covert verbal actions (e.g., covert signing, covert writing, covert typing) and, more generally, of motor imagery \citep{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}.
+Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018} and other forms of covert verbal actions such as covert signing, covert writing, or covert typing and, more generally, other imagined actions.
 
-One of the most influential theoretical model of motor imagery the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, postulates the existence of a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism.
+% One of the most influential theoretical model of motor imagery the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, postulates the existence of a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism.
 In short, covert actions would rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited \citep{oshea_does_2017}.
@@
 
-In this perspective, we explore some theoretical and experimental consequences of considering covert verbal actions (e.g., covert speech, covert typing) as inhibited verbal actions.
+In this perspective, we examine some theoretical and experimental consequences of considering covert verbal actions as inhibited verbal actions.
 We explore two main themes.
@@
 
-How does motor learning/experience influence the multisensory content/experience of motor imagery and covert verbal actions?
-In other words, how to the motor and perceptual system interact during covert verbal actions?
-In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement and delimitation.
-In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of imagined actions, namely studying the imagery of totally novel (i.e., never executed) actions...
+Where does the sensory content of covert verbal actions come from?
+How does motor learning influence the multisensory content of covert verbal actions?
+In other words, how do the motor and perceptual system interact during covert verbal actions?
+In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement in different forms of covert speech.
+In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of covert verbal actions, namely, the imagery of totally novel (i.e., never executed) verbal actions.
 
@@
 
-The production of covert speech is often accompanied by the feeling of hearing speech.
-In this section, we discuss a theoretical account of the mechanisms leading to the generation of these percepts during covert speech, while noticing that these mechanisms could be extended to other forms of covert verbal actions as well.
+The production of covert speech is often (although not always and not for everyone) accompanied by the feeling of hearing speech \cite{hurlburt_investigating_2011}.
+In other words, covert speech is accompanied by a sensory experience that "feels like" hearing speech.
+In this section, we discuss the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, a theoretical account of the mechanisms leading to the generation of such auditory percepts during covert speech, while noticing that these mechanisms could be extended to other covert verbal actions as well.
 
-Where does this sensory (e.g., auditory) content dome from?
-Prediction-by-simulation or prediction-by-association \citep{pickering_integrated_2013}?
+The dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}...
 Direct simulation (attention-guided memory retrieval process) or indirect simulation (motor simulation process) \citep{tian_mental_2012, tian_effect_2013, li_corollary_2020, ma_distinct_2019}?
 The dual stream prediction model \citep{tian_mental_2016}...
+\citep[similar to the distinction between the prediction-by-simulation or prediction-by-association mechanisms of][]{pickering_integrated_2013}...
 
-The balance between these two mechanisms may depend by the precise instructions given to the participants...
-More precisely, depending on whether they are instructed to "imagine speaking" or "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})...
-distinct MEG correlates and effects on a subsequent categorisation task \citep{ma_distinct_2019}...
+The balance between these two mechanisms may depend by the precise instructions given to the participants.
+For instance, depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})...
+Congruent with this hypothesis, it has been shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent /ba/-/ta/ categorisation task \citep{ma_distinct_2019}...
+
+In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may also depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics.
+For instance...
+In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource of each alternative.
+To clarify, we borrow the concept of memoisation as applied to cognition and mental imagery by \cite{dasgupta_memory_2021}.
+In this context, memory can be considered as a mechanism to facilitate computational reuse.
+In the same way...
+efficient cognition may rely on stored past computation results rather than reinventing the wheel every time.
+In the context of motor and speech imagery...
+In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms.
+Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms...
+This idea is supported by several studies, showing an increase in facial EMG activity during the reading of difficult text \cite{babar} or while performing difficult mental arithmetic tasks \cite{babar}.
+See also the discussion in \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
 
@@
 Depending on whether the task needs to form "precise" sensory representations and whether we have the time resources to do it...
-training studies also suggest that we rely more and more on domain-general memory-processed with expertise \cite{tarr_mental_1989, jolicoeur_time_1985}...
-
-In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics.
-In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource of either alternative.
-To clarify, we ...
-the concept of memoisation as applied to cognition and mental imagery \citep{dasgupta_memory_2021}.
-In this context, memory can be considered as a mechanisms to facilitate computational reuse.
-In the same way...
-efficient cognition may relies on stored past computation results rather than reinventing the wheel every time.
-In the context of motor and speech imagery...
-In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms.
-Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms...
-See also the discussion in \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
+Training studies also suggest that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
 
@@
 
-A prediction of this putative mechanism is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions, given that internal models were developed based on precisely the repertoire of already-known actions.
+A prediction of this putative mechanism is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions.
 This prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an intermediate (interpolated) novel action in the articulatory space.
@@
 In the following, we briefly summarise the evidence in favour of the view of covert verbal actions as inhibited verbal actions.
-Then, we discuss the relations between this view and the presumed progressive internalisation of speech during childhood.
-Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms \textit{(and their plausible roles in psychological disorders)}.
+Then, we relate this view with the presumed progressive internalisation of speech during childhood.
+Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms.
 
@@
 
-More detailed categorisation of inhibitory mechanisms can occur at any location in this three-dimensional space but for the current purpose it is sufficient to say that we are interested (purportedly) in an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...
+With regards to covert verbal actions specifically, we hypothesise that they involve an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...
 or maybe both global and effector-specific, cf.
 the results of \cite{rieger_inhibition_2017}...
+Notice that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature, in the sense that while doing motor imagery, the participants is not explicitly asked to not produce an action.
+Instead, they are asked to produce the action \textit{covertly}, which (only implicitly) implies that it should be executed overtly.
 
@@
 Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN...
-A functional dissociation between the preSMA and the rIFC \citep{diesburg_pause-then-cancel_2021}...
+A functional dissociation between the preSMA and the rIFC, pause and cancel \citep{diesburg_pause-then-cancel_2021}...
+Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...
+
+Second, the inhibitory perspective presented here could be causally assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
+For instance, TMS can be used to "brake" these inhibitory mechanisms and "force" execution during motor imagery...
+\citep{angelini_motor_2015, angelini_proactive_2016}...
+Third and finally, inhibition "deficits" in Tourette syndrom...
+Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics (Jackson et al., 2015).
+Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia).
+Ganos et al.
+(2014)...
+performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls.
+However, they observed that the pattern of cerebral activity was different across patients and healthy controls.
+In their review, Jackson et al.
+(2015) suggested that increased control over motor outputs is brought about by local increases in GABAergic “tonic” inhibition within re- gions such as the SMA, leading to localised reductions in the gain of motor excitability.
 Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...
@@
 \cite{loevenbruck_cognitive_2018}...
-However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that to be inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned".
+However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned/regulated/monitored".
 In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level.
 What cognitive and neural mechanisms operate in order to maintain this activity under the threshold?
-In this section, we provided empirical arguments in favour of the first "active inhibition hypothesis", but proponents of the "subliminal hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.
+In this section, we provided empirical arguments in favour of the "active inhibition hypothesis", but proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.
 
-\subsection{Inner speech development: Learning not to produce speech}
+\subsection{Covert speech development: Learning not to produce speech}
 
 \cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, covert speech matured from overt speech.
-\cite{vygotsky_thought_1934} then prominently formulated the that inner speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood.
-The idea of speech internalisation and development of inhibition...
-Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development...
+\cite{vygotsky_thought_1934} then prominently formulated that covert speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood.
+Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development.
 \cite{fernyhough_alien_2004} extended this model...
 What if speech internalisation was related to the development of inhibitory abilities?
+The idea of speech internalisation and development of inhibition...
 
@@
 We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage...
-\cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old).
-Second, the inhibitory perspective presented here could be causally assessed by manipulation the inhibitory network preventing execution during motor imagery.
-For instance, using TMS, can we brake these inhibitory mechanisms and "force" execution during motor imagery...
-\citep{angelini_motor_2015, angelini_proactive_2016}...
-Third and finally, inhibition "deficits" in Tourette syndrom...
+\cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old)...
 
@@
 This led us to a discussion of two main themes, that is, the question of how the sensory content of motor imagery is produced, and the question of how is it possible for motor imagery not to lead to motor execution.
-To sketch an answer to these questions, we connected results from the distinct motor imagery, the inner speech, the motor inhibition literature...
+To sketch an answer to these questions, we connected results from the motor imagery, motor inhibition, and inner speech research traditions.
 
@@
 \end{center}
-\caption{Plausible neural implementation of the (cortical and subcortical) inhibitory mechanisms responsible for proactive inhibition during motor imagery.
-The preSMA, the right pIFC, and the STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production...
-Created with BioRender.com...
+\caption{Plausible neural implementation of the (cortical and subcortical) inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during motor imagery.
+The preSMA, right pIFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production.
+Figure created with BioRender.com.
 FIGURE IN PROGRESS.}\label{fig:2}

### 2021-06-08 manuscript.tex
minor updates

@@
 
-In this perspective, we examine some theoretical and experimental consequences of considering covert verbal actions as inhibited verbal actions.
+In this perspective, we examine some theoretical and experimental consequences of considering covert verbal actions as other forms of imagined actions.
 We explore two main themes.
@@
 Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions more specifically.
-By bridging together recent results from motor imagery, motor inhibition, and inner speech research, we highlight some novel and possibly fruitful lines of research.
+By bridging together recent results from the motor imagery, motor inhibition, and covert speech literature, we highlight some novel and possibly fruitful lines of research.
 
@@
 Where does the sensory content of covert verbal actions come from?
-How does motor learning influence the multisensory content of covert verbal actions?
+How does motor learning shape these sensory percepts?
 In other words, how do the motor and perceptual system interact during covert verbal actions?
@@
 The dual stream prediction model \citep{tian_mental_2016}...
-\citep[similar to the distinction between the prediction-by-simulation or prediction-by-association mechanisms of][]{pickering_integrated_2013}...
+\citep[this proposal shares similarities with the distinction between the prediction-by-simulation or prediction-by-association mechanisms of][]{pickering_integrated_2013}.
 
-The balance between these two mechanisms may depend by the precise instructions given to the participants.
-For instance, depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" speech (similar to the distinction between the "inner ear" and the "inner voice", e.g., \cite{smith_subvocalization_1992})...
-Congruent with this hypothesis, it has been shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent /ba/-/ta/ categorisation task \citep{ma_distinct_2019}...
+The balance between these two mechanisms may depend on the precise instructions given to the participants, which may clue them to produce different form of covert speech.
+For instance, depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" speech \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}...
+Congruent with this hypothesis, it has been shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent /ba/-/ta/ categorisation task \citep{ma_distinct_2019}.
+Moreover...
 
@@
 For instance...
-In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost/resource of each alternative.
-To clarify, we borrow the concept of memoisation as applied to cognition and mental imagery by \cite{dasgupta_memory_2021}.
-In this context, memory can be considered as a mechanism to facilitate computational reuse.
-In the same way...
-efficient cognition may rely on stored past computation results rather than reinventing the wheel every time.
-In the context of motor and speech imagery...
+In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost of (or equivalently, the computational resources available for) each alternative.
+To clarify, we borrow the concept of memoisation as applied to cognition and mental imagery by \cite{dasgupta_memory_2021}.\footnote{Memoisation is a programming technique used to speed-up algorithms or programs.
+It avoids redundant computation by storing computational results and reusing them later.
+When calling a function (where a function can be a motor primitive such as elevating the arm), the function call is intercepted by a memoiser that inspects the previous calls of a function and its outputs.
+If a function has already been called with the same input, then the previously computed output is retrieved and reused.} In this context, memory can be considered as a mechanism to facilitate computational reuse.
+In the same way efficient programming may rely on computational reuse, efficient cognition may rely on stored past computation results rather than reinventing the wheel every time.
+In the context of motor and speech imagery, the memory-retrieval predictions stream would be the memoised version of the simulation-estimation prediction stream, where motor-to-sensory mappings are (party or completely) retrieved from memory, instead of being computed again...
+
 In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms.
-Novel and/or difficult tasks may rely more on the simulation mechanism whereas well known tasks may rely more on associative mechanisms...
-This idea is supported by several studies, showing an increase in facial EMG activity during the reading of difficult text \cite{babar} or while performing difficult mental arithmetic tasks \cite{babar}.
-See also the discussion in \citep{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
+For instance, we hypothesise that novel and/or difficult tasks (which are both computationally more expensive, ceteris paribus) may rely more on the simulation mechanism, whereas well known and/or easy tasks may rely more on associative mechanisms.
+This idea is supported by several studies showing a greater increase in facial EMG activity during the reading of difficult text or while performing difficult mental arithmetic tasks as compared to easier tasks \citep[e.g.,][]{faaborg-andersen_electromyography_1958, sokolov_inner_1972}, suggesting a greater involvement of the speech motor system \citep[and/or a lesser involvement of inhibitory mechanisms, see also the discussion in][]{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
+This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
 
-Memoisation: avoid redundant computation by storing computational results and reusing them later...
+% Memoisation: avoid redundant computation by storing computational results and reusing them later...
 functions call are intercepted with by a memoiser the inspects the previous calls of a function and its outputs.
@@
 
-How can we imagine totally novel (i.e., never executed) actions?
-Broadly speaking, the simulationnist framework suggests that the multisensory experience of motor imagery would result from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions.
+If, as suggested in the previous section, the sensory content of covert verbal actions is (at least in some situations) provided by a motor simulation process, how can we imagine totally novel (i.e., never executed) actions?
+Broadly speaking, the simulationnist framework suggests that the multisensory experience of motor imagery results from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions.
 In other words, internal models developed for the control of actions would then be used to simulate the sensory consequences of covert actions.
-Notice that these internal models are generative models, which means that they can a priori be used to compute (predict) the sensory consequences of any action that can be parsed as a (possibly supramodal) goal to an inverse internal model.
+Crucially, these internal models are generative models, which means that they can be used to compute (i.e., predict) the sensory consequences of any action that can be parsed as a (possibly supramodal) goal to an inverse internal model.
 In other words, this framework makes it possible for novel actions to be simulated internally.\footnote{\cite{mulder_role_2004} assessed whether the mental practice of a totally novel movement (abduction of the big toe of the dominant right foot) resulted in better overt execution over the course of several weeks of practice.
@@
 A prediction of this putative mechanism is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions.
-This prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an intermediate (interpolated) novel action in the articulatory space.
-The same logic could be applied to the covert production of speech with someone else’s voice.
+For instance, when asked to imagine playing table tennis, a tennis player may overestimate movements' amplitude and duration.
+Translated to speech production, this prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an intermediate (interpolated) novel action in the articulatory space.
+The same logic could be applied to the covert production of speech with someone else's voice.
 How can we imagine speaking with the voice of our relatives?
-If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else’s voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems.
-Taking as an illustration the auditory sensations of speech, the subjective auditory sensation of covert speech with someone else’s voice should be situated in a somehow intermediate location in the auditory (e.g., formantic) space between the acoustic properties of our own voice and the acoustic properties of someone else voice.
+If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else's voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems.
+Taking as an illustration the auditory sensations of speech, the subjective auditory sensation of covert speech with someone else's voice should be situated in a somehow intermediate location in the auditory (e.g., formantic) space, between the acoustic properties of our own voice and the acoustic properties of someone else voice.
 
-This prediction could be assessed experimentally by...
+% This prediction could be assessed experimentally by...
 the prediction-by-simulation and the prediction-by-association accounts could be distinguished by constraining the motor system and assessing whether this influences the internal sensory representation of the produced speech.
 If it does...
+
+This prediction could be assessed experimentally by using the sensory attenuation effect observed during covert speech production.
+Auditory stimuli elicit an electrophysiological brain response (the auditory-evoked potential) with a characteristic N1 component.
+This N1 component has been shown to be reduced when the presentation of an auditory stimulus is synchronised with the self-production of a phonetically-matched vocalisation (an effect called N1-suppression).
+More interestingly, \cite{whitford_neurophysiological_2017} shown that the covert production of a phoneme also resulted in sensory attenuation (as assessed by N1-suppression) if the content of the imagined phoneme matched the content of the audible phoneme.
+Therefore, we could describe the subjective auditory sensation of covert speaking with someone else’s voice by manipulating the acoustic (e.g., formantic) properties of the auditory stimulus that is presented to the participant to find the stimulus that produces the greatest sensory attenuation (as assessed by N1-suppression).
+In other words, sensory attenuation should be the strongest when it matches the auditory representation of the speaker.
+If the auditory percepts generated when covert speaking with the voice of someone else is "constrained" by our own motor system, then this point of greatest sensory attenuation should occur in an intermediate location in the feature (e.g., formantic) space.
 
@@
 In the following, we briefly summarise the evidence in favour of the view of covert verbal actions as inhibited verbal actions.
-Then, we relate this view with the presumed progressive internalisation of speech during childhood.
-Finally, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms.
+Then, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms.
+Finally, we relate this view with the presumed progressive internalisation of speech during childhood.
 
@@
 First and foremost, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}.
-Here we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
+Here, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
 To be even more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, specificity.
@@
 
-With regards to covert verbal actions specifically, we hypothesise that they involve an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition...
-or maybe both global and effector-specific, cf.
+With regards to covert verbal actions specifically, we hypothesise that they involve an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition.
+Or maybe both global and effector-specific, cf.
 the results of \cite{rieger_inhibition_2017}...
@@
 
-% Summary of the main proposition (i.e., considering covert verbal actions as inhibited verbal actions) and its consequences on the relation between perception and action, theoretical and experimental perspectives...
+% Summary of the main proposition (i.e., considering covert verbal actions as inhibited verbal actions) and its consequences on the relation between perception and action + theoretical and experimental perspectives.
 
-To sum up, we explored the analogy between covert verbal actions such as covert speech and other forms of motor imagery.
-This led us to a discussion of two main themes, that is, the question of how the sensory content of motor imagery is produced, and the question of how is it possible for motor imagery not to lead to motor execution.
+To sum up, we explored (some of) the theoretical and experimental perspectives that emerge when considering covert verbal actions as other forms of imagined actions.
+This led us to a discussion of two main themes.
+First, we discussed the plausible origins two of the sensory content of convert verbal actions is produced.
+Second, we asked how is it possible for motor imagery not to lead to motor execution.
 To sketch an answer to these questions, we connected results from the motor imagery, motor inhibition, and inner speech research traditions.
 
-We suggested that (section 1 propositions)... and (section 2 propositions)... Taken together, these propositions pave the way for several lines of research that should...
+Regarding the origin of the sensory experience of covert verbal actions, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process.
+We suggested that the balance between these two mechanisms, in addition to the type of covert speech that is prompted by the tasks instructions, may also be determined by the available computational resources (or equivalently, the cost of the task, with novel or more difficult tasks being more costly).
+More precisely...
+
+Regarding the role of general-purpose inhibitory mechanisms during the production of covert verbal actions, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and summarised some propositions from this literature.
+We related the development of response inhibition abilities in childhood development with the purported internalisation of private speech around the same period.
+From the response inhibition perspective, the internalisation of speech from overt to covert speech may essentially be considered as "learning not to produce speech" (i.e., learning pairs of internal models that will be used to simulate speech motor-to-sensory mappings).
+
+Taken together, these propositions pave the way for several lines of research that should... conclusion...
 

### 2021-06-11 manuscript.tex
minor updates to intro

@@
 
+% Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action
+
 The ability to mentally examine our thoughts is central to our subjective experience.
-Mentally anticipating or rehearsing (verbal) actions allows us to become better at performing them \citep[e.g.,][]{toth2020}, to explore/practise novel situations \citep{babar}, or to rehearse past situations \citep{babar}.
-Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action.
+Mentally anticipating or rehearsing verbal actions allows us to become better at performing them \citep[e.g.,][]{toth_does_2020}, to explore/practise novel situations \citep{babar}, or to rehearse past situations \citep{babar}.
 Because speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
-Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018} and other forms of covert verbal actions such as covert signing, covert writing, or covert typing and, more generally, other imagined actions.
+Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018} and other forms of covert verbal actions such as covert writing or covert typing and, more generally, other imagined actions.
 
@@
 First, we discuss the plausible origins of the multisensory (e.g., auditory, kinaesthetic) content of covert verbal actions.
-Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions more specifically.
+Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions, more specifically.
 By bridging together recent results from the motor imagery, motor inhibition, and covert speech literature, we highlight some novel and possibly fruitful lines of research.
@@
 In other words, covert speech is accompanied by a sensory experience that "feels like" hearing speech.
-In this section, we discuss the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, a theoretical account of the mechanisms leading to the generation of such auditory percepts during covert speech, while noticing that these mechanisms could be extended to other covert verbal actions as well.
+In this section, we discuss the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, a theoretical account of the mechanisms leading to the generation of such auditory percepts during covert speech, while noticing that these mechanisms could be extended to other verbal actions as well.
 
-The dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}...
-Direct simulation (attention-guided memory retrieval process) or indirect simulation (motor simulation process) \citep{tian_mental_2012, tian_effect_2013, li_corollary_2020, ma_distinct_2019}?
-The dual stream prediction model \citep{tian_mental_2016}...
-\citep[this proposal shares similarities with the distinction between the prediction-by-simulation or prediction-by-association mechanisms of][]{pickering_integrated_2013}.
+The dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} describes two neural pathways that may provide the auditory content of covert speech.
+First, the simulation-estimation prediction stream implements a motor-to-sensory transformation via motor simulation, that is, by simulating speech movements and the perceptual changes that would be associated with these movements \citep[see also][for a similar proposal]{loevenbruck_cognitive_2018}.
+This stream includes cerebral areas involved in speech motor preparation such as the supplementary motor area, the inferior frontal gyrus, the premotor cortex and the insula, as well as cerebral areas involved in somatosensory estimation and perception such as primary and secondary somatosensory regions, the parietal operculum and the supramarginal gyrus \citep{tian_mental_2016}.
+Second, the memory-retrieval prediction stream may be used to provide auditory percepts by "reconstructing stored perceptual information in modality-specific cortices" \citep{tian_mental_2016}.
+In other words, sensory percepts would be generated by activating sensory-specific cortices from object properties stored in long-term memory.
+This mechanism provides sensory percepts without the need for computing the predicted sensory consequences of (non executed) motor commands.
+This stream includes semantic networks, including frontal, temporal, and parietal regions \citep{tian_mental_2016}.\footnote{This distinction shares similarities with the distinction between the prediction-by-simulation or prediction-by-association mechanisms in speech production and comprehension suggested by \cite{pickering_integrated_2013}.}
 
-The balance between these two mechanisms may depend on the precise instructions given to the participants, which may clue them to produce different form of covert speech.
-For instance, depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" speech \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}...
-Congruent with this hypothesis, it has been shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent /ba/-/ta/ categorisation task \citep{ma_distinct_2019}.
-Moreover...
+The balance between these two mechanisms (i.e., simulation vs.
+association) may depend on the precise instructions given to the participants, which may clue them to produce different forms of covert speech.
+For instance, either one of these two streams may be recruited preferentially depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}.
+Congruent with this hypothesis, \cite{tian_mental_2016} have shown that imagined speaking ...
+Moreover, \cite{ma_distinct_2019} have shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent /ba/-/ta/ categorisation task...
 
 In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may also depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics.
-For instance...
-In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of one of these mechanisms is the computational cost of (or equivalently, the computational resources available for) each alternative.
+In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of either one of these mechanisms is the computational cost of (or equivalently, the computational resources available for) each alternative.
 To clarify, we borrow the concept of memoisation as applied to cognition and mental imagery by \cite{dasgupta_memory_2021}.\footnote{Memoisation is a programming technique used to speed-up algorithms or programs.
@@
 If a function has already been called with the same input, then the previously computed output is retrieved and reused.} In this context, memory can be considered as a mechanism to facilitate computational reuse.
-In the same way efficient programming may rely on computational reuse, efficient cognition may rely on stored past computation results rather than reinventing the wheel every time.
-In the context of motor and speech imagery, the memory-retrieval predictions stream would be the memoised version of the simulation-estimation prediction stream, where motor-to-sensory mappings are (party or completely) retrieved from memory, instead of being computed again...
+In the context of motor and speech imagery, memoisation can be seen in the greater reliance on memory (vs.
+motor processes) in the course of learning, where motor-to-sensory mappings are (party or completely) retrieved from memory, instead of being computed again every time.
 
@@
 If, as suggested in the previous section, the sensory content of covert verbal actions is (at least in some situations) provided by a motor simulation process, how can we imagine totally novel (i.e., never executed) actions?
-Broadly speaking, the simulationnist framework suggests that the multisensory experience of motor imagery results from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions.
+Broadly speaking, the simulationnist framework suggests that the multisensory experience of motor imagery results from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions \citep[e.g.,][]{jeannerod_representing_1994}.
 In other words, internal models developed for the control of actions would then be used to simulate the sensory consequences of covert actions.
-Crucially, these internal models are generative models, which means that they can be used to compute (i.e., predict) the sensory consequences of any action that can be parsed as a (possibly supramodal) goal to an inverse internal model.
+Crucially, these internal models are generative models, which means that they can be used to compute (i.e., predict) the sensory consequences of any action that can be parsed as a (possibly supramodal) goal to an inverse internal model \citep{loevenbruck_cognitive_2018}.
 In other words, this framework makes it possible for novel actions to be simulated internally.\footnote{\cite{mulder_role_2004} assessed whether the mental practice of a totally novel movement (abduction of the big toe of the dominant right foot) resulted in better overt execution over the course of several weeks of practice.
@@
 
-A prediction of this putative mechanism is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions.
+A general prediction of this framework is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions.
 For instance, when asked to imagine playing table tennis, a tennis player may overestimate movements' amplitude and duration.
@@
 If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else's voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems.
-Taking as an illustration the auditory sensations of speech, the subjective auditory sensation of covert speech with someone else's voice should be situated in a somehow intermediate location in the auditory (e.g., formantic) space, between the acoustic properties of our own voice and the acoustic properties of someone else voice.
+In other words, the subjective auditory sensation of covert speech with someone else's voice should be situated in a somehow intermediate (i.e., between the acoustic properties of our own voice and the acoustic properties of someone else voice) location in the auditory (e.g., formantic) space.
 
@@
 Then, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms.
-Finally, we relate this view with the presumed progressive internalisation of speech during childhood.
+Finally, we relate this view to the presumed progressive internalisation of speech during childhood.
 
@@
 
-With regards to covert verbal actions specifically, we hypothesise that they involve an intentional (we know we want to produce motor imagery rather than overt execution) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition.
+With regards to covert verbal actions specifically, we hypothesise that they involve an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition.
 Or maybe both global and effector-specific, cf.
 the results of \cite{rieger_inhibition_2017}...
-Notice that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature, in the sense that while doing motor imagery, the participants is not explicitly asked to not produce an action.
-Instead, they are asked to produce the action \textit{covertly}, which (only implicitly) implies that it should be executed overtly.
+Notice that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature, in the sense that while doing motor imagery, participants are not explicitly asked to not produce an action.
+Instead, they are asked to produce the action \textit{covertly}, which (only implicitly) implies that it should not be executed overtly.
 
 Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}...
-mentioning the success of BCI with neural activity recorded in premotor/motor areas durmong motor imagery and silent speech...
+mentioning the success of BCI with neural activity recorded in premotor/motor areas during motor imagery and silent speech...
 Neural correlates...
@@
 Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN...
-A functional dissociation between the preSMA and the rIFC, pause and cancel \citep{diesburg_pause-then-cancel_2021}...
-Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...
+\cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the preSMA and the rIFC.
+In their model, they suggest that the preSMA would be involved in pausing the action whereas the rIFC would be involved in cancelling (resetting) motor commands...
 
-Second, the inhibitory perspective presented here could be causally assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
+The role of inhibitory mechanisms during covert verbal actions could be causally assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
 For instance, TMS can be used to "brake" these inhibitory mechanisms and "force" execution during motor imagery...
@@
 
-Inhibition or subliminal activity/bypassing?
-\citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} vs.
-\cite{loevenbruck_cognitive_2018}...
+The role of the primary motor cortex and the emission of motor commands during covert speech production has been debated.
+It has been suggested that the primary motor cortex could be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}.
 However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned/regulated/monitored".
@@
 
-\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, covert speech matured from overt speech.
-\cite{vygotsky_thought_1934} then prominently formulated that covert speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood.
-Vygotsky observed, as Piaget did before, that egocentric or "private" speech tend to be internalised during child development.
+\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that covert speech matures from overt speech.
+\cite{vygotsky_thought_1934} then prominently formulated the idea that covert speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood.
+Vygotsky observed, as Piaget before, that egocentric or "private" speech tends to be internalised during child development.
 \cite{fernyhough_alien_2004} extended this model...
@@
 \cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old)...
+Second, the hypothesised co-development of motor imagery and response inhibition abilities could be assessed by looking at the learning of novel actions...
+learning a music instrument...
 
@@
 
-To sum up, we explored (some of) the theoretical and experimental perspectives that emerge when considering covert verbal actions as other forms of imagined actions.
+To sum up, we explored some of the theoretical and experimental perspectives that emerge when considering covert verbal actions as other forms of imagined actions.
 This led us to a discussion of two main themes.
-First, we discussed the plausible origins two of the sensory content of convert verbal actions is produced.
-Second, we asked how is it possible for motor imagery not to lead to motor execution.
+First, we discussed two mechanisms that may be used to provide the sensory (auditory) content of covert verbal actions, and how their respective involvement may be constrained by the available computational resources.
+Second, we asked how it is possible for motor imagery not to lead to motor execution.
 To sketch an answer to these questions, we connected results from the motor imagery, motor inhibition, and inner speech research traditions.
 
-Regarding the origin of the sensory experience of covert verbal actions, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process.
-We suggested that the balance between these two mechanisms, in addition to the type of covert speech that is prompted by the tasks instructions, may also be determined by the available computational resources (or equivalently, the cost of the task, with novel or more difficult tasks being more costly).
-More precisely...
+Regarding neural origin of the sensory experience of covert verbal actions, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process.
+We suggested that the balance between these two mechanisms, in addition to the task instructions (which may prompt different forms of covert speech), may also be determined by the available computational resources (or equivalently, the computational cost of the task, with novel or more difficult tasks being more costly).
+More precisely, novel or more difficult tasks are expected to rely more on the motor-simulation mechanisms whereas well-known and/or easy tasks may rely more on a "memoised version" of the motor simulation: the memory-retrieval prediction stream.
 
-Regarding the role of general-purpose inhibitory mechanisms during the production of covert verbal actions, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and summarised some propositions from this literature.
+Regarding the role of general-purpose inhibitory mechanisms during the production of covert verbal actions, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and we summarised some propositions from this literature.
 We related the development of response inhibition abilities in childhood development with the purported internalisation of private speech around the same period.
-From the response inhibition perspective, the internalisation of speech from overt to covert speech may essentially be considered as "learning not to produce speech" (i.e., learning pairs of internal models that will be used to simulate speech motor-to-sensory mappings).
+From the response inhibition perspective, the internalisation of speech from overt to covert speech may essentially be considered as "learning not to produce speech" (i.e., learning pairs of internal models that will be used to simulate speech motor-to-sensory mappings while not executing speech).
 
-Taken together, these propositions pave the way for several lines of research that should... conclusion...
+Taken together, these propositions pave the way for several lines of research that should consolidate our understanding of covert speech, covert verbal actions, and motor imagery more generally...
 

### 2021-06-22 manuscript.tex
first version of the entire manuscript

@@
 
-\noindent Humans have a remarkable ability to imagine actions without executing them.
-Such motor imagery is accompanied by a subjective multisensory experience with auditory, visual, and kinaesthetic components.
+\noindent Motor imagery is accompanied by a subjective multisensory experience with auditory, visual, and kinaesthetic components.
 An influential hypothesis states that these sensory percepts result from a simulation of the corresponding motor action that relies on the same internal models recruited for the control of overt actions.
@@
 
+% Mentally anticipating or rehearsing verbal actions allows us to become better at performing them \citep[e.g.,][]{toth_does_2020}, to explore/practise novel situations \citep{babar}, or to rehearse past situations \citep{babar}.
+
 The ability to mentally examine our thoughts is central to our subjective experience.
-Mentally anticipating or rehearsing verbal actions allows us to become better at performing them \citep[e.g.,][]{toth_does_2020}, to explore/practise novel situations \citep{babar}, or to rehearse past situations \citep{babar}.
+The internal (covert) production of speech may accompany common activities such as problem solving \citep{baldo_is_2005, sokolov_inner_1972}, future planning \citep{dargembeau_frequency_2011}, reading \citep[e.g.,][]{loevenbruck_left_2005, perrone-bertolotti_how_2012}, or writing \citep{frith_reading_1979}.
 Because speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
@@
 First, the simulation-estimation prediction stream implements a motor-to-sensory transformation via motor simulation, that is, by simulating speech movements and the perceptual changes that would be associated with these movements \citep[see also][for a similar proposal]{loevenbruck_cognitive_2018}.
-This stream includes cerebral areas involved in speech motor preparation such as the supplementary motor area, the inferior frontal gyrus, the premotor cortex and the insula, as well as cerebral areas involved in somatosensory estimation and perception such as primary and secondary somatosensory regions, the parietal operculum and the supramarginal gyrus \citep{tian_mental_2016}.
+This stream includes cerebral areas involved in speech motor preparation such as the supplementary motor area, the inferior frontal gyrus, the premotor cortex and the insula, as well as cerebral areas involved in somatosensory estimation and perception such as primary and secondary somatosensory regions, the parietal operculum, and the supramarginal gyrus \citep{tian_mental_2016}.
 Second, the memory-retrieval prediction stream may be used to provide auditory percepts by "reconstructing stored perceptual information in modality-specific cortices" \citep{tian_mental_2016}.
@@
 This mechanism provides sensory percepts without the need for computing the predicted sensory consequences of (non executed) motor commands.
-This stream includes semantic networks, including frontal, temporal, and parietal regions \citep{tian_mental_2016}.\footnote{This distinction shares similarities with the distinction between the prediction-by-simulation or prediction-by-association mechanisms in speech production and comprehension suggested by \cite{pickering_integrated_2013}.}
+This stream includes semantic networks, including frontal, temporal, and parietal regions \citep[for more details, see][]{tian_mental_2016}.
+
+%\footnote{This distinction shares similarities with the distinction between the prediction-by-simulation or prediction-by-association mechanisms in speech production and comprehension suggested by \cite{pickering_integrated_2013}.}
 
@@
 For instance, either one of these two streams may be recruited preferentially depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}.
-Congruent with this hypothesis, \cite{tian_mental_2016} have shown that imagined speaking ...
-Moreover, \cite{ma_distinct_2019} have shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent /ba/-/ta/ categorisation task...
+In line with this hypothesis, \cite{tian_mental_2016} have shown that imagined speaking more strongly recruits cerebral regions in the simulation stream than imagined hearing, which more strongly recruits cerebral regions in the association stream.
+Moreover, \cite{ma_distinct_2019} have shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent phonetic (discriminating /ba/ vs.
+/da/) categorisation task.
 
@@
 When calling a function (where a function can be a motor primitive such as elevating the arm), the function call is intercepted by a memoiser that inspects the previous calls of a function and its outputs.
-If a function has already been called with the same input, then the previously computed output is retrieved and reused.} In this context, memory can be considered as a mechanism to facilitate computational reuse.
+If a function has already been called with the same input, then the previously computed output is retrieved and reused.} In their view, memory can be considered as a computational resource to facilitate computational reuse through memoisation.
 In the context of motor and speech imagery, memoisation can be seen in the greater reliance on memory (vs.
@@
 
-In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost (or equivalently, the available computational resources), which in turn determines the balance between the simulation and association mechanisms.
+In other words, situational (extrinsic) and individual (intrinsic) characteristics jointly determine the computational cost of (or equivalently, the available computational resources for) the task, which in turn determines the balance between the simulation and association mechanisms.
 For instance, we hypothesise that novel and/or difficult tasks (which are both computationally more expensive, ceteris paribus) may rely more on the simulation mechanism, whereas well known and/or easy tasks may rely more on associative mechanisms.
@@
 In other words, internal models developed for the control of actions would then be used to simulate the sensory consequences of covert actions.
-Crucially, these internal models are generative models, which means that they can be used to compute (i.e., predict) the sensory consequences of any action that can be parsed as a (possibly supramodal) goal to an inverse internal model \citep{loevenbruck_cognitive_2018}.
+Crucially, these internal models are generative models, which means that they can be used to compute (i.e., predict) the sensory consequences of any action that can be parsed as a \citep[possibly supramodal, see][]{loevenbruck_cognitive_2018} goal to an inverse internal model.
 In other words, this framework makes it possible for novel actions to be simulated internally.\footnote{\cite{mulder_role_2004} assessed whether the mental practice of a totally novel movement (abduction of the big toe of the dominant right foot) resulted in better overt execution over the course of several weeks of practice.
@@
 For instance, when asked to imagine playing table tennis, a tennis player may overestimate movements' amplitude and duration.
-Translated to speech production, this prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an intermediate (interpolated) novel action in the articulatory space.
+Translated to speech production, this prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an "intermediate" novel action in the articulatory space.
 The same logic could be applied to the covert production of speech with someone else's voice.
@@
 Here, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
-To be even more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, specificity.
+To be more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, specificity.
 Inhibition can be employed with more or less intentionality (intentional vs.
@@
 With regards to covert verbal actions specifically, we hypothesise that they involve an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition.
-Or maybe both global and effector-specific, cf.
-the results of \cite{rieger_inhibition_2017}...
-Notice that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature, in the sense that while doing motor imagery, participants are not explicitly asked to not produce an action.
+Notice however that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature, in the sense that while doing motor imagery, participants are not explicitly asked to not produce an action \citep{guillot_imagining_2012}.
 Instead, they are asked to produce the action \textit{covertly}, which (only implicitly) implies that it should not be executed overtly.
+Using an action mode (overt vs.
+covert) switching paradigm, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have showed that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{scheil_motor_2018}.
 
-Inhibitory mechanisms underlying the ability to imagine actions \citep{guillot_imagining_2012, schwoebel_man_2002}...
-mentioning the success of BCI with neural activity recorded in premotor/motor areas during motor imagery and silent speech...
-Neural correlates...
-the inhibitory triangle (cf.
-Figure \ref{fig:2}), composed of the preSMA, the rIFC, and the STN...
-\cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the preSMA and the rIFC.
-In their model, they suggest that the preSMA would be involved in pausing the action whereas the rIFC would be involved in cancelling (resetting) motor commands...
+% further confirmed that both global and effector-specific inhibition may be at play during imagined (hand) movements and suggested that these two types of inhibition may work together and compensate for each other...
+\cite{schwoebel_man_2002}...
 
-The role of inhibitory mechanisms during covert verbal actions could be causally assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
-For instance, TMS can be used to "brake" these inhibitory mechanisms and "force" execution during motor imagery...
-\citep{angelini_motor_2015, angelini_proactive_2016}...
-Third and finally, inhibition "deficits" in Tourette syndrom...
-Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics (Jackson et al., 2015).
+After reviewing evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes through which motor commands can be inhibited during motor imagery.
+First, motor inhibition can be integrated within the representation of the action to be produced internally, therefore no active inhibition would be involved during motor imagery (but see the last paragraph of the current section).
+Second, cerebral regions such as the supplementary motor area (SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may progressively weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}, in addition to modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
+More precisely, the pre-SMA and the rIFG may work together to send a stop signal in order to intercept the action process via the basal ganglia (subthalamic nucleus, STN), suppressing the output from the basal ganglia and resulting in inhibitory effects on the primary motor cortex \cite{aron_reactive_2011} (cf.
+Figure \ref{fig:2}).\footnote{\cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the preSMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition.
+In their model, they suggest that the preSMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands.
+We may hypothesise that...
+during motor imagery.} Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.
+
+The role of inhibitory mechanisms during covert verbal actions could be assessed in several ways.
+First, their causal role during motor imagery and covert verbal actions could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
+For instance, TMS coud be used to "brake" these inhibitory mechanisms and "force" execution during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
+Second, the role of inhibitory mechanisms during covert verbal actions could be examined in a population with well-identified inhibitory deficits.
+For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}.
 Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia).
-Ganos et al.
-(2014)...
-performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls.
-However, they observed that the pattern of cerebral activity was different across patients and healthy controls.
-In their review, Jackson et al.
-(2015) suggested that increased control over motor outputs is brought about by local increases in GABAergic “tonic” inhibition within re- gions such as the SMA, leading to localised reductions in the gain of motor excitability.
-Moreover, they also reported a reduced short-interval intracortical inhibition (SICI) in patients with TS, a phenomenon that has been shown to be involved in response inhibition during motor imagery \citep{neige_unravelling_2020}...
+\cite{ganos_action_2014} have showed that the behavioural performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls.
+In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought about by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
+For these reasons, comparing the neural implementation of inhibitory mechanisms during covert verbal actions in patients with TS and healthy controls may shed light on the role and flexibility of these mechanisms and may lead to applied outcomes in the care of motor and verbal tics.
 
-The role of the primary motor cortex and the emission of motor commands during covert speech production has been debated.
+Whether covert speech production is accompanied by the emission of motor commands that are subsequently inhibited has been the matter of debate.
 It has been suggested that the primary motor cortex could be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}.
-However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned/regulated/monitored".
+However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned/regulated/monitored" \citep[see also][]{scheil_motor_2018}.
 In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level.
 What cognitive and neural mechanisms operate in order to maintain this activity under the threshold?
-In this section, we provided empirical arguments in favour of the "active inhibition hypothesis", but proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.
+In this section, we provided empirical arguments in favour of the "active inhibition hypothesis".
+Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.
 
@@
 Vygotsky observed, as Piaget before, that egocentric or "private" speech tends to be internalised during child development.
-\cite{fernyhough_alien_2004} extended this model...
-What if speech internalisation was related to the development of inhibitory abilities?
-The idea of speech internalisation and development of inhibition...
+\cite{fernyhough_alien_2004} extended this model with four levels (stages) of internalisation: external dialogue, private speech, expanded inner speech and condensed inner speech.
+These levels represent stages of development but also defines movements between levels (i.e., how we go from overt to covert speech and conversely).
+The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}.
+Therefore, producing speech covertly crucially depends on successfully inhibiting speech production at several levels (e.g., speech movements).
+We formulate the hypothesis that the progressive internalisation of speech during childhood may be related to the development of inhibitory abilities.
 
-These ideas could be assessed experimentally in several ways.
+This idea could be assessed in several ways.
 First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years).
-We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage...
-\cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old)...
-Second, the hypothesised co-development of motor imagery and response inhibition abilities could be assessed by looking at the learning of novel actions...
-learning a music instrument...
+We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage.
+\cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old).
+This suggests that inhibitory control may play a special role when speech is being internalised, but its role may weaken with expertise.
+This is congruent with the greater reliance on associative mechanisms with expertise, as discussed previously.
 
-\section{Discussion}
+Second, the hypothesised co-development of motor imagery and response inhibition abilities could be assessed by examining how novel actions are internalised in adults.\footnote{While keeping in mind the obvious limitation that the child mind is not equivalent to the adult mind, nor is it equivalent to a smaller version of the adult mind.
+Nevertheless, examining the development of novel imagined actions in adults avoids the contamination of the process of interest (imagined action) by developmental confounds.} For instance, Let’s consider the analogy between speaking and playing a music instrument (e.g., playing the piano).
+Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action.
+Therefore, it seems that (from a certain level of analysis), the act of speech can be paralleled with the act of playing an instrument in that it consists in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedbacks (e.g., kinaesthetic, auditory) for the agent.
+This analogy suggests that we might be able to study the development of internal models responsible for the sensory experience accompanying imagined actions in the adult mind (e.g., when an individual is learning either a novel music instrument or a new language with speech sounds that are not present in his/her native language).
+By examining the development of novel imagined actions in the adult mind and by using motor interference (e.g., articulatory suppression) procedures, we might gain new insights about the internalisation of speech during childhood.
+
+\section{Conclusions}
 
@@
 This led us to a discussion of two main themes.
-First, we discussed two mechanisms that may be used to provide the sensory (auditory) content of covert verbal actions, and how their respective involvement may be constrained by the available computational resources.
+First, we discussed two mechanisms that may be used to provide the sensory content of covert verbal actions, and how their respective involvement may be constrained by the available computational resources.
 Second, we asked how it is possible for motor imagery not to lead to motor execution.
@@
 
-Regarding neural origin of the sensory experience of covert verbal actions, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process.
-We suggested that the balance between these two mechanisms, in addition to the task instructions (which may prompt different forms of covert speech), may also be determined by the available computational resources (or equivalently, the computational cost of the task, with novel or more difficult tasks being more costly).
+Regarding the neural origin of the sensory experience of covert verbal actions, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process.
+We suggested that the balance between these two mechanisms, in addition to the task instructions (which may prompt different forms of covert speech), may also be determined by the available computational resources for (or equivalently, the computational cost of) the task, with novel or more difficult tasks being more costly.
 More precisely, novel or more difficult tasks are expected to rely more on the motor-simulation mechanisms whereas well-known and/or easy tasks may rely more on a "memoised version" of the motor simulation: the memory-retrieval prediction stream.
@@
 We related the development of response inhibition abilities in childhood development with the purported internalisation of private speech around the same period.
-From the response inhibition perspective, the internalisation of speech from overt to covert speech may essentially be considered as "learning not to produce speech" (i.e., learning pairs of internal models that will be used to simulate speech motor-to-sensory mappings while not executing speech).
+From the response inhibition perspective, the internalisation of speech from overt to covert speech may essentially be considered as "learning not to produce speech".
 
-Taken together, these propositions pave the way for several lines of research that should consolidate our understanding of covert speech, covert verbal actions, and motor imagery more generally...
+Taken together, these propositions pave the way for several lines of research that should consolidate our understanding of the relations between the production and perception systems.
+Several outstanding questions remain.
+Amongst others...
 

### 2021-09-15 manuscript.tex
New structure focused on covert speech and motor inhibition

@@
 \usepackage[onehalfspacing]{setspace}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Create explanation Box environment %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{tcolorbox}
+\tcbuselibrary{skins,breakable}
+
+\newtcolorbox[auto counter, number within = chapter, number freestyle = {\noexpand\thechapter.\noexpand\arabic{\tcbcounter}}]{mybox}[2][]{%
+    enhanced,
+    fonttitle = \bfseries,
+    title = Box~1: #2,
+    #1
+    }
 
@@
 
-\title[Covert verbal actions]{What covert verbal actions tell us about the interplay between language, action, and perception}
+\title[Motor inhibition and covert speech]{The role of motor inhibition during covert speech production}
+
+% Alternative title: Does covert speech production imply the motor inhibition of overt speech acts?
 
@@
 
-\noindent Motor imagery is accompanied by a subjective multisensory experience with auditory, visual, and kinaesthetic components.
-An influential hypothesis states that these sensory percepts result from a simulation of the corresponding motor action that relies on the same internal models recruited for the control of overt actions.
-A significant consequence of this hypothesis is that the sensory experience of covert actions would be continuously shaped by sensorimotor interactions with the environment.
+\noindent Covert speech is accompanied by a subjective multisensory experience with auditory and kinaesthetic components.
+An influential hypothesis states that these sensory percepts result from a simulation of the corresponding motor action that relies on the same internal models recruited for the control of overt speech.
+A significant consequence of this hypothesis is that the sensory experience of covert speech would be continuously shaped by sensorimotor interactions with the environment.
 However, the precise computations required by these internal models and their neural implementation remain unclear.
 Moreover, this simulationnist view raises the question of how it is possible to imagine actions without executing them.
-In this perspective, we focus on covert verbal actions such as covert speech, writing, or typing, as an exciting case study to help understanding the interplay between language, motor control, and perceptual processes.
+In this perspective, we focus on covert speech as an exciting case study to help understanding the interplay between language, motor control, and perceptual processes.
 
@@
 \tiny
- \keyFont{\section{Keywords:} motor imagery, motor simulation, motor control, response inhibition, covert speech} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+ \keyFont{\section{Keywords:} covert speech, inner speech, motor imagery, motor simulation, motor control, response inhibition} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
 \end{abstract}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Succinct introduction in four paragraphs.
-% ------------------------------------------
-% 1) Introduction of motor imagery
-% 2) Covert verbals actions
-% 3) Relating 1) and 2) to the thematic of the research topic
-% 4) Aims of the present perspective
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% Broadly construed, motor imagery can be defined as the mental process by which one rehearses an action without engaging in the physical movements involved in this particular action
-
-% Mentally anticipating or rehearsing verbal actions allows us to become better at performing them \citep[e.g.,][]{toth_does_2020}, to explore/practise novel situations \citep{babar}, or to rehearse past situations \citep{babar}.
-
 The ability to mentally examine our thoughts is central to our subjective experience.
@@
 Because speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
-Therefore, a parallel can be drawn between covert speech (also known as \textit{inner speech} or \textit{speech imagery}) \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018} and other forms of covert verbal actions such as covert writing or covert typing and, more generally, other imagined actions.
+Therefore, a parallel can be drawn between covert speech, also known as \textit{inner speech} or \textit{speech imagery} \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}, and other forms of covert verbal actions such as covert writing or covert typing and, more generally, other imagined actions (motor imagery).
 
@@
 
-In this perspective, we examine some theoretical and experimental consequences of considering covert verbal actions as other forms of imagined actions.
+The motor simulation theory \citep{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001} of motor imagery postulates the existence of a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism.
+In short, covert actions would rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited \citep{oshea_does_2017}.
+In this perspective, we examine some theoretical and experimental consequences that emerge when considering covert speech as inhibited overt speech.
 We explore two main themes.
-First, we discuss the plausible origins of the multisensory (e.g., auditory, kinaesthetic) content of covert verbal actions.
-Second, we discuss the under-explored role of inhibitory mechanisms during motor imagery and covert verbal actions, more specifically.
+First, we discuss the under-explored role of inhibitory mechanisms during covert speech production and their plausible neural implementation.
+Second, we consider how different forms of covert speech may involve inhibitory mechanisms differently.
 By bridging together recent results from the motor imagery, motor inhibition, and covert speech literature, we highlight some novel and possibly fruitful lines of research.
+
+\section{Covert verbal actions as inhibited verbal actions}
+
+The proposal that overt and covert actions share common neural circuits is faced with a serious problem.
+If the neural circuits used for the control of overt actions are reused for covert actions, how can covert actions not lead to execution?
+This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
+In the following, we briefly summarise the evidence in favour of the view of covert speech as inhibited overt speech.
+Then, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms.
+Finally, we relate this view to the presumed progressive internalisation of speech during childhood.
+
+\subsection{Cognitive mechanisms and neural implementation}
+
+First and foremost, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}.
+Here, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
+To be more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, specificity.
+Inhibition can be employed with more or less intentionality (intentional vs.
+reactive inhibition), it can planned ahead or employed in the moment (early vs.
+late inhibition), and it can be more or less specifically (global inhibition versus effector-specific or action-specific inhibition).
+
+Crucially, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements), proactive (i.e., planned ahead), and possibly global form of response inhibition.
+Notice however that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature, because while doing motor imagery, participants are not explicitly asked not to produce an action \citep{guillot_imagining_2012}.
+Instead, they are asked to produce the action \textit{covertly}, which (only implicitly) implies that it should not be executed overtly.
+Using an action mode (overt vs.
+covert) switching paradigm, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have showed that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{scheil_motor_2018}.
+
+% further confirmed that both global and effector-specific inhibition may be at play during imagined (hand) movements and suggested that these two types of inhibition may work together and compensate for each other...
+\cite{schwoebel_man_2002}...
+
+After reviewing evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes through which motor commands can be inhibited during motor imagery.
+First, motor inhibition can be integrated within the representation of the action to be produced internally, therefore no active inhibition would be involved during motor imagery (but see the last paragraph of the current section).
+Second, cerebral regions such as the supplementary motor area (SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may progressively weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}, in addition to modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
+More precisely, the pre-SMA and the rIFG may work together to send a stop signal in order to intercept the action process via the basal ganglia (subthalamic nucleus, STN), suppressing the output from the basal ganglia and resulting in inhibitory effects on the primary motor cortex \citep{aron_reactive_2011} (cf.
+Figure \ref{fig:2}).\footnote{\cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the preSMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition.
+In their model, they suggest that the preSMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands.
+Whether this functional dissociation is preserved in motor imagery remains an open question.} Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.
+
+The cause role of inhibitory mechanisms during motor imagery and covert speech could be assessed in several ways.
+First, it could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
+For instance, TMS could be used to "brake" these inhibitory mechanisms and "force" or facilitate execution during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
+Second, the role of inhibitory mechanisms during covert verbal actions could be examined in a population with well-identified inhibitory deficits.
+For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}.
+Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia).
+\cite{ganos_action_2014} have showed that the behavioural performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls.
+In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought about by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
+For these reasons, comparing the neural implementation of inhibitory mechanisms during covert verbal actions in patients with TS and healthy controls may shed light on the role and flexibility of these mechanisms and may lead to applied outcomes in the care of motor and verbal tics.
+
+Whether covert speech production is accompanied by the emission of motor commands that are subsequently inhibited has been the matter of debate.
+It has been suggested that the primary motor cortex could be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}.
+However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned/regulated/monitored" \citep[see also][]{scheil_motor_2018}.
+In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level.
+What cognitive and neural mechanisms operate to maintain this activity under the threshold?
+In this section, we provided empirical arguments in favour of the "active inhibition hypothesis".
+Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.
+
+\subsection{Covert speech development: Learning not to produce speech}
+
+\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that covert speech matures from overt speech.
+\cite{vygotsky_thought_1934} then prominently formulated the idea that covert speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood.
+Vygotsky observed, as Piaget before, that egocentric or "private" speech tends to be internalised during child development.
+\cite{fernyhough_alien_2004} extended this model with four levels (stages) of internalisation: external dialogue, private speech, expanded inner speech and condensed inner speech.
+These levels represent stages of development but also defines movements between levels (i.e., how we go from overt to covert speech and conversely).
+The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}.
+Therefore, producing speech covertly crucially depends on successfully inhibiting speech production at several levels.
+We formulate the hypothesis that the progressive internalisation of speech during childhood may be related to the development of inhibitory abilities.
+
+This idea could be assessed in several ways.
+First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years).
+We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at this age.
+\cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old).
+This suggests that inhibitory control may play a special role when speech is being internalised, but its role may weaken with expertise.
+This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
+
+% This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise (e.g., Tarr and Pinker, 1989;Jolicoeur, 1985)
+
+Second, the hypothesised co-development of motor imagery and response inhibition abilities could be assessed by examining how novel actions are internalised in adults.\footnote{While keeping in mind the obvious limitation that the child mind is not equivalent to the adult mind, nor is it equivalent to a smaller version of the adult mind.
+Nevertheless, examining the development of novel imagined actions in adults avoids the contamination of the process of interest (imagined action) by developmental confounds.} For instance, Let’s consider the analogy between speaking and playing a music instrument (e.g., playing the piano).
+Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action.
+Therefore, it seems that (from a certain level of analysis), the act of speech can be paralleled with the act of playing an instrument in that it consists in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedbacks (e.g., kinaesthetic, auditory) for the agent.
+This analogy suggests that we might be able to study the development of internal models responsible for the sensory experience accompanying imagined actions in the adult mind (e.g., when an individual is learning either a novel music instrument or a new language with speech sounds that are not present in his/her native language).
+By examining the development of novel imagined actions in the adult mind and by using motor interference (e.g., articulatory suppression) procedures, we might gain new insights about the internalisation of speech during childhood.
 
@@
 How does motor learning shape these sensory percepts?
-In other words, how do the motor and perceptual system interact during covert verbal actions?
-In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert verbal actions and their respective involvement in different forms of covert speech.
-In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of covert verbal actions, namely, the imagery of totally novel (i.e., never executed) verbal actions.
+In other words, how do the motor and perceptual system interact during covert speech?
+In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert speech and their respective involvement in different forms of covert speech.
+In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of covert speech, namely, the imagery of totally novel (i.e., never executed) speech acts.
 
@@
 In other words, covert speech is accompanied by a sensory experience that "feels like" hearing speech.
-In this section, we discuss the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, a theoretical account of the mechanisms leading to the generation of such auditory percepts during covert speech, while noticing that these mechanisms could be extended to other verbal actions as well.
+In this section, we discuss the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, a theoretical account of the mechanisms leading to the generation of such auditory percepts during covert speech production.
+
+% while noticing that these mechanisms could be extended to other verbal actions as well.
 
@@
 In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of either one of these mechanisms is the computational cost of (or equivalently, the computational resources available for) each alternative.
-To clarify, we borrow the concept of memoisation as applied to cognition and mental imagery by \cite{dasgupta_memory_2021}.\footnote{Memoisation is a programming technique used to speed-up algorithms or programs.
-It avoids redundant computation by storing computational results and reusing them later.
-When calling a function (where a function can be a motor primitive such as elevating the arm), the function call is intercepted by a memoiser that inspects the previous calls of a function and its outputs.
-If a function has already been called with the same input, then the previously computed output is retrieved and reused.} In their view, memory can be considered as a computational resource to facilitate computational reuse through memoisation.
+To clarify, we borrow the concept of memoisation as applied to cognition and mental imagery by \cite{dasgupta_memory_2021} (cf.
+Box \ref{memoisation}).
+In their view, memory can be considered as a computational resource to facilitate computational reuse through memoisation.
 In the context of motor and speech imagery, memoisation can be seen in the greater reliance on memory (vs.
 motor processes) in the course of learning, where motor-to-sensory mappings are (party or completely) retrieved from memory, instead of being computed again every time.
+
+% \vspace{5mm}
+
+\begin{mybox}[label = memoisation]{Memoisation}
+
+Memoisation is a programming technique used to speed-up algorithms or programs.
+It avoids redundant computation by storing computational results and reusing them later.
+When calling a function (where a function can be a motor primitive), the function call is intercepted by a \textit{memoiser} that inspects the previous calls of a function and its outputs.
+If a function has already been called with the same input, then the previously computed output is retrieved and reused.
+
+\end{mybox}
 
@@
 This idea is supported by several studies showing a greater increase in facial EMG activity during the reading of difficult text or while performing difficult mental arithmetic tasks as compared to easier tasks \citep[e.g.,][]{faaborg-andersen_electromyography_1958, sokolov_inner_1972}, suggesting a greater involvement of the speech motor system \citep[and/or a lesser involvement of inhibitory mechanisms, see also the discussion in][]{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
-This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
+This is congruent with the greater reliance on associative mechanisms with greater expertise, as discussed previously.
 
-% Memoisation: avoid redundant computation by storing computational results and reusing them later...
-functions call are intercepted with by a memoiser the inspects the previous calls of a function and its outputs.
-If a function has already been called with the same input, then the previously computed output is retrieved and reused...
-memoisation can be made more flexible (generalisable) by using \textit{interpolation} between cached outputs...
-for instance, in the context of motor control, reaching a goal (e.g., a cup of tea) can be decomposed in motor primitives, where input-output mapping can be retrieved from a memo table and/or interpolated from sufficiently similar stored mappings...
-or as put by \cite{dasgupta_memory_2021}, the "shift from algorithm to memory"...
-this shift is consistent with studies showing a lesser involvement of the motor system for well known imagined actions...
-Depending on whether the task needs to form "precise" sensory representations and whether we have the time resources to do it...
-Training studies also suggest that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
+% This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
 
-\subsection{The motor imagery of novel actions}
+\subsection{The covert production of novel verbal actions}
 
-If, as suggested in the previous section, the sensory content of covert verbal actions is (at least in some situations) provided by a motor simulation process, how can we imagine totally novel (i.e., never executed) actions?
+If, as suggested in the previous section, the sensory content of covert speech is, at least in some situations, provided by a motor simulation process, how can we imagine totally novel actions?
 Broadly speaking, the simulationnist framework suggests that the multisensory experience of motor imagery results from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions \citep[e.g.,][]{jeannerod_representing_1994}.
 In other words, internal models developed for the control of actions would then be used to simulate the sensory consequences of covert actions.
-Crucially, these internal models are generative models, which means that they can be used to compute (i.e., predict) the sensory consequences of any action that can be parsed as a \citep[possibly supramodal, see][]{loevenbruck_cognitive_2018} goal to an inverse internal model.
+Crucially, these internal models are generative models, which means that they can be used to compute or predict the sensory consequences of any action that can be parsed as a \citep[possibly supramodal, see][]{loevenbruck_cognitive_2018} goal to an inverse internal model.
 In other words, this framework makes it possible for novel actions to be simulated internally.\footnote{\cite{mulder_role_2004} assessed whether the mental practice of a totally novel movement (abduction of the big toe of the dominant right foot) resulted in better overt execution over the course of several weeks of practice.
@@
 For instance, when asked to imagine playing table tennis, a tennis player may overestimate movements' amplitude and duration.
-Translated to speech production, this prediction could be assessed by asking participants to imagine a novel action and subsequently checking whether this improves the execution of an "intermediate" novel action in the articulatory space.
+Translated to speech production, this prediction could be assessed by asking participants to imagine a novel verbal action and subsequently checking whether this improves the execution of an "intermediate" novel action in the articulatory space.
 The same logic could be applied to the covert production of speech with someone else's voice.
 How can we imagine speaking with the voice of our relatives?
-If it is based on simulators (i.e., on internal models), then the covert production of speech with someone else's voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems.
-In other words, the subjective auditory sensation of covert speech with someone else's voice should be situated in a somehow intermediate (i.e., between the acoustic properties of our own voice and the acoustic properties of someone else voice) location in the auditory (e.g., formantic) space.
-
-% This prediction could be assessed experimentally by...
-the prediction-by-simulation and the prediction-by-association accounts could be distinguished by constraining the motor system and assessing whether this influences the internal sensory representation of the produced speech.
-If it does...
+If it is based on simulators, then the covert production of speech with someone else's voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems.
+In other words, the subjective auditory sensation of covert speech with someone else's voice should be situated in a somehow intermediate (i.e., between the acoustic properties of our own voice and the acoustic properties of someone else voice) location in the auditory space.
 
 This prediction could be assessed experimentally by using the sensory attenuation effect observed during covert speech production.
-Auditory stimuli elicit an electrophysiological brain response (the auditory-evoked potential) with a characteristic N1 component.
-This N1 component has been shown to be reduced when the presentation of an auditory stimulus is synchronised with the self-production of a phonetically-matched vocalisation (an effect called N1-suppression).
-More interestingly, \cite{whitford_neurophysiological_2017} shown that the covert production of a phoneme also resulted in sensory attenuation (as assessed by N1-suppression) if the content of the imagined phoneme matched the content of the audible phoneme.
-Therefore, we could describe the subjective auditory sensation of covert speaking with someone else’s voice by manipulating the acoustic (e.g., formantic) properties of the auditory stimulus that is presented to the participant to find the stimulus that produces the greatest sensory attenuation (as assessed by N1-suppression).
+Auditory stimuli elicit an electrophysiological brain response with a characteristic N1 component.
+This N1 component has been shown to be reduced when the presentation of an auditory stimulus is synchronised with the self-production of a phonetically-matched vocalisation, an effect called N1-suppression.
+More interestingly, \cite{whitford_neurophysiological_2017} have shown that the covert production of a phoneme also resulted in sensory attenuation, as assessed by N1-suppression, when the content of the imagined phoneme matched the content of the audible phoneme.
+Therefore, we could describe the subjective auditory sensation of covertly speaking with someone else’s voice by manipulating the acoustic properties of the auditory stimulus that is presented to the participant to find the stimulus that produces the greatest sensory attenuation, as assessed by N1-suppression.
 In other words, sensory attenuation should be the strongest when it matches the auditory representation of the speaker.
-If the auditory percepts generated when covert speaking with the voice of someone else is "constrained" by our own motor system, then this point of greatest sensory attenuation should occur in an intermediate location in the feature (e.g., formantic) space.
-
-\section{Covert verbal actions as inhibited verbal actions}
-
-The proposal that overt and covert actions share common neural circuits is faced with a serious problem.
-If the neural circuits used for the control of overt actions are reused for covert actions, how can covert actions not lead to execution?
-This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
-In the following, we briefly summarise the evidence in favour of the view of covert verbal actions as inhibited verbal actions.
-Then, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms.
-Finally, we relate this view to the presumed progressive internalisation of speech during childhood.
-
-\subsection{Cognitive mechanisms and neural implementation}
-
-First and foremost, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}.
-Here, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
-To be more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, specificity.
-Inhibition can be employed with more or less intentionality (intentional vs.
-reactive inhibition), it can planned ahead or employed in the moment (early vs.
-late inhibition), and it can be more or less specifically (global inhibition versus effector-specific or action-specific inhibition).
-
-With regards to covert verbal actions specifically, we hypothesise that they involve an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition.
-Notice however that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature, in the sense that while doing motor imagery, participants are not explicitly asked to not produce an action \citep{guillot_imagining_2012}.
-Instead, they are asked to produce the action \textit{covertly}, which (only implicitly) implies that it should not be executed overtly.
-Using an action mode (overt vs.
-covert) switching paradigm, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have showed that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{scheil_motor_2018}.
-
-% further confirmed that both global and effector-specific inhibition may be at play during imagined (hand) movements and suggested that these two types of inhibition may work together and compensate for each other...
-\cite{schwoebel_man_2002}...
-
-After reviewing evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes through which motor commands can be inhibited during motor imagery.
-First, motor inhibition can be integrated within the representation of the action to be produced internally, therefore no active inhibition would be involved during motor imagery (but see the last paragraph of the current section).
-Second, cerebral regions such as the supplementary motor area (SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may progressively weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}, in addition to modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
-More precisely, the pre-SMA and the rIFG may work together to send a stop signal in order to intercept the action process via the basal ganglia (subthalamic nucleus, STN), suppressing the output from the basal ganglia and resulting in inhibitory effects on the primary motor cortex \cite{aron_reactive_2011} (cf.
-Figure \ref{fig:2}).\footnote{\cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the preSMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition.
-In their model, they suggest that the preSMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands.
-We may hypothesise that...
-during motor imagery.} Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.
-
-The role of inhibitory mechanisms during covert verbal actions could be assessed in several ways.
-First, their causal role during motor imagery and covert verbal actions could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
-For instance, TMS coud be used to "brake" these inhibitory mechanisms and "force" execution during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
-Second, the role of inhibitory mechanisms during covert verbal actions could be examined in a population with well-identified inhibitory deficits.
-For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}.
-Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia).
-\cite{ganos_action_2014} have showed that the behavioural performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls.
-In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought about by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
-For these reasons, comparing the neural implementation of inhibitory mechanisms during covert verbal actions in patients with TS and healthy controls may shed light on the role and flexibility of these mechanisms and may lead to applied outcomes in the care of motor and verbal tics.
-
-Whether covert speech production is accompanied by the emission of motor commands that are subsequently inhibited has been the matter of debate.
-It has been suggested that the primary motor cortex could be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}.
-However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned/regulated/monitored" \citep[see also][]{scheil_motor_2018}.
-In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level.
-What cognitive and neural mechanisms operate in order to maintain this activity under the threshold?
-In this section, we provided empirical arguments in favour of the "active inhibition hypothesis".
-Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.
-
-\subsection{Covert speech development: Learning not to produce speech}
-
-\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that covert speech matures from overt speech.
-\cite{vygotsky_thought_1934} then prominently formulated the idea that covert speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood.
-Vygotsky observed, as Piaget before, that egocentric or "private" speech tends to be internalised during child development.
-\cite{fernyhough_alien_2004} extended this model with four levels (stages) of internalisation: external dialogue, private speech, expanded inner speech and condensed inner speech.
-These levels represent stages of development but also defines movements between levels (i.e., how we go from overt to covert speech and conversely).
-The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}.
-Therefore, producing speech covertly crucially depends on successfully inhibiting speech production at several levels (e.g., speech movements).
-We formulate the hypothesis that the progressive internalisation of speech during childhood may be related to the development of inhibitory abilities.
-
-This idea could be assessed in several ways.
-First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years).
-We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at at this stage.
-\cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old).
-This suggests that inhibitory control may play a special role when speech is being internalised, but its role may weaken with expertise.
-This is congruent with the greater reliance on associative mechanisms with expertise, as discussed previously.
-
-Second, the hypothesised co-development of motor imagery and response inhibition abilities could be assessed by examining how novel actions are internalised in adults.\footnote{While keeping in mind the obvious limitation that the child mind is not equivalent to the adult mind, nor is it equivalent to a smaller version of the adult mind.
-Nevertheless, examining the development of novel imagined actions in adults avoids the contamination of the process of interest (imagined action) by developmental confounds.} For instance, Let’s consider the analogy between speaking and playing a music instrument (e.g., playing the piano).
-Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action.
-Therefore, it seems that (from a certain level of analysis), the act of speech can be paralleled with the act of playing an instrument in that it consists in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedbacks (e.g., kinaesthetic, auditory) for the agent.
-This analogy suggests that we might be able to study the development of internal models responsible for the sensory experience accompanying imagined actions in the adult mind (e.g., when an individual is learning either a novel music instrument or a new language with speech sounds that are not present in his/her native language).
-By examining the development of novel imagined actions in the adult mind and by using motor interference (e.g., articulatory suppression) procedures, we might gain new insights about the internalisation of speech during childhood.
+If the auditory percepts generated when covertly speaking with the voice of someone else is "constrained" by our own sensory and motor systems, then this point of greatest sensory attenuation should occur in an intermediate location in the feature space.
 
@@
 
-To sum up, we explored some of the theoretical and experimental perspectives that emerge when considering covert verbal actions as other forms of imagined actions.
+To sum up, we explored some of the theoretical and experimental consequences that emerge when considering covert speech production as inhibited overt speech production.
 This led us to a discussion of two main themes.
-First, we discussed two mechanisms that may be used to provide the sensory content of covert verbal actions, and how their respective involvement may be constrained by the available computational resources.
-Second, we asked how it is possible for motor imagery not to lead to motor execution.
-To sketch an answer to these questions, we connected results from the motor imagery, motor inhibition, and inner speech research traditions.
+First, we asked how it is possible for covert speech production not to lead to overt speech production.
+Second, we discussed two mechanisms that may be used to provide the sensory content of covert speech, and how their respective involvement may be constrained by the available computational resources.
+To sketch an answer to these questions, we connected results from the motor imagery, motor inhibition, and covert speech research traditions.
 
-Regarding the neural origin of the sensory experience of covert verbal actions, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process.
-We suggested that the balance between these two mechanisms, in addition to the task instructions (which may prompt different forms of covert speech), may also be determined by the available computational resources for (or equivalently, the computational cost of) the task, with novel or more difficult tasks being more costly.
-More precisely, novel or more difficult tasks are expected to rely more on the motor-simulation mechanisms whereas well-known and/or easy tasks may rely more on a "memoised version" of the motor simulation: the memory-retrieval prediction stream.
-
-Regarding the role of general-purpose inhibitory mechanisms during the production of covert verbal actions, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and we summarised some propositions from this literature.
+Regarding the role of general-purpose inhibitory mechanisms during the production of covert speech, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and we summarised some propositions from this literature.
 We related the development of response inhibition abilities in childhood development with the purported internalisation of private speech around the same period.
@@
 
-Taken together, these propositions pave the way for several lines of research that should consolidate our understanding of the relations between the production and perception systems.
+Regarding the neural origin of the sensory experience of covert speech, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process.
+We suggested that the balance between these two mechanisms, in addition to the task instructions (which may prompt different forms of covert speech), may also be determined by the available computational resources for (or equivalently, the computational cost of) the task, with novel or more difficult tasks being more costly.
+More precisely, novel or more difficult tasks are expected to rely more on the motor-simulation mechanisms whereas well-known and/or easy tasks may rely more on a "memoised version" of the motor simulation: the memory-retrieval prediction stream.
+Whereas the former mechanism should involve active inhibitory mechanisms, the latter should not.
+
+Taken together, these propositions pave the way for several lines of research that should consolidate our understanding of the relations between the speech production and perception systems.
 Several outstanding questions remain.
@@
 
-\color{blue}
+% \color{blue}
 
-The Author Contributions section is mandatory for all articles, including articles by sole authors.
+% The Author Contributions section is mandatory for all articles, including articles by sole authors.
 If an appropriate statement is not provided on submission, a standard one will be inserted during the production process.
@@
 
-\color{black}
+% \color{black}
 
-...
+Conceptualisation: all authors; Funding acquisition: LN; Supervision: UD, ML, AG, FXA; Writing - original draft: LN; Writing - review and editing: all authors.
 

### 2021-09-15 manuscript.tex
Minor updates

@@
 
-\newtcolorbox[auto counter, number within = chapter, number freestyle = {\noexpand\thechapter.\noexpand\arabic{\tcbcounter}}]{mybox}[2][]{%
+\newtcolorbox[auto counter]{mybox}[2][]{%
     enhanced,
@@
 
-% \linenumbers # commented out when sending the abstract
+% commented out when sending the abstract
+\linenumbers
 
@@
 
-\section{Covert verbal actions as inhibited verbal actions}
+\section{Covert speech production as inhibited overt speech production}
 
@@
 \end{center}
-\caption{Plausible neural implementation of the (cortical and subcortical) inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during motor imagery.
+\caption{Plausible implementation of the cortical and subcortical inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during covert speech production.
 The preSMA, right pIFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production.

### 2021-09-22 manuscript.tex
Updating the structure (focusing on the role of motor inhibition)

@@
 % Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
-\def\corrAuthor{Corresponding Author}
+\def\corrAuthor{Ladislas Nalborczyk}
 \def\corrEmail{ladislas.nalborczyk@univ-amu.fr}
@@
 Moreover, this simulationnist view raises the question of how it is possible to imagine actions without executing them.
-In this perspective, we focus on covert speech as an exciting case study to help understanding the interplay between language, motor control, and perceptual processes.
+In this perspective, we consider the role of motor inhibition during covert speech production.
+We suggest that considering covert speech as an inhibited form of overt speech maps naturally to the purported progressive internalisation of overt speech during childhood.
+However, we argue that the role of motor inhibition may differ widely across different forms of covert speech, and that this helps reconciling seemingly contradictory findings from the neuroimaging literature.
+
+% we focus on covert speech as an exciting case study to help understanding the interplay between language, motor control, and perceptual processes.
 
@@
 \tiny
- \keyFont{\section{Keywords:} covert speech, inner speech, motor imagery, motor simulation, motor control, response inhibition} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+ \keyFont{\section{Keywords:} covert speech, inner speech, motor imagery, motor simulation, motor control, motor inhibition} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
 \end{abstract}
@@
 In this perspective, we examine some theoretical and experimental consequences that emerge when considering covert speech as inhibited overt speech.
-We explore two main themes.
 First, we discuss the under-explored role of inhibitory mechanisms during covert speech production and their plausible neural implementation.
-Second, we consider how different forms of covert speech may involve inhibitory mechanisms differently.
+Second, we relate the maturation of inhibitory control during childhood with the progressive internalisation of overt speech.
+Third, we consider how the role of inhibitory mechanisms may differ across different forms of covert speech.
 By bridging together recent results from the motor imagery, motor inhibition, and covert speech literature, we highlight some novel and possibly fruitful lines of research.
@@
 In the following, we briefly summarise the evidence in favour of the view of covert speech as inhibited overt speech.
-Then, we outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms.
-Finally, we relate this view to the presumed progressive internalisation of speech during childhood.
+We outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms.
+Then, we relate this view to the presumed progressive internalisation of speech during childhood.
+Finally, we examine how the role of motor inhibition may differ across different forms of covert speech.
 
@@
 Here, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
-To be more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, specificity.
-Inhibition can be employed with more or less intentionality (intentional vs.
-reactive inhibition), it can planned ahead or employed in the moment (early vs.
-late inhibition), and it can be more or less specifically (global inhibition versus effector-specific or action-specific inhibition).
+To be more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, and specificity.
+Inhibition can be employed with more or less intentionality, from intentional to reactive inhibition, it can be planned ahead or employed in the moment (early vs.
+late inhibition) and can be applied to a specific action, a specific effector, or more globally, that is, to all actions and/or effectors.
 
-Crucially, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements), proactive (i.e., planned ahead), and possibly global form of response inhibition.
+Crucially, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition.
 Notice however that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature, because while doing motor imagery, participants are not explicitly asked not to produce an action \citep{guillot_imagining_2012}.
-Instead, they are asked to produce the action \textit{covertly}, which (only implicitly) implies that it should not be executed overtly.
+Instead, they are asked to produce the action \textit{covertly}, which implicitly implies that it should not be executed overtly.
 Using an action mode (overt vs.
@@
 In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought about by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
-For these reasons, comparing the neural implementation of inhibitory mechanisms during covert verbal actions in patients with TS and healthy controls may shed light on the role and flexibility of these mechanisms and may lead to applied outcomes in the care of motor and verbal tics.
+For these reasons, comparing the neural implementation of inhibitory mechanisms during covert speech in patients with Tourette syndrome and healthy controls may shed light on the role and flexibility of these mechanisms.
 
-Whether covert speech production is accompanied by the emission of motor commands that are subsequently inhibited has been the matter of debate.
-It has been suggested that the primary motor cortex could be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}.
+% and may lead to applied outcomes in the care of motor and verbal tics.
+
+Whether covert speech production is accompanied by the emission of motor commands that are subsequently inhibited has been the matter of debate \citep[e.g.,][]{geva_inner_2018}.
+It has been suggested that the primary motor cortex would be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}.
 However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned/regulated/monitored" \citep[see also][]{scheil_motor_2018}.
@@
 \cite{fernyhough_alien_2004} extended this model with four levels (stages) of internalisation: external dialogue, private speech, expanded inner speech and condensed inner speech.
-These levels represent stages of development but also defines movements between levels (i.e., how we go from overt to covert speech and conversely).
+These levels represent stages of development but also define movements between levels (i.e., how we go from overt to covert speech and conversely).
 The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}.
@@
 
-\section{The interplay between motor control and cognition}
+% \section{The interplay between motor control and cognition}
 
-Where does the sensory content of covert verbal actions come from?
+% \subsection{Where does this sensory content come from?}
+
+% Where does the sensory content of covert verbal actions come from?
 How does motor learning shape these sensory percepts?
@@
 
-\subsection{Where does this sensory content come from?}
+\subsection{Does covert speech always involve motor inhibition?}
 
-The production of covert speech is often (although not always and not for everyone) accompanied by the feeling of hearing speech \cite{hurlburt_investigating_2011}.
+The production of covert speech is often, although not always and not for everyone, accompanied by the feeling of hearing speech \cite{hurlburt_investigating_2011}.
 In other words, covert speech is accompanied by a sensory experience that "feels like" hearing speech.
-In this section, we discuss the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, a theoretical account of the mechanisms leading to the generation of such auditory percepts during covert speech production.
+However, covert speech may also be accompanied by the feeling of producing speech.
+These two facets of covert speech are characterised by different phenomenological experiences.
+In this section, we discuss how these two forms of covert speech may require motor inhibition to a different extent, in the light of the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, a theoretical account of the mechanisms leading to the generation of sensory percepts during covert speech production.
 
@@
 In their view, memory can be considered as a computational resource to facilitate computational reuse through memoisation.
-In the context of motor and speech imagery, memoisation can be seen in the greater reliance on memory (vs.
-motor processes) in the course of learning, where motor-to-sensory mappings are (party or completely) retrieved from memory, instead of being computed again every time.
+In the context of motor and speech imagery, memoisation can be seen in the greater reliance on memory in the course of learning, where motor-to-sensory mappings are partially or completely retrieved from memory, instead of being computed again every time.
 
@@
 For instance, we hypothesise that novel and/or difficult tasks (which are both computationally more expensive, ceteris paribus) may rely more on the simulation mechanism, whereas well known and/or easy tasks may rely more on associative mechanisms.
-This idea is supported by several studies showing a greater increase in facial EMG activity during the reading of difficult text or while performing difficult mental arithmetic tasks as compared to easier tasks \citep[e.g.,][]{faaborg-andersen_electromyography_1958, sokolov_inner_1972}, suggesting a greater involvement of the speech motor system \citep[and/or a lesser involvement of inhibitory mechanisms, see also the discussion in][]{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
+This idea is supported by several studies showing a greater increase in facial EMG activity during the reading of difficult text or while performing difficult mental arithmetic tasks as compared to easier tasks \citep[e.g.,][]{faaborg-andersen_electromyography_1958, sokolov_inner_1972}, suggesting a greater involvement of the speech motor system.
+Alternatively, these results may suggest a lesser involvement of inhibitory mechanisms \citep[see also the discussion in][]{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
 This is congruent with the greater reliance on associative mechanisms with greater expertise, as discussed previously.
+
+To sum up, whereas inner speaking may involve active inhibition of motor commands, inner hearing may not (or to a lesser extent).
+These disparities between inner speaking and inner hearing may explain the large variety of results when looking at the cerebral correlates of covert speech production \citep[as reviewed for instance in][]{geva_inner_2018}.
+Different forms of covert speech, that may vary in condensation, dialogicality, or intentionality \citep{grandchamp_condialint_2019}, may require inhibitory control to a different extent, from no inhibition at all for condensed forms of covert speech to active inhibition of motor commands for fully expanded forms of covert speech.
 
@@
 
-\subsection{The covert production of novel verbal actions}
+% \subsection{The covert production of novel verbal actions}
 
-If, as suggested in the previous section, the sensory content of covert speech is, at least in some situations, provided by a motor simulation process, how can we imagine totally novel actions?
+% If, as suggested in the previous section, the sensory content of covert speech is, at least in some situations, provided by a motor simulation process, how can we imagine totally novel actions?
 Broadly speaking, the simulationnist framework suggests that the multisensory experience of motor imagery results from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions \citep[e.g.,][]{jeannerod_representing_1994}.
@@
 
-A general prediction of this framework is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions.
+% A general prediction of this framework is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions.
 For instance, when asked to imagine playing table tennis, a tennis player may overestimate movements' amplitude and duration.
@@
 
-This prediction could be assessed experimentally by using the sensory attenuation effect observed during covert speech production.
+% This prediction could be assessed experimentally by using the sensory attenuation effect observed during covert speech production.
 Auditory stimuli elicit an electrophysiological brain response with a characteristic N1 component.
@@
 
-% Summary of the main proposition (i.e., considering covert verbal actions as inhibited verbal actions) and its consequences on the relation between perception and action + theoretical and experimental perspectives.
-
-To sum up, we explored some of the theoretical and experimental consequences that emerge when considering covert speech production as inhibited overt speech production.
-This led us to a discussion of two main themes.
+% This led us to a discussion of two main themes.
 First, we asked how it is possible for covert speech production not to lead to overt speech production.
@@
 
+We explored some of the theoretical and experimental consequences that emerge when considering covert speech production as inhibited overt speech production.
+To this end,  we connected results from the motor imagery, motor inhibition, and covert speech research traditions.
 Regarding the role of general-purpose inhibitory mechanisms during the production of covert speech, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and we summarised some propositions from this literature.
@@
 Regarding the neural origin of the sensory experience of covert speech, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process.
-We suggested that the balance between these two mechanisms, in addition to the task instructions (which may prompt different forms of covert speech), may also be determined by the available computational resources for (or equivalently, the computational cost of) the task, with novel or more difficult tasks being more costly.
+We suggested that the balance between these two mechanisms, in addition to the task instructions, which may prompt different forms of covert speech, may also be determined by the available computational resources for (or equivalently, the computational cost of) the task, with novel or more difficult tasks being more costly.
 More precisely, novel or more difficult tasks are expected to rely more on the motor-simulation mechanisms whereas well-known and/or easy tasks may rely more on a "memoised version" of the motor simulation: the memory-retrieval prediction stream.
-Whereas the former mechanism should involve active inhibitory mechanisms, the latter should not.
+Whereas the former mechanism should involve active inhibitory mechanisms, the latter should not, as there should be no (or less) motor commands to inhibit.
+Crucially, different forms of covert speech, varying in condensation, dialogicality, or intentionality, may require inhibitory control to a different extent.
 
-Taken together, these propositions pave the way for several lines of research that should consolidate our understanding of the relations between the speech production and perception systems.
+Taken together, these propositions pave the way for several lines of research that should consolidate our understanding of the relations between overt and covert speech production.
 Several outstanding questions remain.
-Amongst others...
+Amongst others, how does the development of inhibitory control relate with the progressive internalisation of speech during childhood?
+How individual and situational constraints shape the role of motor inhibition during covert speech production?
+How is covert speech affected by poor or degraded inhibitory control?
+Can we experimentally "force" (e.g., using neurostimulation) the externalisation of speech in adults?
+The use of neurostimulation and the comparison between healthy controls and patients with well-identified inhibitory deficits could help refine the involvement of these inhibitory mechanisms during covert speech production, which may lead to applied outcomes in the care of motor and verbal tics.
 

### 2021-09-22 manuscript.tex
Minor changes to abstract

@@
 We suggest that considering covert speech as an inhibited form of overt speech maps naturally to the purported progressive internalisation of overt speech during childhood.
-However, we argue that the role of motor inhibition may differ widely across different forms of covert speech, and that this helps reconciling seemingly contradictory findings from the neuroimaging literature.
+However, we argue that the role of motor inhibition may differ widely across different forms of covert speech, and that considering this variety helps reconciling seemingly contradictory findings from the neuroimaging literature.
 

### 2021-10-19 manuscript.tex
Including feedback from co-authors and updating the main Figure.

--- 2021-09-22 manuscript.tex
@@
 However, the precise computations required by these internal models and their neural implementation remain unclear.
-Moreover, this simulationnist view raises the question of how it is possible to imagine actions without executing them.
-In this perspective, we consider the role of motor inhibition during covert speech production.
+Moreover, this simulationnist view raises the question of how it is possible to imagine speech without executing it.
+In this perspective, we highlight the role of motor inhibition during covert speech production.
 We suggest that considering covert speech as an inhibited form of overt speech maps naturally to the purported progressive internalisation of overt speech during childhood.
-However, we argue that the role of motor inhibition may differ widely across different forms of covert speech, and that this helps reconciling seemingly contradictory findings from the neuroimaging literature.
-
-% we focus on covert speech as an exciting case study to help understanding the interplay between language, motor control, and perceptual processes.
-
-% Since the first explorations of the phenomenological and psychophysiological properties of imagined actions, there has been considerable efforts and progresses towards describing the mechanisms leading to these sensory percepts.
+However, we argue that the role of motor inhibition may differ widely across different forms of covert speech (e.g., condensed vs.
+expanded covert speech) and that considering this variety helps reconciling seemingly contradictory findings from the neuroimaging literature.
 
@@
 
-The ability to mentally examine our thoughts is central to our subjective experience.
+The ability to mentally examine our verbal thoughts is central to our subjective experience.
 The internal (covert) production of speech may accompany common activities such as problem solving \citep{baldo_is_2005, sokolov_inner_1972}, future planning \citep{dargembeau_frequency_2011}, reading \citep[e.g.,][]{loevenbruck_left_2005, perrone-bertolotti_how_2012}, or writing \citep{frith_reading_1979}.
-Because speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
-Therefore, a parallel can be drawn between covert speech, also known as \textit{inner speech} or \textit{speech imagery} \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}, and other forms of covert verbal actions such as covert writing or covert typing and, more generally, other imagined actions (motor imagery).
+Because overt speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
+Therefore, a parallel can be drawn between covert speech, also known as \textit{inner speech} or \textit{speech imagery} \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}, and other forms of covert verbal actions such as covert writing or typing and, more generally, other imagined actions (motor imagery).
 
@@
 
-The motor simulation theory \citep{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001} of motor imagery postulates the existence of a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism.
-In short, covert actions would rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited \citep{oshea_does_2017}.
+The motor simulation theory \citep{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001} of motor imagery postulates the existence of a continuum between the covert and the overt execution of an action where action representations can operate off-line via a simulation mechanism.
+In short, covert actions would rely on the same set of mechanisms as the corresponding overt actions, except that execution is inhibited \citep{oshea_does_2017}.
 In this perspective, we examine some theoretical and experimental consequences that emerge when considering covert speech as inhibited overt speech.
@@
 Third, we consider how the role of inhibitory mechanisms may differ across different forms of covert speech.
-By bridging together recent results from the motor imagery, motor inhibition, and covert speech literature, we highlight some novel and possibly fruitful lines of research.
+By bridging together recent results from the covert speech, motor imagery, and motor inhibition, literature, we highlight some novel and possibly fruitful lines of research.
 
@@
 
-\subsection{Cognitive mechanisms and neural implementation}
+\subsection{Cognitive and neural mechanisms supporting motor inhibition}
 
-First and foremost, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and the idea of cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}.
+First and foremost, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}.
 Here, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
 To be more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, and specificity.
-Inhibition can be employed with more or less intentionality, from intentional to reactive inhibition, it can be planned ahead or employed in the moment (early vs.
-late inhibition) and can be applied to a specific action, a specific effector, or more globally, that is, to all actions and/or effectors.
+Inhibition can be employed with more or less intentionality (intentional vs.
+reactive), planned ahead or employed in the moment (early vs.
+late inhibition), and applied to a specific action and effector, or more globally, that is, to all actions and/or effectors.
 
-Crucially, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements), planned ahead (proactive), and possibly global form of response inhibition.
-Notice however that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature, because while doing motor imagery, participants are not explicitly asked not to produce an action \citep{guillot_imagining_2012}.
-Instead, they are asked to produce the action \textit{covertly}, which implicitly implies that it should not be executed overtly.
+Crucially, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements), planned ahead, and possibly global form of response inhibition.
+Notice however that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature.
+Indeed, in behavioural tasks aiming to assess proactive inhibition, participants are instructed no to execute an action.
+In contrast, while doing motor imagery,
+participants are asked to produce the action \textit{covertly}, which implicitly implies that it should not be executed overtly \citep{guillot_imagining_2012}.
 Using an action mode (overt vs.
@@
 
-After reviewing evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes through which motor commands can be inhibited during motor imagery.
-First, motor inhibition can be integrated within the representation of the action to be produced internally, therefore no active inhibition would be involved during motor imagery (but see the last paragraph of the current section).
-Second, cerebral regions such as the supplementary motor area (SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may progressively weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}, in addition to modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
-More precisely, the pre-SMA and the rIFG may work together to send a stop signal in order to intercept the action process via the basal ganglia (subthalamic nucleus, STN), suppressing the output from the basal ganglia and resulting in inhibitory effects on the primary motor cortex \citep{aron_reactive_2011} (cf.
-Figure \ref{fig:2}).\footnote{\cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the preSMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition.
-In their model, they suggest that the preSMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands.
+After reviewing evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes whereby motor commands can be inhibited during motor imagery.
+First, motor inhibition can be integrated within the representation of the action to be produced internally, therefore no inhibition would be involved during motor imagery.
+Second, cerebral regions such as the supplementary motor area (SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}, in addition to modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
+More precisely, the pre-SMA and the rIFG may work together to intercept the action process via the basal ganglia (subthalamic nucleus, STN), hence suppressing the output from the basal ganglia which in turn might inhibit the primary motor cortex \citep{aron_reactive_2011} (cf.
+Figure \ref{fig:2}).\footnote{\cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the pre-SMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition.
+In their model, they suggest that the pre-SMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands.
 Whether this functional dissociation is preserved in motor imagery remains an open question.} Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.
 
-The cause role of inhibitory mechanisms during motor imagery and covert speech could be assessed in several ways.
+The role of inhibitory mechanisms during motor imagery and covert speech could be assessed in several ways.
 First, it could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
-For instance, TMS could be used to "brake" these inhibitory mechanisms and "force" or facilitate execution during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
+For instance, transcranial magnetic stimulation (TMS) could be used to "brake" these inhibitory mechanisms and "force" or facilitate execution during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
 Second, the role of inhibitory mechanisms during covert verbal actions could be examined in a population with well-identified inhibitory deficits.
@@
 \cite{ganos_action_2014} have showed that the behavioural performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls.
-In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought about by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
+In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
 For these reasons, comparing the neural implementation of inhibitory mechanisms during covert speech in patients with Tourette syndrome and healthy controls may shed light on the role and flexibility of these mechanisms.
-
-% and may lead to applied outcomes in the care of motor and verbal tics.
 
@@
 It has been suggested that the primary motor cortex would be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}.
-However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned/regulated/monitored" \citep[see also][]{scheil_motor_2018}.
+However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}.
 In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level.
@@
 In this section, we provided empirical arguments in favour of the "active inhibition hypothesis".
-Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during motor imagery, thus preventing execution.
+Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during inner speech production, thus preventing execution.
 
@@
 \cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that covert speech matures from overt speech.
-\cite{vygotsky_thought_1934} then prominently formulated the idea that covert speech originates in overt speech, and more specifically, in private egocentric speech, that is, self-addressed overt speech in childhood.
-Vygotsky observed, as Piaget before, that egocentric or "private" speech tends to be internalised during child development.
-\cite{fernyhough_alien_2004} extended this model with four levels (stages) of internalisation: external dialogue, private speech, expanded inner speech and condensed inner speech.
-These levels represent stages of development but also define movements between levels (i.e., how we go from overt to covert speech and conversely).
+\cite{vygotsky_thought_1934} further formulated the idea that covert speech originates from private egocentric speech, that is, self-addressed overt speech in childhood.
+In other words, Vygotsky observed, as Piaget before, that egocentric speech tends to be internalised during child development.
+\cite{fernyhough_alien_2004} extended this idea with four levels of internalisation: external dialogue, private speech, expanded inner speech and condensed inner speech.
+These levels represent stages of development but also define movements between levels, that is, how we go from overt to covert speech and conversely.
 The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}.
@@
 \cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old).
-This suggests that inhibitory control may play a special role when speech is being internalised, but its role may weaken with expertise.
+This suggests that inhibitory control may play a peculiar role when speech is being internalised, but its role may weaken with expertise.
 This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
@@
 Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action.
-Therefore, it seems that (from a certain level of analysis), the act of speech can be paralleled with the act of playing an instrument in that it consists in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedbacks (e.g., kinaesthetic, auditory) for the agent.
+Therefore, it appears that the act of speech can be paralleled with the act of playing an instrument as it consists in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedbacks (e.g., kinaesthetic, auditory) for the agent.
 This analogy suggests that we might be able to study the development of internal models responsible for the sensory experience accompanying imagined actions in the adult mind (e.g., when an individual is learning either a novel music instrument or a new language with speech sounds that are not present in his/her native language).
@@
 
-The production of covert speech is often, although not always and not for everyone, accompanied by the feeling of hearing speech \cite{hurlburt_investigating_2011}.
+The production of covert speech is often, although not always and not for everyone, accompanied by the feeling of hearing speech \citep{hurlburt_investigating_2011}.
 In other words, covert speech is accompanied by a sensory experience that "feels like" hearing speech.
@@
 These two facets of covert speech are characterised by different phenomenological experiences.
-In this section, we discuss how these two forms of covert speech may require motor inhibition to a different extent, in the light of the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, a theoretical account of the mechanisms leading to the generation of sensory percepts during covert speech production.
+In this section, we discuss how these two forms of covert speech may require motor inhibition to a different extent, in the light of the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}.
 
-% while noticing that these mechanisms could be extended to other verbal actions as well.
+% a theoretical account of the mechanisms leading to the generation of sensory percepts during covert speech production.
 
@@
 
-%\footnote{This distinction shares similarities with the distinction between the prediction-by-simulation or prediction-by-association mechanisms in speech production and comprehension suggested by \cite{pickering_integrated_2013}.}
+% \footnote{This distinction shares similarities with the distinction between the prediction-by-simulation or prediction-by-association mechanisms in speech production and comprehension suggested by \cite{pickering_integrated_2013}.}
 
 The balance between these two mechanisms (i.e., simulation vs.
-association) may depend on the precise instructions given to the participants, which may clue them to produce different forms of covert speech.
+memory retrieval) may depend on the precise instructions given to the participants, which may clue them to produce different forms of covert speech.
 For instance, either one of these two streams may be recruited preferentially depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}.
-In line with this hypothesis, \cite{tian_mental_2016} have shown that imagined speaking more strongly recruits cerebral regions in the simulation stream than imagined hearing, which more strongly recruits cerebral regions in the association stream.
+In line with this hypothesis, \cite{tian_mental_2016} have shown that inner speaking more strongly recruits cerebral regions in the simulation stream than inner hearing, which more strongly recruits cerebral regions in the memory-retrieval stream.
 Moreover, \cite{ma_distinct_2019} have shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent phonetic (discriminating /ba/ vs.
@@
 
-In the absence of non-ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may also depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics.
-In addition to \cite{tian_mental_2012}, we suggest that a common currency determining the use of either one of these mechanisms is the computational cost of (or equivalently, the computational resources available for) each alternative.
+In the absence of ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may also depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics.
+We further suggest that a common currency determining the use of either one of these mechanisms is the computational cost of (or equivalently, the computational resources available for) each alternative.
 To clarify, we borrow the concept of memoisation as applied to cognition and mental imagery by \cite{dasgupta_memory_2021} (cf.
@@
 These disparities between inner speaking and inner hearing may explain the large variety of results when looking at the cerebral correlates of covert speech production \citep[as reviewed for instance in][]{geva_inner_2018}.
-Different forms of covert speech, that may vary in condensation, dialogicality, or intentionality \citep{grandchamp_condialint_2019}, may require inhibitory control to a different extent, from no inhibition at all for condensed forms of covert speech to active inhibition of motor commands for fully expanded forms of covert speech.
+Different forms of covert speech, that may vary in condensation, dialogicality, or intentionality \citep[see][]{grandchamp_condialint_2019}, may require inhibitory control to a different extent, from no inhibition at all for condensed forms of covert speech to active inhibition of motor commands for fully expanded forms of covert speech.
 
@@
 We explored some of the theoretical and experimental consequences that emerge when considering covert speech production as inhibited overt speech production.
-To this end,  we connected results from the motor imagery, motor inhibition, and covert speech research traditions.
+To this end, we connected results from the motor imagery, motor inhibition, and covert speech domains.
 Regarding the role of general-purpose inhibitory mechanisms during the production of covert speech, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and we summarised some propositions from this literature.
@@
 Regarding the neural origin of the sensory experience of covert speech, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process.
-We suggested that the balance between these two mechanisms, in addition to the task instructions, which may prompt different forms of covert speech, may also be determined by the available computational resources for (or equivalently, the computational cost of) the task, with novel or more difficult tasks being more costly.
+We suggested that the balance between these two mechanisms, in addition to the task instructions which may prompt different forms of covert speech, may also be determined by the available computational resources for (or equivalently, the computational cost of) the task.
 More precisely, novel or more difficult tasks are expected to rely more on the motor-simulation mechanisms whereas well-known and/or easy tasks may rely more on a "memoised version" of the motor simulation: the memory-retrieval prediction stream.
@@
 \caption{Plausible implementation of the cortical and subcortical inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during covert speech production.
-The preSMA, right pIFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production.
-Figure created with BioRender.com.
-FIGURE IN PROGRESS.}\label{fig:2}
+The pre-SMA, right IFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production.
+Figure created with BioRender.com.}\label{fig:2}
 \end{figure}

### 2021-10-26 manuscript.tex
incorporating feedback from co-authors

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Create explanation Box environment %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Creates an explanation Box environment %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \def\keyFont{\fontsize{8}{11}\helveticabold }
-\def\firstAuthorLast{Nalborczyk {et~al.}} %use et al only if is more than 1 author
+\def\firstAuthorLast{Nalborczyk {et al.}} % use et al only if is more than 1 author
 \def\Authors{Ladislas Nalborczyk\,$^{1,2,*}$, Ursula Debarnot\,$^{3,4}$, Marieke Longcamp\,$^{2}$, Aymeric Guillot\,$^{3,4}$, and F.-Xavier Alario\,$^{1}$}
@@
 \title[Motor inhibition and covert speech]{The role of motor inhibition during covert speech production}
-
-% Alternative title: Does covert speech production imply the motor inhibition of overt speech acts?
 
@@
 
-% One of the most influential theoretical model of motor imagery the motor simulation theory \cite{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001}, postulates the existence of a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism.
-In short, covert actions would rely on the same set of mechanisms as the overt actions they simulate, except that execution is inhibited \citep{oshea_does_2017}.
-A second class of models are concerned with the phenomenon of emulation \citep{grush_emulation_2004} and with internal models \cite[for a review of the similarities and dissimilarities between simulation and emulation models, see][]{gentsch_towards_2016}.
-Internal model theories share the postulate that action control uses internal models, that is, systems that simulate the behaviour of the motor apparatus \citep[e.g.,][]{jordan_forward_1992, kawato_hierarchical_1987}.
-The function of internal models is to estimate and anticipate the outcome of a motor command.
-Among the internal model theories, motor control models based on robotic principles \citep[e.g.,][]{kawato_internal_1999, wolpert_internal_1995} assume two kinds of internal models: a forward model (or simulator) that predicts the sensory consequences of motor commands from efference copies of the issued motor commands, and an inverse model (or controller) that calculates the feedforward motor commands from the desired sensory states \citep{gentsch_towards_2016, loevenbruck_cognitive_2018}.
-Notice that in the following, we do not distinguish further between simulation and emulation, and we use these terms interchangeably to designate the mechanism through which sensory consequences of motor commands (or copy thereof) are computed by forward internal models.
-
-% By building upon models of speech motor control (e.g., Houde \& Nagarajan, 2011; Wolpert et al., 1995), a recent model describes wilful (voluntary) expanded covert speech as "multi-modal acts with multi-sensory percepts stemming from coarse multi-sensory goals" \cite{loevenbruck_cognitive_2018}.
-In other words, this model considers the auditory and kinaesthetic sensations perceived during covert speech to be the predicted sensory consequences of inhibited speech motor acts, emulated by internal forward models that use the efference copies issued from an inverse model (this proposal shares some similarities with the emulation model of motor imagery, Grush, 2004) \cite{grush_emulation_2004}.
-This model is supported by several empirical results providing both behavioural and neurophysiological evidence for the efference copies issued during inner speech production (e.g., Scott, 2013; Whitford et al., 2017)...
-
 The motor simulation theory \citep{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001} of motor imagery postulates the existence of a continuum between the covert and the overt execution of an action where action representations can operate off-line via a simulation mechanism.
@@
 Here, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
-To be more precise, \cite{ridderinkhof_dont_2014} described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, and specificity.
+\cite{ridderinkhof_dont_2014} further described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, and specificity.
 Inhibition can be employed with more or less intentionality (intentional vs.
@@
 
-Crucially, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements), planned ahead, and possibly global form of response inhibition.
+Crucially, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements) and planned ahead form of response inhibition, which may apply both globally and in an effector-specific manner.
+Supporting the latter hypothesis, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have shown, using an action mode (overt vs.
+covert) switching paradigm, that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{scheil_motor_2018}.
 Notice however that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature.
-Indeed, in behavioural tasks aiming to assess proactive inhibition, participants are instructed no to execute an action.
+Indeed, in behavioural tasks aiming to assess proactive inhibition, participants are instructed not to execute an action.
 In contrast, while doing motor imagery,
 participants are asked to produce the action \textit{covertly}, which implicitly implies that it should not be executed overtly \citep{guillot_imagining_2012}.
-Using an action mode (overt vs.
-covert) switching paradigm, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have showed that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{scheil_motor_2018}.
-
-% further confirmed that both global and effector-specific inhibition may be at play during imagined (hand) movements and suggested that these two types of inhibition may work together and compensate for each other...
-\cite{schwoebel_man_2002}...
 
@@
 In their model, they suggest that the pre-SMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands.
-Whether this functional dissociation is preserved in motor imagery remains an open question.} Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.
-
-The role of inhibitory mechanisms during motor imagery and covert speech could be assessed in several ways.
-First, it could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
-For instance, transcranial magnetic stimulation (TMS) could be used to "brake" these inhibitory mechanisms and "force" or facilitate execution during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
-Second, the role of inhibitory mechanisms during covert verbal actions could be examined in a population with well-identified inhibitory deficits.
-For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}.
-Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia).
-\cite{ganos_action_2014} have showed that the behavioural performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls.
-In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
-For these reasons, comparing the neural implementation of inhibitory mechanisms during covert speech in patients with Tourette syndrome and healthy controls may shed light on the role and flexibility of these mechanisms.
+Whether this functional dissociation is preserved in motor imagery and covert speech remains an open question.} Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.
 
@@
 
+% \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}...
+\cite{ganos_action_2014} have showed that the behavioural performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls...
+
+The role of inhibitory mechanisms during motor imagery and covert speech could be assessed in several ways.
+First, it could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
+For instance, transcranial magnetic stimulation (TMS) could be used to "brake" these inhibitory mechanisms and "force" or facilitate execution during motor imagery.
+Second, the role of inhibitory mechanisms during covert verbal actions could be examined in a population with well-identified inhibitory deficits.
+For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}.
+Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia).
+In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
+For these reasons, comparing the neural implementation of inhibitory mechanisms during covert speech in patients with Tourette syndrome and healthy controls may shed light on the role and flexibility of these mechanisms.
+
 \subsection{Covert speech development: Learning not to produce speech}
@@
 In other words, Vygotsky observed, as Piaget before, that egocentric speech tends to be internalised during child development.
-\cite{fernyhough_alien_2004} extended this idea with four levels of internalisation: external dialogue, private speech, expanded inner speech and condensed inner speech.
+\cite{fernyhough_alien_2004} extended this idea with four levels of internalisation: external dialogue, private speech, expanded inner speech, and condensed inner speech.
 These levels represent stages of development but also define movements between levels, that is, how we go from overt to covert speech and conversely.
@@
 
-% This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise (e.g., Tarr and Pinker, 1989;Jolicoeur, 1985)
-
 Second, the hypothesised co-development of motor imagery and response inhibition abilities could be assessed by examining how novel actions are internalised in adults.\footnote{While keeping in mind the obvious limitation that the child mind is not equivalent to the adult mind, nor is it equivalent to a smaller version of the adult mind.
-Nevertheless, examining the development of novel imagined actions in adults avoids the contamination of the process of interest (imagined action) by developmental confounds.} For instance, Let’s consider the analogy between speaking and playing a music instrument (e.g., playing the piano).
+Nevertheless, examining the development of novel imagined actions in adults avoids the contamination of the process of interest (imagined action) by developmental confounds.} For instance, let's consider the analogy between speaking and playing a music instrument (e.g., playing the piano).
 Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action.
-Therefore, it appears that the act of speech can be paralleled with the act of playing an instrument as it consists in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedbacks (e.g., kinaesthetic, auditory) for the agent.
+Therefore, the act of producing speech can be paralleled with the act of playing an instrument as both actions consist in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedbacks (e.g., kinaesthetic, auditory) for the agent.
 This analogy suggests that we might be able to study the development of internal models responsible for the sensory experience accompanying imagined actions in the adult mind (e.g., when an individual is learning either a novel music instrument or a new language with speech sounds that are not present in his/her native language).
 By examining the development of novel imagined actions in the adult mind and by using motor interference (e.g., articulatory suppression) procedures, we might gain new insights about the internalisation of speech during childhood.
-
-% \section{The interplay between motor control and cognition}
-
-% \subsection{Where does this sensory content come from?}
-
-% Where does the sensory content of covert verbal actions come from?
-How does motor learning shape these sensory percepts?
-In other words, how do the motor and perceptual system interact during covert speech?
-In the first subsection, we discuss two mechanisms that may be responsible for providing the sensory content of covert speech and their respective involvement in different forms of covert speech.
-In the second subsection, we discuss an exciting avenue for investigating the influence of motor learning on the sensory content of covert speech, namely, the imagery of totally novel (i.e., never executed) speech acts.
 
@@
 In this section, we discuss how these two forms of covert speech may require motor inhibition to a different extent, in the light of the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}.
-
-% a theoretical account of the mechanisms leading to the generation of sensory percepts during covert speech production.
 
@@
 
-% This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
-
-% \subsection{The covert production of novel verbal actions}
-
-% If, as suggested in the previous section, the sensory content of covert speech is, at least in some situations, provided by a motor simulation process, how can we imagine totally novel actions?
-Broadly speaking, the simulationnist framework suggests that the multisensory experience of motor imagery results from the simulation of the corresponding motor action, reusing internal models developed for the control of overt actions \citep[e.g.,][]{jeannerod_representing_1994}.
-In other words, internal models developed for the control of actions would then be used to simulate the sensory consequences of covert actions.
-Crucially, these internal models are generative models, which means that they can be used to compute or predict the sensory consequences of any action that can be parsed as a \citep[possibly supramodal, see][]{loevenbruck_cognitive_2018} goal to an inverse internal model.
-In other words, this framework makes it possible for novel actions to be simulated internally.\footnote{\cite{mulder_role_2004} assessed whether the mental practice of a totally novel movement (abduction of the big toe of the dominant right foot) resulted in better overt execution over the course of several weeks of practice.
-They observed that although mental practise did improve execution in the group of participants that already had some experience with the task at baseline, mental practise did not lead to statistically significant improvements in execution in the group of participants that had zero experience with the task at baseline.
-However, a Bayesian reanalysis of their results suggests that the evidence in favour of the null hypothesis was rather inconclusive ($\text{BF}_{01} = 1.92$, using a weakly informative Cauchy prior on the standardised effect size for the alternative hypothesis, with $r = 1$).}
-
-% A general prediction of this framework is that the imagination of novel actions, and more precisely, the predicted sensory consequences of novel actions, may be "biased" or "constrained" by the repertoire of already-known actions.
-For instance, when asked to imagine playing table tennis, a tennis player may overestimate movements' amplitude and duration.
-Translated to speech production, this prediction could be assessed by asking participants to imagine a novel verbal action and subsequently checking whether this improves the execution of an "intermediate" novel action in the articulatory space.
-The same logic could be applied to the covert production of speech with someone else's voice.
-How can we imagine speaking with the voice of our relatives?
-If it is based on simulators, then the covert production of speech with someone else's voice should possess sensory properties that are somehow "biased" or "constrained" by the properties of our own sensory and motor systems.
-In other words, the subjective auditory sensation of covert speech with someone else's voice should be situated in a somehow intermediate (i.e., between the acoustic properties of our own voice and the acoustic properties of someone else voice) location in the auditory space.
-
-% This prediction could be assessed experimentally by using the sensory attenuation effect observed during covert speech production.
-Auditory stimuli elicit an electrophysiological brain response with a characteristic N1 component.
-This N1 component has been shown to be reduced when the presentation of an auditory stimulus is synchronised with the self-production of a phonetically-matched vocalisation, an effect called N1-suppression.
-More interestingly, \cite{whitford_neurophysiological_2017} have shown that the covert production of a phoneme also resulted in sensory attenuation, as assessed by N1-suppression, when the content of the imagined phoneme matched the content of the audible phoneme.
-Therefore, we could describe the subjective auditory sensation of covertly speaking with someone else’s voice by manipulating the acoustic properties of the auditory stimulus that is presented to the participant to find the stimulus that produces the greatest sensory attenuation, as assessed by N1-suppression.
-In other words, sensory attenuation should be the strongest when it matches the auditory representation of the speaker.
-If the auditory percepts generated when covertly speaking with the voice of someone else is "constrained" by our own sensory and motor systems, then this point of greatest sensory attenuation should occur in an intermediate location in the feature space.
-
 \section{Conclusions}
-
-% This led us to a discussion of two main themes.
-First, we asked how it is possible for covert speech production not to lead to overt speech production.
-Second, we discussed two mechanisms that may be used to provide the sensory content of covert speech, and how their respective involvement may be constrained by the available computational resources.
-To sketch an answer to these questions, we connected results from the motor imagery, motor inhibition, and covert speech research traditions.
 
@@
 To this end, we connected results from the motor imagery, motor inhibition, and covert speech domains.
-Regarding the role of general-purpose inhibitory mechanisms during the production of covert speech, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and we summarised some propositions from this literature.
+Regarding the role and implementation of general-purpose inhibitory mechanisms during the production of covert speech, we suggested that these may be similar to the inhibitory network responsible for proactive response inhibition and we summarised some propositions from this literature.
 We related the development of response inhibition abilities in childhood development with the purported internalisation of private speech around the same period.
@@
 
-% \color{blue}
-
-% The Author Contributions section is mandatory for all articles, including articles by sole authors.
-If an appropriate statement is not provided on submission, a standard one will be inserted during the production process.
-The Author Contributions statement must describe the contributions of individual authors referred to by their initials and, in doing so, all authors agree to be accountable for the content of the work.
-Please see  \href{http://home.frontiersin.org/about/author-guidelines#AuthorandContributors}{here} for full authorship criteria.
-
-% \color{black}
-
 Conceptualisation: all authors; Funding acquisition: LN; Supervision: UD, ML, AG, FXA; Writing - original draft: LN; Writing - review and editing: all authors.
@@
 \section*{Funding}
-
-% Details of all funding sources should be provided, including grant numbers if applicable. Please ensure to add all necessary funding information, as after publication this is no longer possible.
 
@@
 \caption{Plausible implementation of the cortical and subcortical inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during covert speech production.
-The pre-SMA, right IFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production.
+The pre-SMA, posterior rIFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production.
 Figure created with BioRender.com.}\label{fig:2}

### 2021-10-26 manuscript.tex
incorporating feedback

@@
 
-The motor simulation theory \citep{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001} of motor imagery postulates the existence of a continuum between the covert and the overt execution of an action where action representations can operate off-line via a simulation mechanism.
+The motor simulation theory \citep{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001} of motor imagery postulates the existence of a continuum between the covert and the overt execution of an action, where action representations can operate off-line via a simulation mechanism.
 In short, covert actions would rely on the same set of mechanisms as the corresponding overt actions, except that execution is inhibited \citep{oshea_does_2017}.
@@
 Third, we consider how the role of inhibitory mechanisms may differ across different forms of covert speech.
-By bridging together recent results from the covert speech, motor imagery, and motor inhibition, literature, we highlight some novel and possibly fruitful lines of research.
+By bridging together recent results from the covert speech, motor imagery, and motor inhibition literature, we highlight some novel and possibly fruitful lines of research.
 
@@
 reactive), planned ahead or employed in the moment (early vs.
-late inhibition), and applied to a specific action and effector, or more globally, that is, to all actions and/or effectors.
+late inhibition), and applied to a specific action and effector, or more globally, to all actions and/or effectors.
 

### 2021-10-27 manuscript.tex
Minor updates in figure

@@
 It has been suggested that the primary motor cortex would be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}.
-However, stating that motor imagery only involve subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}.
+However, stating that motor imagery only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}.
 In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level.
@@
 This suggests that inhibitory control may play a peculiar role when speech is being internalised, but its role may weaken with expertise.
-This is consistent with results from training studies suggesting that we rely more and more on domain-general (e.g., memory-based) processes with expertise \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
+This is consistent with results from training studies suggesting that, with growing expertise, we tend to rely more and more on memory-based processes to produce mental imagery \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
 
@@
 First, the simulation-estimation prediction stream implements a motor-to-sensory transformation via motor simulation, that is, by simulating speech movements and the perceptual changes that would be associated with these movements \citep[see also][for a similar proposal]{loevenbruck_cognitive_2018}.
-This stream includes cerebral areas involved in speech motor preparation such as the supplementary motor area, the inferior frontal gyrus, the premotor cortex and the insula, as well as cerebral areas involved in somatosensory estimation and perception such as primary and secondary somatosensory regions, the parietal operculum, and the supramarginal gyrus \citep{tian_mental_2016}.
+This stream includes cerebral areas involved in speech motor preparation such as the supplementary motor area, the inferior frontal gyrus, the premotor cortex and the insula, as well as brain areas involved in somatosensory estimation and perception such as primary and secondary somatosensory regions, the parietal operculum, and the supramarginal gyrus \citep{tian_mental_2016}.
 Second, the memory-retrieval prediction stream may be used to provide auditory percepts by "reconstructing stored perceptual information in modality-specific cortices" \citep{tian_mental_2016}.
@@
 For instance, either one of these two streams may be recruited preferentially depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}.
-In line with this hypothesis, \cite{tian_mental_2016} have shown that inner speaking more strongly recruits cerebral regions in the simulation stream than inner hearing, which more strongly recruits cerebral regions in the memory-retrieval stream.
+In line with this hypothesis, \cite{tian_mental_2016} have shown that inner speaking more strongly recruits brain regions in the simulation stream than inner hearing, which more strongly recruits brain regions in the memory-retrieval stream.
 Moreover, \cite{ma_distinct_2019} have shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent phonetic (discriminating /ba/ vs.
@@
 For instance, we hypothesise that novel and/or difficult tasks (which are both computationally more expensive, ceteris paribus) may rely more on the simulation mechanism, whereas well known and/or easy tasks may rely more on associative mechanisms.
-This idea is supported by several studies showing a greater increase in facial EMG activity during the reading of difficult text or while performing difficult mental arithmetic tasks as compared to easier tasks \citep[e.g.,][]{faaborg-andersen_electromyography_1958, sokolov_inner_1972}, suggesting a greater involvement of the speech motor system.
+This idea is supported by several studies showing a greater increase in facial EMG activity during the reading of difficult text or while performing difficult mental arithmetic tasks as compared to easier tasks % \citep[e.g.,][]{faaborg-andersen_electromyography_1958, sokolov_inner_1972}, suggesting a greater involvement of the speech motor system.
 Alternatively, these results may suggest a lesser involvement of inhibitory mechanisms \citep[see also the discussion in][]{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
@@
 Whereas the former mechanism should involve active inhibitory mechanisms, the latter should not, as there should be no (or less) motor commands to inhibit.
-Crucially, different forms of covert speech, varying in condensation, dialogicality, or intentionality, may require inhibitory control to a different extent.
+
+% Crucially, different forms of covert speech, varying in condensation, dialogicality, or intentionality, may require inhibitory control to a different extent.
 

### 2021-10-29 manuscript.tex
minor updates

@@
 
+% A significant consequence of this hypothesis is that the sensory experience of covert speech would be shaped by sensorimotor interactions with the environment.
+However, the precise computations required by these internal models and their neural implementation remain unclear.
+Moreover,
+
 \noindent Covert speech is accompanied by a subjective multisensory experience with auditory and kinaesthetic components.
 An influential hypothesis states that these sensory percepts result from a simulation of the corresponding motor action that relies on the same internal models recruited for the control of overt speech.
-A significant consequence of this hypothesis is that the sensory experience of covert speech would be continuously shaped by sensorimotor interactions with the environment.
-However, the precise computations required by these internal models and their neural implementation remain unclear.
-Moreover, this simulationnist view raises the question of how it is possible to imagine speech without executing it.
-In this perspective, we highlight the role of motor inhibition during covert speech production.
+This simulationnist view raises the question of how it is possible to imagine speech without executing it.
+In this perspective, we discuss the possible role(s) played by motor inhibition during covert speech production.
 We suggest that considering covert speech as an inhibited form of overt speech maps naturally to the purported progressive internalisation of overt speech during childhood.
@@
 The ability to mentally examine our verbal thoughts is central to our subjective experience.
-The internal (covert) production of speech may accompany common activities such as problem solving \citep{baldo_is_2005, sokolov_inner_1972}, future planning \citep{dargembeau_frequency_2011}, reading \citep[e.g.,][]{loevenbruck_left_2005, perrone-bertolotti_how_2012}, or writing \citep{frith_reading_1979}.
-Because overt speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
-Therefore, a parallel can be drawn between covert speech, also known as \textit{inner speech} or \textit{speech imagery} \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}, and other forms of covert verbal actions such as covert writing or typing and, more generally, other imagined actions (motor imagery).
+This covert (internal)  production of speech typically accompanies everyday activities such as problem solving \citep{baldo_is_2005, sokolov_inner_1972}, future planning \citep{dargembeau_frequency_2011}, reading \citep[e.g.,][]{loevenbruck_left_2005, perrone-bertolotti_how_2012}, or writing \citep{frith_reading_1979}.
+Because \textit{overt} speech production results from sequences of motor commands that are assembled to reach a given communication goal, it belongs to the broader category of motor actions \citep{jeannerod_motor_2006}.
+Therefore, a parallel can be drawn between covert speech, also known as \textit{inner speech} or \textit{speech imagery} \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}, and other imagined actions (i.e., motor imagery).
+The motor simulation theory of motor imagery \citep{jeannerod_representing_1994, jeannerod_neural_2001, jeannerod_origin_2006} postulates a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism.
 
-The motor simulation theory \citep{jeannerod_origin_2006, jeannerod_representing_1994, jeannerod_neural_2001} of motor imagery postulates the existence of a continuum between the covert and the overt execution of an action, where action representations can operate off-line via a simulation mechanism.
-In short, covert actions would rely on the same set of mechanisms as the corresponding overt actions, except that execution is inhibited \citep{oshea_does_2017}.
-In this perspective, we examine some theoretical and experimental consequences that emerge when considering covert speech as inhibited overt speech.
-First, we discuss the under-explored role of inhibitory mechanisms during covert speech production and their plausible neural implementation.
+However, the proposal that overt and covert actions share common processes and neural circuits is faced with a serious problem.
+If the neural circuits used for the control of overt actions are also used for covert actions, how can covert actions not lead to execution?
+This puzzle was coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}.
+It can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
+In this perspective, we examine some theoretical and experimental consequences that emerge from considering covert speech as inhibited overt speech.
+First, we explore the role and plausible neural implementation of inhibitory mechanisms during covert speech production.
 Second, we relate the maturation of inhibitory control during childhood with the progressive internalisation of overt speech.
-Third, we consider how the role of inhibitory mechanisms may differ across different forms of covert speech.
-By bridging together recent results from the covert speech, motor imagery, and motor inhibition literature, we highlight some novel and possibly fruitful lines of research.
+Third, we consider how inhibitory mechanisms may play different roles across different forms of covert speech.
+By bridging recent results from the covert speech, motor imagery, and motor inhibition literature, we highlight some novel and possibly fruitful lines of research.
 
@@
 
-The proposal that overt and covert actions share common neural circuits is faced with a serious problem.
-If the neural circuits used for the control of overt actions are reused for covert actions, how can covert actions not lead to execution?
-This puzzle, coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}, can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
-In the following, we briefly summarise the evidence in favour of the view of covert speech as inhibited overt speech.
-We outline some working hypotheses regarding the cognitive and neural implementation of these inhibitory mechanisms.
-Then, we relate this view to the presumed progressive internalisation of speech during childhood.
-Finally, we examine how the role of motor inhibition may differ across different forms of covert speech.
-
 \subsection{Cognitive and neural mechanisms supporting motor inhibition}
 
-First and foremost, we need to make a distinction between at least two different types of inhibition: the inhibition of physical response (e.g., planning to raise the arm and finally not doing it), and cognitive inhibition, defined as "the stopping or overriding of a mental process, in whole or in part, with or without intention" \citep{gorfein_concept_2007}.
-Here, we are concerned with the former, which can be defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
+First and foremost, we need to make a distinction between at least two different types of inhibition.
+First, cognitive inhibition, defined as the stopping or overriding of a mental process, with or without intention \citep{gorfein_concept_2007}.
+Second, the inhibition of physical response, or motor inhibition, defined broadly as the withholding, suppression, or overriding of an inappropriate, prepotent, or unwanted motor response \citep{aron_neural_2007, oshea_go_2018}.
+Here, we are concerned with the latter.
 \cite{ridderinkhof_dont_2014} further described the concept of response inhibition on three continuous dimensions: intentionality, premeditation, and specificity.
-Inhibition can be employed with more or less intentionality (intentional vs.
-reactive), planned ahead or employed in the moment (early vs.
-late inhibition), and applied to a specific action and effector, or more globally, to all actions and/or effectors.
+Inhibition can be employed with more or less intentionality, planned ahead or employed in the moment, and applied to a specific action and effector, or more globally, to all actions and/or effectors.
 
-Crucially, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but automatic (we do not explicitly think about not producing movements) and planned ahead form of response inhibition, which may apply both globally and in an effector-specific manner.
-Supporting the latter hypothesis, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have shown, using an action mode (overt vs.
+Within \citeauthor{ridderinkhof_dont_2014}'s classification of response inhibitions, we hypothesise that covert speech involves an intentional (we know we want to produce these actions covertly rather than overtly) but implicit/automatic (we do not explicitly think about not producing movements) and planned ahead form of response inhibition.
+The distinction between implicit and explicit inhibition seems important to highlight.
+Indeed, the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature.
+Indeed, in behavioural tasks aiming to assess proactive inhibition, participants are instructed not to execute an action.
+In contrast, while doing motor imagery, participants are asked to imagine the action, which implies that it should not be executed overtly \citep{guillot_imagining_2012}.
+Moreover, the type of motor inhibition that is implemented during covert speech necessarily has to be planned ahead, otherwise speech acts would sometimes be (at least partially) executed.
+Regarding the level at which motor inhibition may be applied during covert speech, we hypothesise that inhibition may apply both globally and in an effector-specific manner.
+Supporting this hypothesis, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have shown, using an action mode (overt vs.
 covert) switching paradigm, that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{scheil_motor_2018}.
-Notice however that the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature.
-Indeed, in behavioural tasks aiming to assess proactive inhibition, participants are instructed not to execute an action.
-In contrast, while doing motor imagery,
-participants are asked to produce the action \textit{covertly}, which implicitly implies that it should not be executed overtly \citep{guillot_imagining_2012}.
 
-After reviewing evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes whereby motor commands can be inhibited during motor imagery.
-First, motor inhibition can be integrated within the representation of the action to be produced internally, therefore no inhibition would be involved during motor imagery.
-Second, cerebral regions such as the supplementary motor area (SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}, in addition to modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
+Based on evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes whereby motor commands can be inhibited during motor imagery.
+First, motor inhibition can be integrated within the representation of the action to be produced internally.
+Second, cerebral regions such as the supplementary motor area (SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
 More precisely, the pre-SMA and the rIFG may work together to intercept the action process via the basal ganglia (subthalamic nucleus, STN), hence suppressing the output from the basal ganglia which in turn might inhibit the primary motor cortex \citep{aron_reactive_2011} (cf.
-Figure \ref{fig:2}).\footnote{\cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the pre-SMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition.
+Figure \ref{triangle}).
+In addition to inter-regional inhibitory influences, motor imagery has been shown to be associated with modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
+Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.
+
+% \cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the pre-SMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition.
 In their model, they suggest that the pre-SMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands.
-Whether this functional dissociation is preserved in motor imagery and covert speech remains an open question.} Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.
+Whether this functional dissociation is preserved in motor imagery and covert speech remains an open question.
 
-Whether covert speech production is accompanied by the emission of motor commands that are subsequently inhibited has been the matter of debate \citep[e.g.,][]{geva_inner_2018}.
-It has been suggested that the primary motor cortex would be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018}.
-However, stating that motor imagery only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}.
+% It has been suggested that the primary motor cortex would be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018, grandchamp_condialint_2019}
+
+Whether motor commands are emitted and subsequently inhibited during covert speech production is an issue that has been debated \citep[e.g.,][]{geva_inner_2018}.
+It has been suggested that during covert speech production, motor commands would be "simply specified in sub-threshold way, requiring no active inhibition" \citep{geva_inner_2018}.
+Alternatively, during covert speech production, motor commands may be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018, grandchamp_condialint_2019}.
+However, stating that covert speech (or motor imagery, more generally) only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}.
 In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level.
@@
 In this section, we provided empirical arguments in favour of the "active inhibition hypothesis".
-Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during inner speech production, thus preventing execution.
+Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during covert speech production, thus preventing execution.
 
@@
 
-The role of inhibitory mechanisms during motor imagery and covert speech could be assessed in several ways.
+The putative involvement and functional role of inhibitory mechanisms during covert speech could be assessed in several ways.
 First, it could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
-For instance, transcranial magnetic stimulation (TMS) could be used to "brake" these inhibitory mechanisms and "force" or facilitate execution during motor imagery.
-Second, the role of inhibitory mechanisms during covert verbal actions could be examined in a population with well-identified inhibitory deficits.
+For instance, transcranial magnetic stimulation (TMS) could be used to interrupt these inhibitory mechanisms and thus facilitate execution during motor imagery.
+Second, the role of inhibitory mechanisms during covert verbal actions could be examined in populations with well-identified inhibitory deficits.
 For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}.
 Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia).
-In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs is brought by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
+In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs, acquired by repeatedly trying to suppress tics, is brought by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
 For these reasons, comparing the neural implementation of inhibitory mechanisms during covert speech in patients with Tourette syndrome and healthy controls may shed light on the role and flexibility of these mechanisms.
@@
 
-\cite{watson_psychology_1919} suggested that thought (i.e., covert speech, in his terminology) was rooted in (overt) speech, that is, that covert speech matures from overt speech.
-\cite{vygotsky_thought_1934} further formulated the idea that covert speech originates from private egocentric speech, that is, self-addressed overt speech in childhood.
-In other words, Vygotsky observed, as Piaget before, that egocentric speech tends to be internalised during child development.
-\cite{fernyhough_alien_2004} extended this idea with four levels of internalisation: external dialogue, private speech, expanded inner speech, and condensed inner speech.
+% In other words, Vygotsky observed that egocentric speech tends to be internalised during child development.
+
+\cite{watson_psychology_1919} suggested that thought was rooted in overt speech.
+In his terminology, thought referred to covert speech.
+Hence, his view was that covert speech matures from overt speech.
+\cite{vygotsky_thought_1934} further formulated the idea that covert speech is internalised during childhood from private egocentric speech, that is, from self-addressed overt speech.
+\cite{fernyhough_alien_2004} extended these ideas by proposing four levels of internalisation: external dialogue, private speech, expanded inner speech, and condensed inner speech.
 These levels represent stages of development but also define movements between levels, that is, how we go from overt to covert speech and conversely.
@@
 Therefore, producing speech covertly crucially depends on successfully inhibiting speech production at several levels.
+
 We formulate the hypothesis that the progressive internalisation of speech during childhood may be related to the development of inhibitory abilities.
-
-This idea could be assessed in several ways.
+This hypothesis could be tested in several ways.
 First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years).
-We would expect the ability to imagine actions and speech specifically to be positively correlated with inhibitory skills at this age.
-\cite{wang_relationship_2021} provided correlational evidence that motor imagery and motor inhibition performance improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old (but did not correlate at 11 years old).
+We would expect the ability to imagine actions, and speech specifically, to be positively correlated with inhibitory skills at this age.
+\cite{wang_relationship_2021} provided correlational evidence that motor imagery (as assessed by a hand laterality judgement task and alphanumeric rotation task) and motor inhibition performance (as assessed by a stop-signal task) improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old but did not correlate at 11 years old.
 This suggests that inhibitory control may play a peculiar role when speech is being internalised, but its role may weaken with expertise.
@@
 
-Second, the hypothesised co-development of motor imagery and response inhibition abilities could be assessed by examining how novel actions are internalised in adults.\footnote{While keeping in mind the obvious limitation that the child mind is not equivalent to the adult mind, nor is it equivalent to a smaller version of the adult mind.
-Nevertheless, examining the development of novel imagined actions in adults avoids the contamination of the process of interest (imagined action) by developmental confounds.} For instance, let's consider the analogy between speaking and playing a music instrument (e.g., playing the piano).
-Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action.
-Therefore, the act of producing speech can be paralleled with the act of playing an instrument as both actions consist in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedbacks (e.g., kinaesthetic, auditory) for the agent.
+Second, the hypothesised co-development of motor imagery and response inhibition abilities could be tested by examining how novel actions are internalised in adults.
+For instance, let's consider the analogy between speaking and playing a music instrument (e.g., playing the piano).
+The act of producing speech can be paralleled with the act of playing an instrument.
+Both actions consist in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedback (e.g., kinaesthetic, auditory) for the agent.
 This analogy suggests that we might be able to study the development of internal models responsible for the sensory experience accompanying imagined actions in the adult mind (e.g., when an individual is learning either a novel music instrument or a new language with speech sounds that are not present in his/her native language).
-By examining the development of novel imagined actions in the adult mind and by using motor interference (e.g., articulatory suppression) procedures, we might gain new insights about the internalisation of speech during childhood.
+By examining the development of novel imagined actions in the adult mind and by using motor interference (e.g., articulatory suppression) procedures, we might gain new insights about the internalisation of speech during childhood.\footnote{While keeping in mind the obvious limitation that the child mind is not equivalent to the adult mind, nor is it equivalent to a smaller version of the adult mind.
+Nevertheless, examining the development of novel imagined actions in adults avoids the contamination of the process of interest (imagined action) by developmental confounds.}
+
+% Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action.
+Therefore
 
@@
 These two facets of covert speech are characterised by different phenomenological experiences.
-In this section, we discuss how these two forms of covert speech may require motor inhibition to a different extent, in the light of the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}.
+In this section, we discuss how these two forms of covert speech may require motor inhibition to a different extent.
+
+% in the light of the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}.
 
@@
 Second, the memory-retrieval prediction stream may be used to provide auditory percepts by "reconstructing stored perceptual information in modality-specific cortices" \citep{tian_mental_2016}.
-In other words, sensory percepts would be generated by activating sensory-specific cortices from object properties stored in long-term memory.
 This mechanism provides sensory percepts without the need for computing the predicted sensory consequences of (non executed) motor commands.
-This stream includes semantic networks, including frontal, temporal, and parietal regions \citep[for more details, see][]{tian_mental_2016}.
+Auditory percepts may be retrieved from various memory sources, relying (amongst others) on the hippocampal structures \citep{tian_mental_2016}.
+Auditory percepts may also be retrieved from lexical and semantic information stored in semantic networks, including frontal, temporal, and parietal regions \citep[for more details, see][]{tian_mental_2016}.
+
+% In other words, sensory percepts would be generated by activating sensory-specific cortices from object properties stored in long-term memory.
 
@@
 The balance between these two mechanisms (i.e., simulation vs.
-memory retrieval) may depend on the precise instructions given to the participants, which may clue them to produce different forms of covert speech.
-For instance, either one of these two streams may be recruited preferentially depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}.
+memory retrieval) may depend on the circumstances promoting covert speech or, in the lab, on the precise instructions given to the participants, which may cue them to produce different forms of covert speech.
+For instance, either one of these two streams may be preferentially recruited depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}.
 In line with this hypothesis, \cite{tian_mental_2016} have shown that inner speaking more strongly recruits brain regions in the simulation stream than inner hearing, which more strongly recruits brain regions in the memory-retrieval stream.
-Moreover, \cite{ma_distinct_2019} have shown that inner speaking and inner hearing have distinct MEG correlates and effects on a subsequent phonetic (discriminating /ba/ vs.
-/da/) categorisation task.
+\cite{ma_distinct_2019} have shown that inner speaking and inner hearing have distinct magnetoencephalographic (MEG) correlates and distinct effects on a subsequent phonetic categorisation task (discriminating /ba/ vs.
+/da/).
 
-In the absence of ambiguous instructions, and in line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may also depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics.
+In line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may also depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics.
 We further suggest that a common currency determining the use of either one of these mechanisms is the computational cost of (or equivalently, the computational resources available for) each alternative.
@@
 Box \ref{memoisation}).
-In their view, memory can be considered as a computational resource to facilitate computational reuse through memoisation.
-In the context of motor and speech imagery, memoisation can be seen in the greater reliance on memory in the course of learning, where motor-to-sensory mappings are partially or completely retrieved from memory, instead of being computed again every time.
+In these authors' view, memory can be considered as a computational resource to facilitate computational reuse through memoisation.
+In the context of motor and speech imagery, memoisation can be seen in the increasing reliance on memory in the course of learning.
+
+% where motor-to-sensory mappings are partially or completely retrieved from memory, instead of being computed again every time.
 
@@
 
-\begin{mybox}[label = memoisation]{Memoisation}
+\begin{mybox}[label=memoisation,float,floatplacement=!htb]{Memoisation}
 
@@
 When calling a function (where a function can be a motor primitive), the function call is intercepted by a \textit{memoiser} that inspects the previous calls of a function and its outputs.
-If a function has already been called with the same input, then the previously computed output is retrieved and reused.
+If a function has already been called with the same input, then the previously computed output is retrieved and reused.\\
+
+In the context of covert speech, memoisation can be postulated as the process by which covert speech percepts produced by motor simulation are stored for later retrieval and use without invoking the motor simulation mechanism.
 
@@
 For instance, we hypothesise that novel and/or difficult tasks (which are both computationally more expensive, ceteris paribus) may rely more on the simulation mechanism, whereas well known and/or easy tasks may rely more on associative mechanisms.
-This idea is supported by several studies showing a greater increase in facial EMG activity during the reading of difficult text or while performing difficult mental arithmetic tasks as compared to easier tasks % \citep[e.g.,][]{faaborg-andersen_electromyography_1958, sokolov_inner_1972}, suggesting a greater involvement of the speech motor system.
+This idea is supported by several studies showing a greater increase in facial EMG activity during the reading of difficult text or while performing difficult mental arithmetic tasks, compared to easier tasks \citep[e.g.,][]{faaborg-andersen_electromyography_1958, sokolov_inner_1972}, suggesting a greater involvement of the speech motor system.
 Alternatively, these results may suggest a lesser involvement of inhibitory mechanisms \citep[see also the discussion in][]{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
@@
 
-To sum up, whereas inner speaking may involve active inhibition of motor commands, inner hearing may not (or to a lesser extent).
-These disparities between inner speaking and inner hearing may explain the large variety of results when looking at the cerebral correlates of covert speech production \citep[as reviewed for instance in][]{geva_inner_2018}.
-Different forms of covert speech, that may vary in condensation, dialogicality, or intentionality \citep[see][]{grandchamp_condialint_2019}, may require inhibitory control to a different extent, from no inhibition at all for condensed forms of covert speech to active inhibition of motor commands for fully expanded forms of covert speech.
+To sum up, whereas inner speaking may involve active inhibition of motor commands, inner hearing may not.
+These disparities between inner speaking and inner hearing may explain the variety of neural correlates reported for covert speech production \citep[as reviewed for instance in][]{geva_inner_2018}.
+More generally, different forms of covert speech, that may vary in condensation (from thinking without words to thinking in words), dialogicality (whether covert speech features monologues or dialogues), or intentionality \citep[for more details, see][]{grandchamp_condialint_2019}, may require inhibitory control to a different extent, from no inhibition at all for condensed forms of covert speech to active inhibition of motor commands for fully expanded forms of covert speech.
 
@@
 
-We explored some of the theoretical and experimental consequences that emerge when considering covert speech production as inhibited overt speech production.
+We explored some of the theoretical and experimental consequences that emerge from considering covert speech production as an inhibited form of overt speech production.
 To this end, we connected results from the motor imagery, motor inhibition, and covert speech domains.
@@
 
-Regarding the neural origin of the sensory experience of covert speech, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation-based process or by a memory-based process.
-We suggested that the balance between these two mechanisms, in addition to the task instructions which may prompt different forms of covert speech, may also be determined by the available computational resources for (or equivalently, the computational cost of) the task.
+Regarding the neural origin of the sensory experience of covert speech, we discussed the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}, which suggests that these sensory percepts may be provided either by a motor-simulation process or by a memory-retrieval process.
+We suggested that the balance between these two mechanisms may be determined by task instructions, which may prompt different forms of covert speech, and also by the computational cost of the task.
 More precisely, novel or more difficult tasks are expected to rely more on the motor-simulation mechanisms whereas well-known and/or easy tasks may rely more on a "memoised version" of the motor simulation: the memory-retrieval prediction stream.
@@
 
-Taken together, these propositions pave the way for several lines of research that should consolidate our understanding of the relations between overt and covert speech production.
+These propositions pave the way for several lines of research that should consolidate our understanding of the relations between overt and covert speech production.
 Several outstanding questions remain.
 Amongst others, how does the development of inhibitory control relate with the progressive internalisation of speech during childhood?
-How individual and situational constraints shape the role of motor inhibition during covert speech production?
+How do individual and situational constraints shape the role of motor inhibition during covert speech production?
 How is covert speech affected by poor or degraded inhibitory control?
-Can we experimentally "force" (e.g., using neurostimulation) the externalisation of speech in adults?
+Can we experimentally force the externalisation of speech in adults, for example through neurostimulation?
 The use of neurostimulation and the comparison between healthy controls and patients with well-identified inhibitory deficits could help refine the involvement of these inhibitory mechanisms during covert speech production, which may lead to applied outcomes in the care of motor and verbal tics.
@@
 
-Conceptualisation: all authors; Funding acquisition: LN; Supervision: UD, ML, AG, FXA; Writing - original draft: LN; Writing - review and editing: all authors.
+Conceptualisation: all authors; Funding acquisition: LN, ML, FXA; Supervision: UD, ML, AG, FXA; Writing - original draft: LN; Writing - review and editing: all authors.
 
@@
 
-\section*{Acknowledgements}
+% \section*{Acknowledgements}
 
-None.
+% None.
 
@@
 The pre-SMA, posterior rIFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production.
-Figure created with BioRender.com.}\label{fig:2}
+Figure created with BioRender.com.}\label{triangle}
 \end{figure}

### 2021-10-29 manuscript.tex
incorporating final feedback

@@
 
-%\setcitestyle{square} % for Physics and Applied Mathematics and Statistics articles
 % \usepackage{url,hyperref,lineno,microtype,subcaption}
@@
 % Leave a blank line between paragraphs instead of using \\
-
 \def\keyFont{\fontsize{8}{11}\helveticabold }
@@
 
-% A significant consequence of this hypothesis is that the sensory experience of covert speech would be shaped by sensorimotor interactions with the environment.
-However, the precise computations required by these internal models and their neural implementation remain unclear.
-Moreover,
-
 \noindent Covert speech is accompanied by a subjective multisensory experience with auditory and kinaesthetic components.
@@
  \keyFont{\section{Keywords:} covert speech, inner speech, motor imagery, motor simulation, motor control, motor inhibition} % All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+
 \end{abstract}
@@
 
-% \cite{diesburg_pause-then-cancel_2021} proposed a functional dissociation between the pre-SMA and the rIFC in a two-stage "pause-then-cancel" model of action inhibition.
-In their model, they suggest that the pre-SMA would be involved in (globally) pausing the action whereas the rIFC would be involved in selectively cancelling (resetting) motor commands.
-Whether this functional dissociation is preserved in motor imagery and covert speech remains an open question.
-
-% It has been suggested that the primary motor cortex would be "bypassed" during covert speech  \citep[e.g.,][]{tian_mental_2012, tian_effect_2013, tian_mental_2016} or that motor commands would be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018, grandchamp_condialint_2019}
-
 Whether motor commands are emitted and subsequently inhibited during covert speech production is an issue that has been debated \citep[e.g.,][]{geva_inner_2018}.
 It has been suggested that during covert speech production, motor commands would be "simply specified in sub-threshold way, requiring no active inhibition" \citep{geva_inner_2018}.
-Alternatively, during covert speech production, motor commands may be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018, grandchamp_condialint_2019}.
+Alternatively, motor commands may be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018, grandchamp_condialint_2019}.
 However, stating that covert speech (or motor imagery, more generally) only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}.
@@
 Proponents of the "subliminal level hypothesis" need to clarify how this activity is maintained at a subthreshold level during covert speech production, thus preventing execution.
-
-% \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}...
-\cite{ganos_action_2014} have showed that the behavioural performance during a stop-signal reaction-time task was similar across Tourette patients and healthy controls...
 
@@
 Verbal tics can consist of repeating sounds, words, or utterances (palilalia), producing inappropriate or obscene utterances (coprolalia), or the repetition of another’s words (echolalia).
-In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs, acquired by repeatedly trying to suppress tics, is brought by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
+In their review, \cite{jackson_inhibition_2015} suggested that increased control over motor outputs, acquired by repeatedly trying to suppress tics, is brought about by local increases in GABAergic "tonic" inhibition within regions such as the SMA, leading to localised reductions in the gain of motor excitability.
 For these reasons, comparing the neural implementation of inhibitory mechanisms during covert speech in patients with Tourette syndrome and healthy controls may shed light on the role and flexibility of these mechanisms.
@@
 \subsection{Covert speech development: Learning not to produce speech}
-
-% In other words, Vygotsky observed that egocentric speech tends to be internalised during child development.
 
@@
 \cite{fernyhough_alien_2004} extended these ideas by proposing four levels of internalisation: external dialogue, private speech, expanded inner speech, and condensed inner speech.
-These levels represent stages of development but also define movements between levels, that is, how we go from overt to covert speech and conversely.
+These levels represent stages of development but also define movements between levels, that is, how a speaker may go from overt to covert speech and conversely.
 The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}.
-Therefore, producing speech covertly crucially depends on successfully inhibiting speech production at several levels.
+Therefore, producing covert speech crucially depends on successfully inhibiting speech production at several levels.
 
@@
 
-% Essentially, learning to play the piano can be said to consist in learning to produce and coordinate complex and fine-grained motor sequences that in turn produce multisensory (e.g., kinaesthetic, auditory, visual) feedback to the agent producing of the action.
-Therefore
-
 \subsection{Does covert speech always involve motor inhibition?}
@@
 
-% in the light of the dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016}.
-
 The dual stream prediction model \citep{tian_mental_2012, tian_effect_2013, tian_mental_2016} describes two neural pathways that may provide the auditory content of covert speech.
@@
 Auditory percepts may be retrieved from various memory sources, relying (amongst others) on the hippocampal structures \citep{tian_mental_2016}.
-Auditory percepts may also be retrieved from lexical and semantic information stored in semantic networks, including frontal, temporal, and parietal regions \citep[for more details, see][]{tian_mental_2016}.
+Auditory percepts may also be retrieved from a broad fronto-temporo-parietal lexico-semantic network \citep[for more details, see][]{tian_mental_2016}.
 
-% In other words, sensory percepts would be generated by activating sensory-specific cortices from object properties stored in long-term memory.
-
-% \footnote{This distinction shares similarities with the distinction between the prediction-by-simulation or prediction-by-association mechanisms in speech production and comprehension suggested by \cite{pickering_integrated_2013}.}
+% Auditory percepts may also be retrieved from lexical and semantic information stored in semantic networks, including frontal, temporal, and parietal regions \citep[for more details, see][]{tian_mental_2016}.
 
@@
 In the context of motor and speech imagery, memoisation can be seen in the increasing reliance on memory in the course of learning.
-
-% where motor-to-sensory mappings are partially or completely retrieved from memory, instead of being computed again every time.
-
-% \vspace{5mm}
 
@@
 
-% Crucially, different forms of covert speech, varying in condensation, dialogicality, or intentionality, may require inhibitory control to a different extent.
-
 These propositions pave the way for several lines of research that should consolidate our understanding of the relations between overt and covert speech production.
@@
 \section*{Conflict of Interest Statement}
-
-% All financial, commercial or other relationships that might be perceived by the academic community as representing a potential conflict of interest must be disclosed.
-If no such relationship exists, authors will be asked to confirm the following statement:
 
@@
 
-% Please see the availability of data guidelines for more information, at https://www.frontiersin.org/about/author-guidelines#AvailabilityofData
-
-\bibliographystyle{template/frontiersinSCNS_ENG_HUMS} % for Science, Engineering and Humanities and Social Sciences articles, for Humanities and Social Sciences articles please include page numbers in the in-text citations
-%\bibliographystyle{frontiersinHLTH&FPHY} % for Health, Physics and Mathematics articles
-% \bibliography{test}
+\bibliographystyle{template/frontiersinSCNS_ENG_HUMS}
 \bibliography{bibliography/covert_verbal_actions}
-
-%%% Make sure to upload the bib file along with the tex file and PDF
-%%% Please see the test.bib file for some examples of references
 

### 2021-12-17 manuscript.tex
Incorporating feedback from reviewers

@@
 An influential hypothesis states that these sensory percepts result from a simulation of the corresponding motor action that relies on the same internal models recruited for the control of overt speech.
-This simulationnist view raises the question of how it is possible to imagine speech without executing it.
+This simulationist view raises the question of how it is possible to imagine speech without executing it.
 In this perspective, we discuss the possible role(s) played by motor inhibition during covert speech production.
 We suggest that considering covert speech as an inhibited form of overt speech maps naturally to the purported progressive internalisation of overt speech during childhood.
-However, we argue that the role of motor inhibition may differ widely across different forms of covert speech (e.g., condensed vs.
+We further argue that the role of motor inhibition may differ widely across different forms of covert speech (e.g., condensed vs.
 expanded covert speech) and that considering this variety helps reconciling seemingly contradictory findings from the neuroimaging literature.
@@
 Therefore, a parallel can be drawn between covert speech, also known as \textit{inner speech} or \textit{speech imagery} \citep[for reviews, see][]{alderson-day_inner_2015, perrone-bertolotti_what_2014, loevenbruck_cognitive_2018}, and other imagined actions (i.e., motor imagery).
-The motor simulation theory of motor imagery \citep{jeannerod_representing_1994, jeannerod_neural_2001, jeannerod_origin_2006} postulates a continuum between the covert and the overt execution of an action and that action representations can operate off-line via a simulation mechanism.
+The motor simulation theory of motor imagery \citep{jeannerod_representing_1994, jeannerod_neural_2001, jeannerod_origin_2006} postulates a continuum between the covert and the overt execution of an action, and that action representations can operate off-line via a simulation mechanism.
+
+% It can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
 
@@
 If the neural circuits used for the control of overt actions are also used for covert actions, how can covert actions not lead to execution?
-This puzzle was coined as \textit{the problem of inhibition} by \cite{jeannerod_neural_2001}.
-It can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
+This puzzle was coined as \textit{the problem of inhibition of execution} by \cite{jeannerod_neural_2001}.
 In this perspective, we examine some theoretical and experimental consequences that emerge from considering covert speech as inhibited overt speech.
@@
 The distinction between implicit and explicit inhibition seems important to highlight.
-Indeed, the type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature.
+The type of motor inhibition that may be at play during motor imagery is still different from the "proactive inhibition" in the motor inhibition literature.
 Indeed, in behavioural tasks aiming to assess proactive inhibition, participants are instructed not to execute an action.
-In contrast, while doing motor imagery, participants are asked to imagine the action, which implies that it should not be executed overtly \citep{guillot_imagining_2012}.
+In contrast, while doing motor imagery, participants are asked to imagine the action, which indirectly implies that it should not be executed overtly \citep{guillot_imagining_2012}.
 Moreover, the type of motor inhibition that is implemented during covert speech necessarily has to be planned ahead, otherwise speech acts would sometimes be (at least partially) executed.
-Regarding the level at which motor inhibition may be applied during covert speech, we hypothesise that inhibition may apply both globally and in an effector-specific manner.
+Finally, the level at which motor inhibition may be applied can be inferred from the example of hand movements.
+\cite{rieger_inhibition_2017} used an action mode (overt vs.
+covert) switching paradigm, to show that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{bart_decay_2021, bart_expectations_2021, bart_inhibitory_2021, scheil_motor_2018}.
+Here, we hypothesise that inhibition during covert speech may similarly apply both globally and in an effector-specific manner.
+
+% Regarding the level at which motor inhibition may be applied during covert speech, we hypothesise that inhibition may apply both globally and in an effector-specific manner.
 Supporting this hypothesis, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have shown, using an action mode (overt vs.
-covert) switching paradigm, that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{scheil_motor_2018}.
+covert) switching paradigm, that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{bart_expectations_2021, bart_decay_2021, scheil_motor_2018}.
 
 Based on evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes whereby motor commands can be inhibited during motor imagery.
-First, motor inhibition can be integrated within the representation of the action to be produced internally.
-Second, cerebral regions such as the supplementary motor area (SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
+First, motor inhibition can be integrated within the representation of the action to be produced internally, so that only subthreshold motor commands may be involved during motor imagery \citep[see also][]{bach_why_2021, glover_executive_2020}.
+Second, cerebral regions such as the pre-supplementary motor area (pre-SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
 More precisely, the pre-SMA and the rIFG may work together to intercept the action process via the basal ganglia (subthalamic nucleus, STN), hence suppressing the output from the basal ganglia which in turn might inhibit the primary motor cortex \citep{aron_reactive_2011} (cf.
 Figure \ref{triangle}).
-In addition to inter-regional inhibitory influences, motor imagery has been shown to be associated with modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
+In addition to such inter-regional inhibitory influences, motor imagery has been shown to be associated with modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
 Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.
 
-Whether motor commands are emitted and subsequently inhibited during covert speech production is an issue that has been debated \citep[e.g.,][]{geva_inner_2018}.
-It has been suggested that during covert speech production, motor commands would be "simply specified in sub-threshold way, requiring no active inhibition" \citep{geva_inner_2018}.
-Alternatively, motor commands may be emitted but subsequently inhibited by frontal regions \citep[e.g.,][]{loevenbruck_cognitive_2018, grandchamp_condialint_2019}.
+Whether speech motor commands are emitted and subsequently inhibited during covert production is an issue that has been debated \citep[e.g.,][]{geva_inner_2018}.
+It has been suggested that during covert speech production, motor commands would be "simply specified in subthreshold way, requiring no active inhibition" \citep{geva_inner_2018}.
+Alternatively, motor commands may be emitted but subsequently inhibited by frontal or prefrontal regions such as the pre-SMA or rIFG \citep[e.g.,][]{jeannerod_neural_2001, loevenbruck_cognitive_2018, grandchamp_condialint_2019}.
 However, stating that covert speech (or motor imagery, more generally) only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}.
 In other words, we still need to explain how (in a mechanistic and/or developmental way) this activity is maintained at a subthreshold level.
-What cognitive and neural mechanisms operate to maintain this activity under the threshold?
 In this section, we provided empirical arguments in favour of the "active inhibition hypothesis".
@@
 
-The putative involvement and functional role of inhibitory mechanisms during covert speech could be assessed in several ways.
+The putative involvement and functional role of (cortical and subcortical) inhibitory mechanisms during covert speech could be assessed in several ways.
 First, it could be assessed by experimentally manipulating the activity of the inhibitory network responsible for preventing execution during motor imagery.
-For instance, transcranial magnetic stimulation (TMS) could be used to interrupt these inhibitory mechanisms and thus facilitate execution during motor imagery.
-Second, the role of inhibitory mechanisms during covert verbal actions could be examined in populations with well-identified inhibitory deficits.
+For instance, transcranial magnetic stimulation (TMS) could be used to interrupt these inhibitory mechanisms and thus trigger execution during motor imagery.
+Second, it could be assessed by looking at covert speech production in patients with acquired (focal) brain damage.
+For instance, \cite{schwoebel_man_2002} observed that bilateral parietal lesions can lead patients to execute actions when they asked to imagine them, suggesting a failure of inhibitory mechanisms.
+Third, the role of inhibitory mechanisms during covert verbal actions could be examined in populations with well-identified inhibitory deficits.
 For instance, Tourette syndrome is a childhood-onset neurological disorder affecting approximately 1\% of children and characterised by chronic motor and phonic tics \citep{jackson_inhibition_2015}.
@@
 Hence, his view was that covert speech matures from overt speech.
-\cite{vygotsky_thought_1934} further formulated the idea that covert speech is internalised during childhood from private egocentric speech, that is, from self-addressed overt speech.
+\cite{vygotsky_thought_1934} further elaborated the idea that covert speech is internalised during childhood from private egocentric speech, that is, from self-addressed overt speech.
 \cite{fernyhough_alien_2004} extended these ideas by proposing four levels of internalisation: external dialogue, private speech, expanded inner speech, and condensed inner speech.
-These levels represent stages of development but also define movements between levels, that is, how a speaker may go from overt to covert speech and conversely.
+These levels represent stages of development but also define movements between levels, that is, how a speaker may transform overt speech to covert speech, and conversely.
 The level at which speech is expressed may depend on inhibitory control applied at different levels in the production flow, such as the formulation or the articulatory planning level \citep{grandchamp_condialint_2019}.
@@
 
-We formulate the hypothesis that the progressive internalisation of speech during childhood may be related to the development of inhibitory abilities.
+Here, we hypothesise that the progressive internalisation of speech during childhood may be related to the development of inhibitory abilities.
 This hypothesis could be tested in several ways.
 First, the relation between speech internalisation and inhibitory abilities could be assessed during development at the critical ages (i.e., between 6 and 8 years).
-We would expect the ability to imagine actions, and speech specifically, to be positively correlated with inhibitory skills at this age.
-\cite{wang_relationship_2021} provided correlational evidence that motor imagery (as assessed by a hand laterality judgement task and alphanumeric rotation task) and motor inhibition performance (as assessed by a stop-signal task) improve together between 7 and 11 years old, and that these two abilities correlated at 7 years old but did not correlate at 11 years old.
-This suggests that inhibitory control may play a peculiar role when speech is being internalised, but its role may weaken with expertise.
-This is consistent with results from training studies suggesting that, with growing expertise, we tend to rely more and more on memory-based processes to produce mental imagery \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
+We would expect the ability to imagine actions, and speech specifically, to be positively correlated with motor inhibition at this age.
+\cite{wang_relationship_2021} provided correlational evidence that motor imagery (assessed in a hand laterality judgement task) and motor inhibition performance (assessed in a stop-signal task) improve together between 7 and 11 years old, and that these two abilities correlate at 7 years old but did not correlate at 11 years old.
+This suggests that inhibitory control may play a more prominent role role when speech is being internalised, but its role may weaken with expertise.
+This would be consistent with results from training studies suggesting that, with growing expertise, mental imagery increasingly relies on memory-based processes  \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
 
 Second, the hypothesised co-development of motor imagery and response inhibition abilities could be tested by examining how novel actions are internalised in adults.
-For instance, let's consider the analogy between speaking and playing a music instrument (e.g., playing the piano).
-The act of producing speech can be paralleled with the act of playing an instrument.
+Consider for instance how the act of producing speech can be paralleled with the act of playing a music instrument (e.g., the piano).
 Both actions consist in the coordination of complex movements that result in some modifications of the environment, that in turn generate sensory feedback (e.g., kinaesthetic, auditory) for the agent.
 This analogy suggests that we might be able to study the development of internal models responsible for the sensory experience accompanying imagined actions in the adult mind (e.g., when an individual is learning either a novel music instrument or a new language with speech sounds that are not present in his/her native language).
-By examining the development of novel imagined actions in the adult mind and by using motor interference (e.g., articulatory suppression) procedures, we might gain new insights about the internalisation of speech during childhood.\footnote{While keeping in mind the obvious limitation that the child mind is not equivalent to the adult mind, nor is it equivalent to a smaller version of the adult mind.
+By examining the development of novel imagined actions in the adult mind and by using motor interference (e.g., articulatory suppression) procedures, we might gain new insights about the internalisation of speech during childhood.\footnote{We should keep in mind the obvious limitation that the child mind is not equivalent to the adult mind, nor is it equivalent to a smaller version of the adult mind.
 Nevertheless, examining the development of novel imagined actions in adults avoids the contamination of the process of interest (imagined action) by developmental confounds.}
@@
 
-The production of covert speech is often, although not always and not for everyone, accompanied by the feeling of hearing speech \citep{hurlburt_investigating_2011}.
-In other words, covert speech is accompanied by a sensory experience that "feels like" hearing speech.
-However, covert speech may also be accompanied by the feeling of producing speech.
+The production of covert speech is often, although not always and not for everyone, accompanied by the feeling of \textit{hearing} speech \citep{hurlburt_investigating_2011}.
+However, covert speech may also be accompanied by the feeling of \textit{producing} speech.
 These two facets of covert speech are characterised by different phenomenological experiences.
@@
 This stream includes cerebral areas involved in speech motor preparation such as the supplementary motor area, the inferior frontal gyrus, the premotor cortex and the insula, as well as brain areas involved in somatosensory estimation and perception such as primary and secondary somatosensory regions, the parietal operculum, and the supramarginal gyrus \citep{tian_mental_2016}.
-Second, the memory-retrieval prediction stream may be used to provide auditory percepts by "reconstructing stored perceptual information in modality-specific cortices" \citep{tian_mental_2016}.
+Second, the memory-retrieval prediction stream provides auditory percepts by "reconstructing stored perceptual information in modality-specific cortices" \citep{tian_mental_2016}.
 This mechanism provides sensory percepts without the need for computing the predicted sensory consequences of (non executed) motor commands.
-Auditory percepts may be retrieved from various memory sources, relying (amongst others) on the hippocampal structures \citep{tian_mental_2016}.
-Auditory percepts may also be retrieved from a broad fronto-temporo-parietal lexico-semantic network \citep[for more details, see][]{tian_mental_2016}.
+Auditory percepts may be retrieved from various memory sources, relying (amongst others) on the hippocampal formation \citep{tian_mental_2016}, or from a broad fronto-temporo-parietal lexico-semantic network \citep[for more details, see][]{tian_mental_2016}.
 
-% Auditory percepts may also be retrieved from lexical and semantic information stored in semantic networks, including frontal, temporal, and parietal regions \citep[for more details, see][]{tian_mental_2016}.
-
-The balance between these two mechanisms (i.e., simulation vs.
-memory retrieval) may depend on the circumstances promoting covert speech or, in the lab, on the precise instructions given to the participants, which may cue them to produce different forms of covert speech.
+The balance between the mechanisms of simulation and memory retrieval may depend on the circumstances promoting covert speech or, in the lab, on the precise instructions given to participants, which may cue them to produce different forms of covert speech.
 For instance, either one of these two streams may be preferentially recruited depending on whether participants are instructed to "imagine speaking" or to "imagine hearing" \citep[see also the distinction between the "inner ear" and the "inner voice", e.g.,][]{smith_subvocalization_1992}.
-In line with this hypothesis, \cite{tian_mental_2016} have shown that inner speaking more strongly recruits brain regions in the simulation stream than inner hearing, which more strongly recruits brain regions in the memory-retrieval stream.
+In line with this hypothesis, \cite{tian_mental_2016} have shown that inner speaking recruits brain regions in the simulation stream more strongly than inner hearing, which conversely recruits more strongly brain regions in the memory-retrieval stream.
 \cite{ma_distinct_2019} have shown that inner speaking and inner hearing have distinct magnetoencephalographic (MEG) correlates and distinct effects on a subsequent phonetic categorisation task (discriminating /ba/ vs.
@@
 
-In line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may also depend on situational (e.g., surrounding noise) and intrinsic (e.g., expertise) characteristics.
-We further suggest that a common currency determining the use of either one of these mechanisms is the computational cost of (or equivalently, the computational resources available for) each alternative.
+In line with \cite{tian_mental_2012}, we suggest that the balance between these two mechanisms may also depend on a participant's situational (e.g., surrounding noise) and individual (e.g., expertise) characteristics.
+We further suggest that a common currency to determine the recruitment of either one of these mechanisms is the computational cost of (or equivalently, the computational resources available for) each alternative.
 To clarify, we borrow the concept of memoisation as applied to cognition and mental imagery by \cite{dasgupta_memory_2021} (cf.
 Box \ref{memoisation}).
-In these authors' view, memory can be considered as a computational resource to facilitate computational reuse through memoisation.
+In these authors' view, memory can be considered as a computational resource that facilitates computational reuse through memoisation.
 In the context of motor and speech imagery, memoisation can be seen in the increasing reliance on memory in the course of learning.
@@
 Memoisation is a programming technique used to speed-up algorithms or programs.
-It avoids redundant computation by storing computational results and reusing them later.
+It avoids redundant computation by storing computational results and reusing them later \citep{dasgupta_memory_2021}.
 When calling a function (where a function can be a motor primitive), the function call is intercepted by a \textit{memoiser} that inspects the previous calls of a function and its outputs.
@@
 Alternatively, these results may suggest a lesser involvement of inhibitory mechanisms \citep[see also the discussion in][]{nalborczyk_understanding_2019-1, nalborczyk_re-analysing_2020}.
-This is congruent with the greater reliance on associative mechanisms with greater expertise, as discussed previously.
+This is congruent with the increased reliance on associative mechanisms with greater expertise, as discussed previously.
 
@@
 These disparities between inner speaking and inner hearing may explain the variety of neural correlates reported for covert speech production \citep[as reviewed for instance in][]{geva_inner_2018}.
-More generally, different forms of covert speech, that may vary in condensation (from thinking without words to thinking in words), dialogicality (whether covert speech features monologues or dialogues), or intentionality \citep[for more details, see][]{grandchamp_condialint_2019}, may require inhibitory control to a different extent, from no inhibition at all for condensed forms of covert speech to active inhibition of motor commands for fully expanded forms of covert speech.
+More generally, different forms of covert speech may vary in condensation (from thinking without words to thinking in words), dialogicality (whether covert speech features monologues or dialogues), or intentionality \citep[for more details, see][]{grandchamp_condialint_2019} and may thus require inhibitory control to a different extent, from no inhibition at all for condensed forms of covert speech to active inhibition of motor commands for fully expanded forms of covert speech.
 
@@
 We related the development of response inhibition abilities in childhood development with the purported internalisation of private speech around the same period.
-From the response inhibition perspective, the internalisation of speech from overt to covert speech may essentially be considered as "learning not to produce speech".
+From the response inhibition perspective, the internalisation of speech from overt to covert speech may essentially be considered as "learning not to execute speech".
 
@@
 Several outstanding questions remain.
-Amongst others, how does the development of inhibitory control relate with the progressive internalisation of speech during childhood?
-How do individual and situational constraints shape the role of motor inhibition during covert speech production?
-How is covert speech affected by poor or degraded inhibitory control?
+Amongst others, further research should aim at testing whether and how the development of inhibitory control relates with the progressive internalisation of speech during childhood.
+Do individual and situational constraints shape the role of motor inhibition during covert speech production?
+Is covert speech affected by poor or degraded inhibitory control?
 Can we experimentally force the externalisation of speech in adults, for example through neurostimulation?
@@
 \bibliographystyle{template/frontiersinSCNS_ENG_HUMS}
-\bibliography{bibliography/covert_verbal_actions}
+\bibliography{bibliography/covert_verbal_actions2}
 
@@
 \caption{Plausible implementation of the cortical and subcortical inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during covert speech production.
-The pre-SMA, posterior rIFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production.
+The pre-SMA, posterior IFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production.
 Figure created with BioRender.com.}\label{triangle}

### 2022-01-31 manuscript.tex
updating the bib file's name
Updates from Overleaf

@@
 
-% \usepackage{url,hyperref,lineno,microtype,subcaption}
 \usepackage{url,hyperref,lineno,microtype}
@@
 
-% It can be rephrased as follows: given the putative role of the motor system in providing the multisensory content of motor imagery, how is it possible for motor imagery not to lead to motor execution?
-
 However, the proposal that overt and covert actions share common processes and neural circuits is faced with a serious problem.
@@
 
-% Regarding the level at which motor inhibition may be applied during covert speech, we hypothesise that inhibition may apply both globally and in an effector-specific manner.
-Supporting this hypothesis, \cite{rieger_inhibition_2017} and \cite{bart_inhibitory_2021} have shown, using an action mode (overt vs.
-covert) switching paradigm, that the motor imagery of hand movements is accompanied by both global and effector-specific inhibition \citep[these results were also replicated in][]{bart_expectations_2021, bart_decay_2021, scheil_motor_2018}.
-
-Based on evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested three possible routes whereby motor commands can be inhibited during motor imagery.
-First, motor inhibition can be integrated within the representation of the action to be produced internally, so that only subthreshold motor commands may be involved during motor imagery \citep[see also][]{bach_why_2021, glover_executive_2020}.
-Second, cerebral regions such as the pre-supplementary motor area (pre-SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
-More precisely, the pre-SMA and the rIFG may work together to intercept the action process via the basal ganglia (subthalamic nucleus, STN), hence suppressing the output from the basal ganglia which in turn might inhibit the primary motor cortex \citep{aron_reactive_2011} (cf.
-Figure \ref{triangle}).
-In addition to such inter-regional inhibitory influences, motor imagery has been shown to be associated with modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
+Based on evidence from electrophysiological, neuroimaging, and clinical studies, \cite{guillot_imagining_2012} suggested several possible routes whereby motor commands can be inhibited during motor imagery.
+First, cerebral regions such as the pre-supplementary motor area (pre-SMA) \citep{kasess_suppressive_2008} or the right inferior frontal gyrus (rIFG) may weaken the motor commands that are emitted during motor imagery \citep[e.g.,][]{angelini_motor_2015, angelini_proactive_2016}.
+More precisely, the pre-SMA and the rIFG may work together to intercept the action process via the basal ganglia (subthalamic nucleus), hence suppressing the output from the basal ganglia which in turn might inhibit the primary motor cortex \citep{aron_reactive_2011}.
+Second, motor imagery has been shown to be associated with modulations of short-interval intracortical inhibition within the primary motor cortex itself \citep{neige_unravelling_2020}.
 Third, downstream regions in the cerebellum \citep[e.g.,][]{lotze_activation_1999}, in the brainstem \citep[e.g.,][]{jeannerod_neural_2001, jeannerod_motor_2006}, or at the spinal level may contribute to motor inhibition at a later stage.
 
-Whether speech motor commands are emitted and subsequently inhibited during covert production is an issue that has been debated \citep[e.g.,][]{geva_inner_2018}.
+In addition to these three possible routes, another possibility highlighted by \cite{guillot_imagining_2012} is that motor inhibition can be integrated within the representation of the action to be produced internally, so that only subthreshold motor commands may be involved during motor imagery \citep[hereafter referred to as the "subliminal level hypothesis", see also][]{bach_why_2021, glover_executive_2020}.
 It has been suggested that during covert speech production, motor commands would be "simply specified in subthreshold way, requiring no active inhibition" \citep{geva_inner_2018}.
-Alternatively, motor commands may be emitted but subsequently inhibited by frontal or prefrontal regions such as the pre-SMA or rIFG \citep[e.g.,][]{jeannerod_neural_2001, loevenbruck_cognitive_2018, grandchamp_condialint_2019}.
 However, stating that covert speech (or motor imagery, more generally) only involves subthreshold activity (and therefore is not accompanied by the emission of motor commands that are inhibited) simply shifts the problem from "how and where motor commands are subsequently inhibited" to "how and where the magnitude of activity in the motor system is planned or monitored" \citep[see also][]{scheil_motor_2018}.
@@
 \cite{wang_relationship_2021} provided correlational evidence that motor imagery (assessed in a hand laterality judgement task) and motor inhibition performance (assessed in a stop-signal task) improve together between 7 and 11 years old, and that these two abilities correlate at 7 years old but did not correlate at 11 years old.
-This suggests that inhibitory control may play a more prominent role role when speech is being internalised, but its role may weaken with expertise.
+This suggests that inhibitory control may play a more prominent role when speech is being internalised, but its role may weaken with expertise.
 This would be consistent with results from training studies suggesting that, with growing expertise, mental imagery increasingly relies on memory-based processes  \citep[e.g.,][]{tarr_mental_1989, jolicoeur_time_1985}.
@@
 
-% \section*{Acknowledgements}
-
-% None.
-
-% \section*{Supplemental Data}
-
-% \href{http://home.frontiersin.org/about/author-guidelines#SupplementaryMaterial}{Supplementary Material} should be uploaded separately on submission, if there are Supplementary Figures, please include the caption in the same file as the figure.
-LaTeX Supplementary Material templates can be found in the Frontiers LaTeX folder.
-
 \section*{Data Availability Statement}
@@
 \bibliographystyle{template/frontiersinSCNS_ENG_HUMS}
-\bibliography{bibliography/covert_verbal_actions2}
+\bibliography{bibliography/covert_verbal_actions}
 
-\section*{Figure captions}
+% \section*{Figure captions}
 
@@
 
-% \begin{figure}[ht] % float was h! initially
-% \begin{center}
-% \includegraphics[width=0.75\textwidth]{figures/simulation_association.png} % This is a *.eps file
-% \end{center}
-% \caption{High-level depiction of the prediction-by-simulation (in blue) and prediction-by-association (in orange) mechanisms.
-The balance (weighting) between these two mechanisms during covert verbal actions depends on both task demands and "computational cost" (cf.
-text for more details), which are jointly determined by internal (individual) and external (situational) characteristics (e.g., expertise or (equivalently) task difficulty, noise, feedback perturbation).}\label{fig:1}
-% \end{figure}
-
-\begin{figure}[ht] % float was h! initially
-\begin{center}
-\includegraphics[width=0.75\textwidth]{figures/inhibitory_triangle.png} % This is a *.eps file
-\end{center}
-\caption{Plausible implementation of the cortical and subcortical inhibitory mechanisms responsible for the "proactive" (but implicit) response inhibition at play during covert speech production.
-The pre-SMA, posterior IFC, and STN together form an \textit{inhibitory network} known as the \textit{inhibitory triangle}, which may be responsible for braking motor commands during covert speech production.
-Figure created with BioRender.com.}\label{triangle}
-\end{figure}
-
 %%% If you are submitting a figure with subfigures please combine these into one image file with part labels integrated.
